### 2006-02-05 article/Article.tex
begin article
darcs-hash:20060205212122-2fc9d-9d7dadc08b8cbd930a0ae743c0a4ceedd3790241.gz

%
% Complete documentation on the extended LaTeX markup used for Insight
% documentation is available in ``Documenting Insight'', which is part
% of the standard documentation for Insight.  It may be found online
% at:
%
%     http://www.itk.org/

\documentclass{InsightArticle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  hyperref should be the last package to be loaded.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}
% to be able to use options in graphics
\usepackage{graphicx}
% for pseudo code
\usepackage{listings}
% subfigures
\usepackage{subfigure}

%  This is a template for Papers to the Insight Journal. 
%  It is comparable to a technical report format.

% The title should be descriptive enough for people to be able to find
% the relevant document. 
\title{WrapITK: Enhanced languages support\\ for the Insight Toolkit}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.1}

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$} {\small{and}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
\authoraddress{{$^1$}Unit\'e de Biologie du D\'eveloppement et de la Reproduction, Institut National de la Recherche Agronomique, 78350 Jouy-en-Josas, France\\
{$^2$}Stanford University, CA 94305, USA\\
{$^3$}Creatis, CNRS, 69621 Villeurbanne, France}

\begin{document}
\lstset{language=python}
\maketitle

\ifhtml
\chapter*{Front Matter\label{front}}
\fi

\begin{abstract}
\noindent
ITK is a huge image analysis library, which contains lots of state of the arts
algorithms implementations. However, using it in C++ can be difficult and is
definitively bad suited for prototyping. WrapITK aims to allow classes from ITK
(and custom, classes that interact with ITK) to be "wrapped" for use with
languages like Python, Tcl, and Java.
\end{abstract}

\tableofcontents

\section{Introduction}

WrapITK is a project designed to allow classes from ITK (and custom, classes
that interact with ITK) to be "wrapped" for use with languages like
Python, Tcl, and Java.

Note that ITK already has a wrapping infrastructure. This project aims to be
address the following deficits of the existing wrappers (and others):
\begin{itemize}
  \item  ITK is a huge library, but only a small number of classes are available
in target languages. It become quickly frustrating for the user, especially when
he have to spend lot of time to extend the current set of classes. Even if it is
not yet complete, the WrapITK's set of classes have been highly extended. Moreover,
the user can choose at build time which types and which dimensions he want to wrap.

  \item  The template arguments set is poorly choosen, making sometime impossible
to create a pipeline. In WrapITK, most of the filters have the same input and output
types. Only a few filters allow to change type. This make the types manipulated 
by filters more consistent.

  \item  The python's \verb$InsightToolkit$ module is only strucutred as a big list
of names. This make it nearly unusable in the python interpreter. The python's
module organization is completely changed to be more structured and flexible.

  \item  Lots of types returned by ITK object's methods are not usable in target
languages. For example, the \verb$GetPixel()$ method of the class \verb$itk::Image$
returns a string describing a pointer, but don't return the pixel value. In WrapITK,
most types used in classes are available in target languages.

  \item  Names in target laguages are inconsistents.

  \item  The ITK wrapping system is difficult to understand and maintain. WrapITK was
written -- and thoroughly documented -- to be as easy as possible to understand,
maintain, and extend.

  \item  It is non-trivial to add wrappers for different ITK classes to the system. In
WrapITK, adding a wrapper can be as simple as adding a single file containing a
few well-documented cmake macros.

  \item  It is difficult if not impossible to add original-style ITK wrappers for
external C++ classes that interact with ITK. WrapITK provides explicit hooks for
external C++ classes to be wrapped and even installed in the WrapITK tree so
that they interact seamlessly with the other wrapped classes.

  \item  Once the ITK wrappers are built, using them from within the target languages
is in many cases painful, forcing Python code (for example) to look a lot like
C++ code, but nastier. In particular, template types must be hard-coded into
every function name. WrapITK attempts to address this in Python by providing
run-time lookup of templated types. Additionally, WrapITK ensures that
\verb$SmartPointer$s are always returned and acceptable as input, so no bare pointers
are ever exposed to Python. This is not the case in the standard ITK wrappers.

\end{itemize}

Currently, WrapITK only supports Python properly; Java and Tcl libraries build
correctly but the Java and Tcl support classes for loading these libraries needs
some updating.

\section{User guide}

  \subsection{Installation}

    \subsubsection{Get the software}

A tarball archive is submitted with the article.

To get the last version, the user can get the last version from the darcs repository
with the command 
\verb$darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/$.

For the user which don't want to use darcs but want the last development version,
a nightly updated archive is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz}.

    \subsubsection{CableSwig}

WrapITK requires ITK and CableSwig to have been previously downloaded and built.
To get CableSwig, simply run:
\verb$cvs -d:pserver:anonymous@public.kitware.com:/cvsroot/CableSwig co CableSwig$
(Note that no cvs login is needed here.)

If you check out CableSwig into the \verb$Insight/Utilities$ directory, then it will be
built as a part of ITK, and will be automatically detected by WrapITK when ITK
is found.

    \subsubsection{Required and optional patches}

WrapITK will work properly with a CVS checkout of ITK from 2006-1-31 or later,
or with the ITK 2.4.1 release. If you are using 2.4.1, there are several
required patches to correct bugs in ITK that must be applied. Follow the
directions in \verb$WrapITK/patches$ to do so. Additionally, there are some optional
patches to the ITK source in \verb$WrapITK/patches/optional$ which can be applied to
either a CVS checkout of ITK or to version 2.4.1. These optional patches provide
better support for python by providing \verb$__str__$ methods and the like.

    \subsubsection{Build options}

After CableSwig and ITK have been (possibly patched) and built, building WrapITK
with cmake is simple. Run ccmake in a new directory with the path to the WrapITK
source tree as the first argument, and provide the locations of the ITK and
CableSwig build trees if ccmake so requests. Build options are relatively
self-explanatory.

Note that each individual filter that is wrapped can declare which dimensions it
should be wrapped for, and what image types it can accept. For example, a filter
could declare that it should only be wrapped for 3D images with floating-point
typed pixels. In this case, then wrappers will only be created if the user has
selected to build 3-dimensional image wrappers and has selected one or more
floating point types (e.g. double or float) in ccmake. Thus, the ccmake
configuration specifies the maximum possible range of image and filter types to
be created, and each filter is wrapped for some subset of that range.

    \subsubsection{Install WrapITK or use it in the build tree}

  \subsection{Python usage}

     \subsubsection{Configuring python and importing the libraries}

If WrapITK has been installed, then using it from within python is trivial:
simply issue the command \verb$import itk$, and you are ready to go. This
is because WrapITK installs a pth file in the python site-packages directory so
that python knows where to find the itk scripts.

If WrapITK has not been installed, then you will either need to set the
\verb$PYTHONPATH$ environment variable to contain the directory
\verb$/path-to-WrapITK-build/Python$, add  this path to sys.paths within python, or
start python from that directory. After this, \verb$import itk$ will work
properly.

     \subsubsection{Basic Usage}

Most class in the itk python module are "template proxy classes" that
encapsulate all of the template instantiations that were created at build time.
If three-dimensional unsigned char and unsigned short image types were created,
they can be accessed as follows:
\begin{itemize}
  \item \verb$itk.Image[itk.UC, 3]$ or \verb$itk.Image.UC3$
  \item \verb$itk.Image[itk.US, 3]$ or \verb$itk.Image.US3$
\end{itemize}

Filters templated on images can be similarly accessed:
\begin{itemize}
  \item \verb$itk.ImageFileReader[itk.Image[itk.UC,3]]$
  \item or \verb$itk.ImageFileReader[itk.Image.UC3]$
  \item or even \verb$itk.ImageFileReader[image]$ if \verb$image$ is of type \verb$UC3$.
\end{itemize}
This makes it easy to write generic routines which
can deal with any input image type.

Each class has a \verb$New()$ method which returns a smart pointer to that class. The
\verb$New()$ method in python has some additional features:
\begin{itemize}
  \item Arguments to the new method are assumed to be filter inputs. So you could
write:
\small \begin{verbatim}
adder = itk.AddImageFilter[...].New()
adder.SetInput1(inputA)
adder.SetInput2(inputB)
\end{verbatim} \normalsize
or you could write
\small \begin{verbatim}
adder = itk.AddImageFilter[...].New(inputA, inputB)
\end{verbatim} \normalsize

  \item Additionally, keyword arguments are allowed as well. Keyword arguments cause
the corresponding \verb$Set...$ method to be called, so you could write the
following:
\small \begin{verbatim}
itk.ImageFileWriter[image].New(image, FileName="foo.tif")
\end{verbatim} \normalsize
or
\small \begin{verbatim}
itk.ImageFileWriter[image].New(Input=image, FileName="foo.tif")
\end{verbatim} \normalsize

\end{itemize}

     \subsubsection{Advanced Features}
As an extra bonus, it is possible to view the doxygen documentation for each
class as the python docstring. This string is available as:
\small \begin{verbatim}
print itk.Image.__doc__
\end{verbatim} \normalsize
or even better (if you use iPython)
\small \begin{verbatim}
itk.Image?
\end{verbatim} \normalsize

Several steps are necessary to obtain this nirvana, however. First, when
configuring the build in ccmake, you must set \verb$DOXYGEN_MAN_PATH$ to some directory
where man pages for the ITK classes will be created. Then, after the build, you
must run \verb$make_doxygen_config.py$ from within the \verb$Python$ directory in the build
directory, to collect information about the wrapped classes and create a doxygen
configuration file to make these man pages. Finally, run doxygen with that
configuration file. After these three simple steps, class docstrings will
contain the man page information. Note that this is limited to systems which
support the python \verb$commands$ module, and which have \verb$groff$ in the path. This
basically means anything but windows will work. (Cygwin should work too.)

In addition (as mentioned above), WrapITK by default ensures that no bare
pointers are ever returned to python: instead reference-counting \verb$SmartPointer$s
are used. However, there may be times when extracting a bare pointer or creating
a new \verb$SmartPointer$ is necessary. To get a bare pointer from a smart pointer, use
the \verb$GetPointer()$ method, as in ITK proper. To create a new smart pointer, the
\verb$SmartPointer$ template proxy class can be used just as above:
\small \begin{verbatim}
smartPtr = itk.SmartPointer[itk.Image[itk.US, 2]](image.GetPointer())
\end{verbatim} \normalsize
or just
\small \begin{verbatim}
smartPtr = itk.SmartPointer[image](image.GetPointer())
\end{verbatim} \normalsize

    \subsection{TCL usage}

    \subsection{Java usage}

\section{Developer guide}

What follows is a brief description of how the WrapITK build system works, how
it can be extended, and how to write external projects.

  \subsection{WrapITK description}

     \subsubsection{Creating a CMakeLists.txt file for a wrapper library}
Each WrapITK sub-library (e.g. \verb$ITKCommonA$, or \verb$ITKAlgorithms$) lives in a
sub-directory of the WrapITK project (e.g. \verb$CommonA$ or \verb$Algorithms$) with a
\verb$CMakeLists.txt$ file that describes how that library  and language support files
(e.g. python template definitions) is to be created. Moreover, any external
project will need a similar file to describe how to create that library.

See \verb$SampleCMakeLists.txt$ in this directory for a description of each macro and
option that can appear in such a file. What follows is the usual set of commands
that will appear:

\small \begin{verbatim}
BEGIN_WRAPPER_LIBRARY("MySpatialObjectExtensions")
SET(WRAPPER_LIBRARY_DEPENDS ITKSpatialObject ITKCommonA)
SET(WRAPPER_LIBRARY_LINK_LIBRARIES ITKCommon)
WRAPPER_LIBRARY_CREATE_WRAP_FILES()
WRAPPER_LIBRARY_CREATE_LIBRARY()
\end{verbatim} \normalsize

\begin{itemize}
  \item \verb$BEGIN_WRAPPER_LIBRARY()$ sets up the environment to wrap a set of classes into a
library with a given name. This macro is defined in \verb$itkConfigWrapping.cmake$
\verb$WRAPPER_LIBRARY_DEPENDS$ stores the list of WrapITK libraries on which the
current library depends (e.g. which libraries wrap classes like \verb$Image$ or
\verb$SpatialObject$, that are going to be used in the current library). Every project
should at least depend on \verb$ITKCommonA$.

  \item \verb$WRAPPER_LIBRARY_LINK_LIBRARIES$ stores a set of other libraries to add at link
time. This can be 3rd party libraries that you will use (be sure to properly set
\verb$LINK_DIRECTORIES$ in this case), or more commonly, the ITK libraries that need to
be linked in, like \verb$ITKCommon$, \verb$ITKIO$, or other.

  \item \verb$WRAPPER_LIBRARY_CREATE_WRAP_FILES()$ scans all of the \verb$wrap_XXX.cmake$ files in the
current directory and uses the directives within to create CableSwig input files
for these classes. Information about template instantiations is also recorded
for the language support files that are created next. This macro is defined in
\verb$CreateCableSwigInputs.cmake$, and calls language support macros from
\verb$CreateLanguageSupport.cmake$.

  \item Finally, \verb$WRAPPER_LIBRARY_CREATE_LIBRARY()$ creates rules to parse the CalbeSwig
inputs and compile a wrapper library. This macro also causes various language
support files to be created (python only currently) which make it easy to load
that library in python, and which know about the template instances defined.
This macro is defined in \verb$CreateWrapperLibrary.cmake$, and calls language support
macros from \verb$CreateLanguageSupport.cmake$.
\end{itemize}

     \subsubsection{Creating wrapXXX.cmake files to wrap classes}

A \verb$wrap_XXX.cmake file$ defines a group of classes and/or template instantiations
to be wrapped. Often one such file is defined for each class wrapped, but this
is not strictly necessary.

Within such a file, directives are issued to wrap classes and particular
template instances. All of the available directives are defined and documented
in CreateCableSwigInputs.cmake. The basics are presented here:

\begin{itemize}
  \item \verb$WRAP_INCLUDE("header.h")$ -- causes the named header to be \verb$#included$ in the
generated files.

  \item \verb$WRAP_CLASS("fully_qualified::ClassName" [POINTER|POINTER_WITH_SUPERCLASS])$ --
causes a templated class to be wrapped. All namespaces must be included in the
class name, and note that no template instantiation is given. Template
instantiations are created with various \verb$WRAP$ directives, described below,
between invocations of \verb$WRAP_CLASS()$ and \verb$END_WRAP_CLASS()$.

\verb$WRAP_CLASS$ issues an implicit call to \verb$WRAP_INCLUDE("ClassName.h")$, so the header
for the wrapped class itself does not need to be manually included. To disable
this behavior, set \verb$WRAPPER_AUTO_INCLUDE_HEADERS$ to \verb$OFF$.

The final optional parameter to \verb$WRAP_CLASS$ is \verb$POINTER$ or
\verb$POINTER_WITH_SUPERCLASS$. If no options are passed, then the class is wrapped
as-is. If \verb$POINTER$ is passed, then the class and the typedef'd \verb$class::Pointer$
type is wrapped. (\verb$Class::Pointer$ had better be a \verb$SmartPointer$ instantiation, or
things won't work. This is always the case for ITK-style code.) If
\verb$POINTER_WITH_SUPERCLASS$ is provided, then \verb$class::Pointer$, \verb$class::Superclass$ and
\verb$class::Superclass::Pointer$ are all wrapped. (Again, this only works for
ITK-style code where the class has a typedef'd \verb$Superclass$, and the superclass
has Self and \verb$Pointer$ typedefs.)

  \item \verb$WRAP("mangled_suffix" "template parameters")$ -- When issued between \verb$WRAP_CLASS$
and \verb$END_WRAP_CLASS$, this command causes a particular template instantiation of
the current class to be wrapped. The parameter \verb$mangled_suffix$ is a suffix to
append to the class's name that uniquely identifies this particular template
instantiation, and "template parameters" are whatever should go between the \verb$< >$
template instantiation brackets. (Do not include the brackets.) If you are
wrapping a filter, there are simpler macros to use, which are defined at the
bottom of \verb$CreateCableSwigInputs$ and described below.

  \item \verb$WRAP_type(size)$ (where 'type' is \verb$INT$, \verb$SIGN_INT$, \verb$REAL$, \verb$VECTOR_REAL$,
\verb$COV_VECTOR_REAL$ or \verb$RGB$) -- create a template instantiation with 'size'
\verb$itk::Image$ parameters of the given pixel type. So if you are wrapping a filter
which should take two images with integral pixel types, write \verb$WRAP_INT(2)$. The
specific integral data type(s) (\verb$char$, \verb$long$, or \verb$short$ in the \verb$WRAP_INT$ case) will
be determined by the user-selected build parameters (e.g. \verb$WRAP_long$, and
\verb$WRAP_short$).

  \item \verb$WRAP_type_DIMS(size dims)$ (with \verb$type$ as above) -- Wrap a filter for certain
dimensions only. Dims should be either a semicolon-separated list of valid
dimensions, or something of the form \verb$'3+'$ to specify that the filter can be
instantiated only for three- and higher-dimensional images. Note that if the
user has not selected to wrap a given dimension at build time, a filter wrapped
with \verb$WRAP_type_DIMS$ will not be instantiated: the final dimensions wrapped are
the {/em intersection} of the user-selected dimensions and the valid dimensions
declared with \verb$WRAP_type_DIMS$.

  \item \verb$END_WRAP_CLASS()$ -- end a block of template instantiations for a particular
class.

  \item \verb$WRAP_NON_TEMPLATE_CLASS("fully_qualified::ClassName" [POINTER|POINTER_WITH_SUPERCLASS])$
 -- Same as \verb$WRAP_CLASS$, but creates a wrapper
for a non-templated class. No \verb$END_WRAP_CLASS()$ is necessary after this macro
because there is no block of template instantiating commands to close.
\end{itemize}

  \subsection{Extending or customizing WrapITK}

To minimize build times and library size, it is possible to manually prevent
various classes from being wrapped. WrapITK is divided into several
sub-libraries, each with a sub-directory: \verb$Algorithms$, \verb$BasicFilters[ABC]$,
\verb$Common[AB]$, \verb$IO$, \verb$Numerics$, \verb$SpatialObject$, and \verb$VXLNumerics$. Within these
directories are sets or \verb$wrap_XXX.cmake$ files, where \verb$XXX$ is the name of the class
(or set of classes) to be wrapped. To prevent one of these classes from being
wrapped, simply rename the file to anything that does {\em not} start with \verb$wrap_$ and
end with cmake. (E.g. append \verb$.notwrapped$ to the name.) (This is probably
unsafe to do in the \verb$Common$, \verb$Numerics$, or \verb$IO$ directories.)

To add classes to be wrapped, it is recommended that you create a simple
{\em External Project} described below. If this is out of the question, you could
create additional \verb$wrap_XXX.cmake$ files in the appropriate directory. (Read on
for instructions as to what to put in these files.)

  \subsection{External projects}

    \subsubsection{Why external projects?}

% In WrapITK/ExternalProjects there are several sample "External Projects" that
% can be built to provide additional functionality to WrapITK and to serve as a
% demonstration for how to create your own such projects. One project is an
% ITK-VTK bridge, and the other is a Python class to allow conversion from
% Numeric/Numarray/numpy matrices to ITK images (and vice-versa).

    \subsubsection{Building}
To build an external project, first ensure that WrapITK has been properly built.
Then use ccmake to configure a build directory for the external project. If
WrapITK has not been installed, you will have to manually enter the path to the
WrapITK build directory.

    \subsubsection{Usage}
Once an external project has been built, it can be tested directly from the
build tree. Start python in the external project build directory's Python
subdirectory, and run the command \verb$import ProjectConfig$ (or 
\verb$import ProjectConfig-[Debug|Release|...]$ if you were using an IDE, depending on which
build configuration was set from the IDE). This command sets up the search paths
properly so that WrapITK and the newly-created library files can be found. Then
type \verb$import ...$ (where \verb$...$ is replaced with the name of the external
project; e.g. \verb$import BufferConversion$), and use the project.

    \subsubsection{Installation}
Simply type \verb$make install$ (or run your IDE's install step) to install the
external project into the WrapITK tree (provided WrapITK has already been
installed). Now the external project can be used just like any of the other
WrapITK libraries, and it will be imported into the \verb$itk$ namespace when the
\verb$import itk$ command is issued from Python. (This can be disabled by setting
\verb$WRAPPER_LIBRARY_AUTO_LOAD$ to \verb$OFF$ in the external project's \verb$CMakeLists.txt$.)

    \subsubsection{Top-level CMakeLists for external projects}
In addition to having a set of \verb$wrap_XXX.cmake$ files and the proper
commands to read in these files and create a library (all described above), an
external project's CMakeLists file needs at least one additional command to
start it out: \verb$FIND_PACKAGE(WrapITK REQUIRED)$.

This command will cause cmake to try to find the WrapITK build/install
directory. If WrapITK has been installed, this will work on the first try.
Otherwise, you will have to set (within ccmake, or in the CMakeLists if you
prefer) the variable \verb$WrapITK_DIR$ to contain the path to the WrapITK build
directory.

    \subsubsection{BufferConversion: an example of extension for one language}

    \subsubsection{ItkVtkGlue: an example of extension for all languages, including C++}

  \subsection{Extending language support and adding more languages}

    \subsubsection{Generating target language code}

    \subsubsection{typemaps}

  \subsection{Contributing to WrapITK}

\section{Acknowledgments}

\section{Conclusion}

% \url{http://www.itk.org}
% \code{Insight/Documentation/Style.pdf}
% \section{Principles of Solar Spot Detection}
% \cite{ITKSoftwareGuide}.
% \doxygen{ImageToImageFilter}

% \small \begin{verbatim}
% \end{verbatim} \normalsize

% The {itemize} environment uses a bullet for each \item.  If you want the 
% \item's numbered, use the {enumerate} environment instead.
% \begin{itemize}
%   \item  Insight Toolkit 2.4.
%   \item  CMake 2.2
% \end{itemize}

% \ref{cthead1}

% \begin{figure}[htbp]
% \centering
% \includegraphics{cthead1}
% \caption{The input image.\label{cthead1}}
% \end{figure}

\appendix

\bibliographystyle{plain}
\bibliography{InsightJournal}
\nocite{ITKSoftwareGuide}

\end{document}

### 2006-02-14 article/Article.tex
article continuated
darcs-hash:20060214160346-2fc9d-a98f2c55f2c361c674684b8711c66e4908cde057.gz

@@
 in target languages. It become quickly frustrating for the user, especially when
-he have to spend lot of time to extend the current set of classes. Even if it is
+he has to spend lot of time to extend the current set of classes. Even if it is
 not yet complete, the WrapITK's set of classes have been highly extended. Moreover,
@@
 to create a pipeline. In WrapITK, most of the filters have the same input and output
-types. Only a few filters allow to change type. This make the types manipulated 
-by filters more consistent.
-
-  \item  The python's \verb$InsightToolkit$ module is only strucutred as a big list
-of names. This make it nearly unusable in the python interpreter. The python's
-module organization is completely changed to be more structured and flexible.
+types, and only a few filters allow to change type. This make the types manipulated 
+by filters more consistent, and the user should always be able to build his pipeline.
 
@@
 
-  \item  Names in target laguages are inconsistents.
+  \item  Names in target laguages are inconsistents. WrapITK use a strict naming
+convention which should make easier to identify the template arguments.
 
   \item  The ITK wrapping system is difficult to understand and maintain. WrapITK was
-written -- and thoroughly documented -- to be as easy as possible to understand,
+written - and thoroughly documented - to be as easy as possible to understand,
 maintain, and extend.
@@
 
-  \item  Once the ITK wrappers are built, using them from within the target languages
-is in many cases painful, forcing Python code (for example) to look a lot like
-C++ code, but nastier. In particular, template types must be hard-coded into
-every function name. WrapITK attempts to address this in Python by providing
-run-time lookup of templated types. Additionally, WrapITK ensures that
-\verb$SmartPointer$s are always returned and acceptable as input, so no bare pointers
-are ever exposed to Python. This is not the case in the standard ITK wrappers.
+  \item  The python's \verb$InsightToolkit$ module is only structured as a big
+list of names. It make it nearly unusable in the python interpreter. WrapITK
+comes with a new well designed python module easy to use in interpreter, and
+aproviding run-time lookup of templated types - thing which can't be easily done
+in C++. Additionally, WrapITK ensures that \verb$SmartPointer$s are always
+returned and acceptable as input, so no bare pointers are ever exposed to
+Python. This is not the case in the standard ITK wrappers.
 
@@
 some updating.
+
+It have been tested on Mandriva Linux, and MacOS X.
 
@@
 
-To get the last version, the user can get the last version from the darcs repository
+To get the last version from the darcs repository can be obtained
 with the command 
@@
 \url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz}.
+
+A rpm package for Mandriva Linux will be available soon.
 
@@
 either a CVS checkout of ITK or to version 2.4.1. These optional patches provide
-better support for python by providing \verb$__str__$ methods and the like.
+better support for python by providing some methods like \verb$__str__$, or methods
+for standard python sequence interface (see below).
 
@@
 After CableSwig and ITK have been (possibly patched) and built, building WrapITK
-with cmake is simple. Run ccmake in a new directory with the path to the WrapITK
+with cmake is simple. Run \verb$ccmake$ in a new directory with the path to the WrapITK
 source tree as the first argument, and provide the locations of the ITK and
@@
 self-explanatory.
+
+The project is provided with defaults build option which should OK for most of
+users. However, for specific needs, you might want to change those options:
+\begin{itemize}
+  \item \verb$WRAP_DIMS$ is the list of dimensions which will be available in the
+target languages. The dimensions must be separated by a semicolon (\verb$;$).
+By default dimensions 2 and 3 are available.
+  \item \verb$WRAP_covariant_vector_double$, \verb$OFF$ by default.
+  \item \verb$WRAP_covariant_vector_float$, \verb$ON$ by default.
+  \item \verb$WRAP_double$ \verb$OFF$, by default.
+  \item \verb$WRAP_float$ \verb$ON$, by default. Note that it is the only signed
+type selected by default, so you will have to use floats to manipulate signed
+values.
+  \item \verb$WRAP_rgb_unsigned_char$, \verb$ON$ by default.
+  \item \verb$WRAP_rgb_unsigned_short$, \verb$OFF$ by default.
+  \item \verb$WRAP_signed_char$, \verb$OFF$ by default.
+  \item \verb$WRAP_signed_long$, \verb$OFF$ by default.
+  \item \verb$WRAP_signed_short$, \verb$OFF$ by default.
+  \item \verb$WRAP_unsigned_char$, \verb$OFF$ by default.
+  \item \verb$WRAP_unsigned_long$, \verb$OFF$ by default. Some filters, like
+\verb$WatershedImageFilter$ require this type. Some filters to return to a
+wrapped type from \verb$unsigned long$ are provided, even if this option is
+set to \verb$OFF$.
+  \item \verb$WRAP_unsigned_short$, \verb$ON$ by default. \verb$unsigned short$
+is the only integer type available by default. This type have been choose rather
+than \verb$unsigned char$ to be able to manipulate 8-bits as well as 16-bits images,
+and to be able to manipulate labeled images more than 255 labels. It is still
+possible to save images with the \verb$unsigned char$ type, even if
+\verb$WRAP_unsigned_char$ is set to \verb$OFF$.
+  \item \verb$WRAP_vector_double$, \verb$OFF$ by default.
+  \item \verb$WRAP_vector_float$, \verb$ON$ by default.
+
+\end{itemize}
+
+The user should modify those options carefully: activate all the types, and/or
+add lots of dimensions will produce very large binary files which will take lots
+of memory once loaded.
 
@@
 
+Note that you should always build your project outside the source tree.
+
     \subsubsection{Install WrapITK or use it in the build tree}
+
+Once built, WrapITK can be installed or used in place.
 
@@
 simply issue the command \verb$import itk$, and you are ready to go. This
-is because WrapITK installs a pth file in the python site-packages directory so
+is because WrapITK installs a pth file in the python \verb$site-packages$ directory so
 that python knows where to find the itk scripts.
@@
 \verb$PYTHONPATH$ environment variable to contain the directory
-\verb$/path-to-WrapITK-build/Python$, add  this path to sys.paths within python, or
+\verb$/path-to-WrapITK-build/Python$, add  this path to \verb$sys.paths$ within python, or
 start python from that directory. After this, \verb$import itk$ will work
@@
 encapsulate all of the template instantiations that were created at build time.
-If three-dimensional unsigned char and unsigned short image types were created,
+If three-dimensional \verb$unsigned char$ and \verb$unsigned short$ image types were created,
 they can be accessed as follows:
 \begin{itemize}
-  \item \verb$itk.Image[itk.UC, 3]$ or \verb$itk.Image.UC3$
-  \item \verb$itk.Image[itk.US, 3]$ or \verb$itk.Image.US3$
+  \item \verb$itk.Image[itk.UC, 3]$
+  \item \verb$itk.Image[itk.US, 3]$
 \end{itemize}
+Note that the C type \verb$unsigned char$ is given with \verb$itk.UC$, and \verb$unsigned short$
+with \verb$itk.US$.
+
+The template parameters can also be put in a variable, and declared once
+in a script:
+\begin{verbatim}
+dim = 3
+pixelType = itk.UC
+imageType = itk.Image[pixelType, dim]
+
+image = imageType.New()
+\end{verbatim}
+This construction is similar to what is done in C++, and make it easy to change
+the dimension used for example - it can even be changed at run-time.
+
+A more convenient syntaxe for usage in interpreter is also available:
+\begin{itemize}
+  \item \verb$itk.Image.UC3$
+  \item \verb$itk.Image.US3$
+\end{itemize}
+\verb$itk.Image.UC3$ refere to the same class than \verb$itk.Image[itk.UC, 3]$
+but have the advantage to allow the usage of tab completion in the interpreter,
+and so let the user easily know which template arguments he can use.
+However, this notation is more rigid than the one above and won't let the user
+specify the type and the type and the dimension used in a single place, and thus,
+should be use only in interpreter.
 
@@
   \item or \verb$itk.ImageFileReader[itk.Image.UC3]$
-  \item or even \verb$itk.ImageFileReader[image]$ if \verb$image$ is of type \verb$UC3$.
+  \item or \verb$itk.ImageFileReader.IUC3$
+  \item or \verb$itk.ImageFileReader[imageType]$
+  \item or even with an instance of class used as template parameter: \verb$itk.ImageFileReader[image]$.
 \end{itemize}
 This makes it easy to write generic routines which
-can deal with any input image type.
+can deal with any input image type. For example, an function which take an image
+as parameter and write it to a file without having to give the image type can be:
+\begin{verbatim}
+def write( image, fileName ) :
+    writer = itk.ImageFileWriter[ image ].New()
+    writer.SetFileName( fileName )
+    writer.SetInput( image )
+    writer.Update()
+\end{verbatim}
 
@@
 write:
-\small \begin{verbatim}
+\begin{verbatim}
 adder = itk.AddImageFilter[...].New()
-adder.SetInput1(inputA)
-adder.SetInput2(inputB)
-\end{verbatim} \normalsize
+adder.SetInput1( readerA.GetOutput() )
+adder.SetInput2( readerB.GetOutput() )
+\end{verbatim}
 or you could write
-\small \begin{verbatim}
-adder = itk.AddImageFilter[...].New(inputA, inputB)
-\end{verbatim} \normalsize
+\begin{verbatim}
+adder = itk.AddImageFilter[...].New( readerA.GetOutput(), readerB.GetOutput() )
+\end{verbatim}
+or even
+\begin{verbatim}
+adder = itk.AddImageFilter[...].New( readerA, readerB )
+\end{verbatim}
+In that case, \verb$New$ will use the \verb$GetOutput()$ of the object if it
+exist to get the image, and the inputs of the new filter.
 
@@
 following:
-\small \begin{verbatim}
+\begin{verbatim}
 itk.ImageFileWriter[image].New(image, FileName="foo.tif")
-\end{verbatim} \normalsize
+\end{verbatim}
 or
-\small \begin{verbatim}
+\begin{verbatim}
 itk.ImageFileWriter[image].New(Input=image, FileName="foo.tif")
-\end{verbatim} \normalsize
+\end{verbatim}.
+
+\end{itemize}
+
+With that notation, the \verb$write$ function becomes more simple:
+\begin{verbatim}
+def write( image, fileName ) :
+    writer = itk.ImageFileWriter[ image ].New( image, FileName=fileName )
+    writer.Update()
+\end{verbatim}
+
+and, more important, most of classes can be instanciated and parametered in one line,
+which make ITK less verbose, and a lots more easy to use in the interpreter.
+
+     \subsubsection{Python specific functions}
+
+Some convenient functions are provided with the itk module. They all begin with a lower
+case character to clearly show they are not part of ITK.
+\begin{itemize}
+  \item \verb$itk.image( object )$ try to return an image from the object given in
+parameter. This function is used in most of the next functions to allow the user to
+pass an image or a filter.
+
+  \item \verb$itk.range( object )$ return the range of values of an image in a tuple.
+\verb$object$ can be an image or a filter. In case of a filter, \verb$itk.image()$ is used
+to get the output image of the filter. The function update the pipeline by calling
+\verb$UpdateOutputInformation()$ and \verb$Update()$.
+
+Example:
+\begin{verbatim}
+1> import itk
+
+2> reader = itk.ImageFileReader.IUC2.New(FileName="cthead1.png")
+
+3> itk.range(reader)
+3> (0, 255)
+\end{verbatim}
+
+  \item \verb$itk.size( object )$ return the size of an image.
+\verb$object$ can be an image or a filter. In case of a filter, \verb$itk.image()$ is used
+to get the output image of the filter. The function update only the information of the
+pipeline, by calling \verb$UpdateOutputInformation()$, but don't trigger a full update
+of the pipeline.
+
+Example:
+\begin{verbatim}
+4> itk.size(reader)
+4> <C itk::Size<(2)> instance at _d40b8a09_p_itk__SizeT2_t>
+
+5> print itk.size(reader)
+<Size [256, 256]>
+
+6> list(itk.size(reader))
+6> [256, 256]
+\end{verbatim}
+Note that commands 5 and 6 can be used only with the optional patches.
+
+  \item \verb$itk.template( object )$ returns the template class and parameters
+of a class or instance of this class.
+
+Example:
+\begin{verbatim}
+7> itk.template(reader)
+7> (<itkTemplate itk::ImageFileReader>, (<class 'itkImage.itkImageUC2'>,))
+\end{verbatim}
+
+  \item \verb$itk.write( object, fileName )$ write an image in a file, without
+having to pass the image type.
+\verb$object$ can be an image or a filter. In case of a filter, \verb$itk.image()$ is used
+to get the output image of the filter. The function update the pipeline by calling
+\verb$UpdateOutputInformation()$ and \verb$Update()$.
+
+Example:
+\begin{verbatim}
+8> itk.write(reader, 'out.png')
+\end{verbatim}
+
+  \item \verb$itk.show()$, \verb$itk.show2D()$ and \verb$itk.show3D()$ are used to
+display images. \verb$itk.show2D()$ requires to have \verb$imview$ installed.
+\verb$itk.show3D()$ requires to have ItkVtk, PyQt, and iPython installed, and to use
+iPython with the \verb$-qthread$ option.
+
+\verb$itk.show()$ call the best viewer according to the image type.
+
+\verb$itk.show2D()$
+can be called with a 3D image as parameter to show the image slice by slice.
+
+\verb$itk.show3D()$ display a volumic rendering of the image. See Figure~\ref{screenshot}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=0.18]{capture1}
+\caption{A screenshot of WrapITK in action.\label{screenshot}}
+\end{figure}
+
+  \item \verb$itk.strel$
 
@@
 
+Write me.
+
     \subsection{Java usage}
+
+Write me.
 

### 2006-02-15 ExternalProjects/ItkVtk/Wrapping/Python/itkvtk.py
rename ItkVtk to avoid conflict between ItkVtk.py and itkvtk.py on non-case sensitive filesystems
darcs-hash:20060215150559-2fc9d-f14651fa50040990c65cf2a75a8ccefc5cd78845.gz

@@ -1,13 +1,0 @@
-
-import itk, vtk
-import ItkVtk
-
-names = [name for name in dir(ItkVtk) if not name.startswith("__")]
-for name in names :
-    setattr(itk, name, ItkVtk.__dict__[name])
-    
-# some cleanup
-del itk, vtk, ItkVtk, names, name
-
-# also keep ItkVtk members in that namespace
-from ItkVtk import *

### 2006-02-15 ExternalProjects/ItkVtkGlue/Wrapping/Python/itkvtk.py

@@ -1,0 +1,13 @@
+
+import itk, vtk
+import ItkVtkGlue
+
+names = [name for name in dir(ItkVtkGlue) if not name.startswith("__")]
+for name in names :
+    setattr(itk, name, ItkVtkGlue.__dict__[name])
+    
+# some cleanup
+del itk, vtk, ItkVtkGlue, names, name
+
+# also keep ItkVtkGlue members in that namespace
+from ItkVtkGlue import *

### 2006-02-15 article/Article.tex
add some TODO items
darcs-hash:20060214161432-2fc9d-4937c4638cee0e759259a7a11bc4eeb8730621fc.gz
some small additions to the article
darcs-hash:20060215170349-2fc9d-56eeceaa2bc5a8f4817a3bf58073e27261c9f78e.gz

@@
 
+TODO: provide more binary packages - for mac and windows.
+
     \subsubsection{CableSwig}
@@
 
-     \subsubsection{Basic Usage}
+TODO: alternatively, the submodules may be imported
 
+     \subsubsection{Template usage}
 Most class in the itk python module are "template proxy classes" that
@@
   \item or \verb$itk.ImageFileReader[imageType]$
-  \item or even with an instance of class used as template parameter: \verb$itk.ImageFileReader[image]$.
+  \item or even with an instance of the class used as template parameter: \verb$itk.ImageFileReader[image]$.
 \end{itemize}
@@
 
-Each class has a \verb$New()$ method which returns a smart pointer to that class. The
+     \subsubsection{The {\em New()} method}
+
+Losts of classes have a \verb$New()$ method which returns a smart pointer to that class. The
 \verb$New()$ method in python has some additional features:
@@
 
-     \subsubsection{Python specific functions}
+     \subsubsection{Python specific functions in the {\em itk} module}
 
@@
 
+  \item \verb$itk.auto_progress$
+
 \end{itemize}
@@
      \subsubsection{Advanced Features}
+
 As an extra bonus, it is possible to view the doxygen documentation for each
@@
 
+TODO: rename ItkVtk to ItkVtkGlue to avoid problems wiht non-case sensitive filesystems.
+
   \subsection{Extending language support and adding more languages}
@@
   \subsection{Contributing to WrapITK}
+
+- test
+- Work on tcl, java, and others
+- add more classes
+
+talk about darcs
 

### 2006-02-15 Python/itkBase.py
fix itkBase.py to (with luck) deal with loader path issues.
darcs-hash:20060215195543-733a7-5e76d302475d1ad57bed1c6449db22b062830f70.gz

@@ -98,7 +98,7 @@ def LoadModule(name, namespace = None):
 def LoadSWIGLibrary(moduleName):
   """Do all the work to set up the environment so that a SWIG-generated library
   can be properly loaded. This invloves setting paths, etc., defined in itkConfig."""
-  import sys, imp, itkConfig
+  import os, sys, imp, itkConfig
   
   # To share symbols across extension modules, we must set
   #     sys.setdlopenflags(dl.RTLD_NOW|dl.RTLD_GLOBAL)
@@ -123,6 +123,10 @@ def LoadSWIGLibrary(moduleName):
   # libraries or other swig-generated scripts.
   sys.path.insert(1, itkConfig.swig_lib)
   sys.path.insert(1, itkConfig.swig_py)
+  # also change to the swig_lib directory so that the loader can find non-module
+  # library files like SwigRuntimePython linked into the python module that's loaded.
+  old_cwd = os.getcwd()
+  os.chdir(itkConfig.swig_lib)
   
   # find and load the module
   try:
@@ -135,6 +139,7 @@ def LoadSWIGLibrary(moduleName):
     # and restore environment to normalcy
     sys.path.remove(itkConfig.swig_lib)
     sys.path.remove(itkConfig.swig_py)
+    os.chdir(old_cwd)
     if oldflags and hasattr(sys, 'setdlopenflags'):
       # try to avoid raising an exception, because if we do, the import exception
       # that might have occured above in the try block won't get reported.

### 2006-02-16 Python/itkBase.py
Fix problem in itkBase: if other modules were loaded before 'import itk' then the itk namespace would be missing those symbols.
darcs-hash:20060216181728-733a7-58f7571b4d9af2a017ee53084bfb9a6b7a3ea6de.gz

@@ -19,8 +19,19 @@ def LoadModule(name, namespace = None):
   this_module = sys.modules.setdefault(name, imp.new_module(name))
  
   # if this library and it's template instantiations have already been loaded
-  # into sys.modules, bail out
-  if hasattr(this_module, '__templates_loaded') : return
+  # into sys.modules, bail out after loading the defined symbols into 'namespace'
+  if hasattr(this_module, '__templates_loaded'):
+    if namespace:
+        swig = namespace.setdefault('swig', imp.new_module('swig'))
+        swig.__dict__.update(this_module.swig.__dict__)
+        symbols = [(k, v) for k, v in this_module.__dict__.items() 
+          if not (k.startswith('_') or k == 'swig')]
+        # don't worry about overwriting the symbols in namespace -- any common
+        # symbols should be of type itkTemplate, which is a singleton type. That
+        # is, they are all identical, so replacing one with the other isn't a
+        # problem.
+        namespace.update(symbols)
+    return
   
   # We're definitely going to load the templates. We set templates_loaded here
   # instead of at the end of the file to protect against cyclical dependencies

### 2006-02-17 Python/itk.py
never import itk in itkTemplate to allow to load only a part of itk
darcs-hash:20060217174343-2fc9d-0b43734b68faf86f4ae9f50087fc69dfb95113c8.gz

@@ -23,9 +23,10 @@ del itkBase, itkConfig, os
 # new features introduced by itk module
 # each new feature use a name in lower case
 
-# set this variable to True to automatically add an progress display to the newly created
-# filter.
-auto_progress = False
+def auto_progress( b ):
+  import itkTemplate
+  itkTemplate.auto_progress = b
+  
 
 # Function to print itk object info
 import sys
@@ -68,16 +69,7 @@ def strel(imageClass, radius=1) :
   return st
   
 # return an image
-def image(input) :
-    try :
-	img = input.GetOutput()
-    except AttributeError :
-	img = input
-    try :
-	img = img.GetPointer()
-    except AttributeError :
-	pass
-    return img
+from itkTemplate import image
 
 # return the template of a class and its parameters
 def template(cl) :

### 2006-02-17 Python/itkTemplate.py

@@ -288,12 +288,12 @@ class itkTemplate(object):
 
 # create a new New function which accepts parameters
 def New(self, *args, **kargs) :
-  import itk, sys
+  import sys
   
   newItkObject = self.__New_orig__()
   
   # try to get the images from the filters in args
-  args = [itk.image(arg) for arg in args]
+  args = [image(arg) for arg in args]
   
   # args without name are filter used to set input image
   #
@@ -345,7 +345,8 @@ def New(self, *args, **kargs) :
     attrib(value)
 
   # now, try to add observer to display progress
-  if itk.auto_progress :
+  if auto_progress :
+    import ITKPyUtils, ITKCommonA
     try :
       def progress() :
         clrLine = "\033[2000D\033[K"
@@ -355,9 +356,9 @@ def New(self, *args, **kargs) :
         if p == 1 :
           print >> sys.stderr, clrLine,
 
-      command = itk.PyCommand.New()
+      command = ITKPyUtils.PyCommand.New()
       command.SetCommandCallable(progress)
-      newItkObject.AddObserver(itk.ProgressEvent(), command.GetPointer())
+      newItkObject.AddObserver(ITKCommonA.ProgressEvent(), command.GetPointer())
     except :
       # it seems that something goes wrong...
       # as this feature is designed for prototyping, it's not really a problem
@@ -367,3 +368,18 @@ def New(self, *args, **kargs) :
   return newItkObject
 
 
+# set this variable to True to automatically add an progress display to the newly created
+# filter.
+auto_progress = False
+
+
+def image(input) :
+    try :
+	img = input.GetOutput()
+    except AttributeError :
+	img = input
+    try :
+	img = img.GetPointer()
+    except AttributeError :
+	pass
+    return img

### 2006-02-17 Python/Tests/itk-functions.py
rename classFromObject to class_
darcs-hash:20060217175830-2fc9d-f70cea8f9a6cc5cbc789604e8e95e7478f3d8bd5.gz

@@ -15,10 +15,10 @@ reader = ReaderType.New(FileName=fileName)
 itk.echo(reader)
 itk.echo(reader, sys.stdout)
 
-# test classFromObject
-assert itk.classFromObject(reader) == ReaderType
-assert itk.classFromObject(reader.GetPointer()) == ReaderType
-assert itk.classFromObject("dummy") == str
+# test class_
+assert itk.class_(reader) == ReaderType
+assert itk.class_(reader.GetPointer()) == ReaderType
+assert itk.class_("dummy") == str
 
 # test template
 assert itk.template(ReaderType) == (itk.ImageFileReader, (IType,))

### 2006-02-17 Python/itk.py

@@ -54,7 +54,7 @@ def size(imageOrFilter) :
 def strel(imageClass, radius=1) :
   # be sure to have an image class
   imageClass = image(imageClass)
-  imageClass = classFromObject(imageClass)
+  imageClass = class_(imageClass)
   (tpl, param) = template(imageClass)
   if tpl != Image :
     raise ValueError, "imageClass must be an Image class or object"
@@ -74,7 +74,7 @@ from itkTemplate import image
 # return the template of a class and its parameters
 def template(cl) :
   from itkTemplate import itkTemplate
-  return itkTemplate.__class_to_template__[classFromObject(cl)]
+  return itkTemplate.__class_to_template__[class_(cl)]
   
 # return ctype
 def ctype(s) :
@@ -85,7 +85,7 @@ def ctype(s) :
   return ret
   
 # return a class from an instance
-def classFromObject(obj) :
+def class_(obj) :
   import inspect
   if inspect.isclass(obj) :
     # obj is already a class !

### 2006-02-17 Python/itkTemplate.py
do not display the full repr of the class - its name is enough
darcs-hash:20060217181122-2fc9d-6333c1059045f4b6ad2a2891b7fc2a86904cba29.gz

@@ -348,11 +348,12 @@ def New(self, *args, **kargs) :
   if auto_progress :
     import ITKPyUtils, ITKCommonA
     try :
+      repr_str = repr(self).split("'")[1].split(".")[1]
       def progress() :
         clrLine = "\033[2000D\033[K"
-        # newItkObject is kept referenced with a closure
+        # newItkObject and repr_str are kept referenced with a closure
         p = newItkObject.GetProgress()
-        print >> sys.stderr, clrLine+"%s: %f" % (repr(self), p),
+        print >> sys.stderr, clrLine+"%s: %f" % (repr_str, p),
         if p == 1 :
           print >> sys.stderr, clrLine,
 

### 2006-02-17 Python/itkTemplate.py
use self.__name__ directly instead of the useless substring of repr
darcs-hash:20060217181409-2fc9d-873629918189a23f046c69e6d87869c0c64e92fb.gz

@@ -348,12 +348,11 @@ def New(self, *args, **kargs) :
   if auto_progress :
     import ITKPyUtils, ITKCommonA
     try :
-      repr_str = repr(self).split("'")[1].split(".")[1]
       def progress() :
         clrLine = "\033[2000D\033[K"
-        # newItkObject and repr_str are kept referenced with a closure
+        # newItkObject is kept referenced with a closure
         p = newItkObject.GetProgress()
-        print >> sys.stderr, clrLine+"%s: %f" % (repr_str, p),
+        print >> sys.stderr, clrLine+"%s: %f" % (self.__name__, p),
         if p == 1 :
           print >> sys.stderr, clrLine,
 

### 2006-02-17 article/Article.tex
add description for auto_progress
darcs-hash:20060217182403-2fc9d-0c65d4ee2e971dc17ed6471bf04501617758bff1.gz

@@
 
-  \item \verb$itk.auto_progress$
+  \item \verb$itk.auto_progress( b )$ is used to automatically add a progress report
+to all the newly created filters. \verb$b$ must be \verb$True$ or \verb$False$. If
+\verb$b$ is true, a line like
+\begin{verbatim}
+itkMedianImageFilterIF2IF2: 0.109990
+\end{verbatim}
+is displayed on the standard output. 
+While prototyping, it is a convenient way for the user to know if
+the execution time will be short or if he can do something more useful than waiting
+for the filter to complete (like having a cup of tea).
 

### 2006-02-17 article/Article.tex
add itk.class_ description
darcs-hash:20060217182957-2fc9d-d29bf24d5191d32d9a34f82bd3cd08a5ab7b2b38.gz

@@
 
+  \item \verb$itk.class_( object )$ return the class of an object. The \verb$__class__$
+attribute is often not what the user want with ITK. \verb$itk.class_$ is a convenient
+function to get the class of an ITK object.
+
+Note that it is called \verb$class_$ and not \verb$class$, because \verb$class$ is a
+reseved word in python.
+
+Example:
+\begin{verbatim}
+10> median.__class__
+10> <class 'itkMedianImageFilter.itkMedianImageFilterIF2IF2_PointerPtr'>
+
+11> itk.class_(median)
+11> <class 'itkMedianImageFilter.itkMedianImageFilterIF2IF2'>
+\end{verbatim}
+
 \end{itemize}

### 2006-02-17 article/Article.tex
add the command to the auto_progress example
darcs-hash:20060217183059-2fc9d-92bc72e412521871f20a27816d408c42cf37ec2a.gz
begin sequence chapter
darcs-hash:20060217184412-2fc9d-0120d88273cf428ea451546027c5718120bb2395.gz

@@
 
+     \subsubsection{Use python sequences instead of ITK objects}
+
+To set the radius of a \verb$MedianImageFilter$ object, for example, the user have to
+create a \verb$Size$ object and use it as argument of the \verb$SetRadius()$ method.
+\begin{verbatim}
+12> radius = itk.Size[2]()
+
+13> radius.SetElement(0, 3)
+
+14> radius.SetElement(1, 5)
+
+15> median.SetRadius(radius)
+\end{verbatim}.
+
+Note that the \verb$SetElement()$ method doesn't check the bound of the object, and thus
+is unsafe. The following code is executed, and can lead to a segmentation fault.
+
+\begin{verbatim}
+16> radius.SetElement(1000, 5)
+\end{verbatim}.
+
+A more safe and convenient way to do that, if you have installed the optional patch,
+is to use the standard python list interface.
+
+\begin{verbatim}
+17> radius[0] = 3
+
+18> radius[1] = 5
+\end{verbatim}.
+
+This time, a bound check is performed, and the user is not able to use an invalid index.
+
+\begin{verbatim}
+20> radius[2] = 1
+---------------------------------------------------------------------------
+exceptions.IndexError                                Traceback (most recent call last)
+
+/home/glehmann/src/contrib-itk/regionalExtrema/<ipython console>
+
+/home/glehmann/src/contrib-itk/regionalExtrema/itkSize.py in __setitem__(*args)
+
+IndexError: /usr/include/InsightToolkit/Common/itkSize.h:202:
+itk::ERROR: Size: index out of range
+\end{verbatim}.
+
      \subsubsection{Python specific functions in the {\em itk} module}
@@
 to all the newly created filters. \verb$b$ must be \verb$True$ or \verb$False$. If
-\verb$b$ is true, a line like
+\verb$b$ is true, something like
 \begin{verbatim}
+9> median.Update()
 itkMedianImageFilterIF2IF2: 0.109990

### 2006-02-21 article/Article.tex
complete python sequence part
darcs-hash:20060221125536-2fc9d-dfcf2572a08765de3ca75bbfcd41eea75535f69e.gz

@@
 
-     \subsubsection{Use python sequences instead of ITK objects}
+     \subsubsection{Python sequences and ITK}
 
@@
 \end{verbatim}.
+
+Even if it's a safe method, it is still not really convenient.
+
+Instead of using \verb$Size$ object, it is possible to use python sequences, like lists
+and tuple.
+
+\begin{verbatim}
+21> median.SetRadius([3, 5])
+
+22> median.SetRadius((3, 5))
+\end{verbatim}.
+
+Also, with the optional patches, some itk object can be converted to python sequences.
+
+\begin{verbatim}
+22> median.GetRadius()
+22> <C itk::Size<(2)> instance at _58b40f09_p_itk__SizeT2_t>
+
+23> list(median.GetRadius())
+23> [3, 5]
+
+24> tuple(median.GetRadius())
+24> (3, 5)
+\end{verbatim}.
+
+To set the same radius for all dimensions, it is possible to use the \verb$*$ python
+sequence operator - that way, it is possible to write code independant of dimension.
+
+\begin{verbatim}
+25> median.SetRadius( [3]*2 )
+\end{verbatim}.
+
+Or a simple number can also be used.
+
+\begin{verbatim}
+26> median.SetRadius( 3 )
+\end{verbatim}.
+
+Here is the list of itk classes which can currently be substituted by python sequences:
+\begin{itemize}
+  \item \verb$CovariantVector$
+  \item \verb$FixedArray$
+  \item \verb$Index$
+  \item \verb$Offset$
+  \item \verb$Size$
+  \item \verb$Vector$
+\end{itemize}
 
@@
 \includegraphics[scale=0.18]{capture1}
-\caption{A screenshot of WrapITK in action.\label{screenshot}}
+\caption{A screenshot of WrapITK in action with python.\label{screenshot}}
 \end{figure}

### 2006-02-21 article/Article.tex
small fixes
darcs-hash:20060221211128-2fc9d-cbf936c604ae24e517cbc0da3420d87d43f0f5d9.gz

@@
 % snail-mail address if you like.
-\author{Ga\"etan Lehmann{$^1$} {\small{and}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
+\author{Ga\"etan Lehmann{$^1$}{\small{,}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
 \authoraddress{{$^1$}Unit\'e de Biologie du D\'eveloppement et de la Reproduction, Institut National de la Recherche Agronomique, 78350 Jouy-en-Josas, France\\
@@
 
-A \verb$wrap_XXX.cmake file$ defines a group of classes and/or template instantiations
+A \verb$wrap_XXX.cmake$ file defines a group of classes and/or template instantiations
 to be wrapped. Often one such file is defined for each class wrapped, but this
@@
 template instances. All of the available directives are defined and documented
-in CreateCableSwigInputs.cmake. The basics are presented here:
+in \verb$CreateCableSwigInputs.cmake$. The basics are presented here:
 
@@
 ITK-style code where the class has a typedef'd \verb$Superclass$, and the superclass
-has Self and \verb$Pointer$ typedefs.)
+has \verb$Self$ and \verb$Pointer$ typedefs.)
 
@@
 bottom of \verb$CreateCableSwigInputs$ and described below.
+
+  \item \verb$COND_WRAP("mangled_suffix" "template parameters" "type list")$
 

### 2006-02-22 article/Article.tex
rename COND_WRAP to WRAP_TYPES
darcs-hash:20060221211616-2fc9d-c3424e877108e660679eb550e61e41e9f04f1170.gz
rename WRAP to WRAP_TEMPLATE, as suggested by Zach
darcs-hash:20060222121542-2fc9d-ee33a59ee01e853026c3285d9624ff23785c8874.gz

@@
 
-  \item \verb$WRAP("mangled_suffix" "template parameters")$ -- When issued between \verb$WRAP_CLASS$
+  \item \verb$WRAP_TEMPLATE("mangled_suffix" "template parameters")$ -- When issued between \verb$WRAP_CLASS$
 and \verb$END_WRAP_CLASS$, this command causes a particular template instantiation of
@@
 
-  \item \verb$COND_WRAP("mangled_suffix" "template parameters" "type list")$
+  \item \verb$WRAP_TYPES("mangled_suffix" "template parameters" "type list")$
 

### 2006-02-22 article/Article.tex
rename WRAP_TYPES to WRAP_TEMPLATE_IF_TYPE and WRAP_DIMS to WRAP_TEMPLATE_IF_DIMS
darcs-hash:20060222123323-2fc9d-4524f12d07b354b6bc5562a4ed882ff28cc29f48.gz
rename WRAP_* to WRAP_IMAGE_FILTER_*
darcs-hash:20060222162353-2fc9d-a461a3842ef9ea31c759989cdc9e562a65cd8a9c.gz

@@
 \begin{itemize}
-  \item \verb$WRAP_DIMS$ is the list of dimensions which will be available in the
+  \item \verb$WRAP_TEMPLATE_IF_DIMS$ is the list of dimensions which will be available in the
 target languages. The dimensions must be separated by a semicolon (\verb$;$).
@@
 
-  \item \verb$WRAP_TYPES("mangled_suffix" "template parameters" "type list")$
+  \item \verb$WRAP_TEMPLATE_IF_TYPES("mangled_suffix" "template parameters" "type list")$
 
@@
 \verb$itk::Image$ parameters of the given pixel type. So if you are wrapping a filter
-which should take two images with integral pixel types, write \verb$WRAP_INT(2)$. The
-specific integral data type(s) (\verb$char$, \verb$long$, or \verb$short$ in the \verb$WRAP_INT$ case) will
+which should take two images with integral pixel types, write \verb$WRAP_IMAGE_FILTER_INT(2)$. The
+specific integral data type(s) (\verb$char$, \verb$long$, or \verb$short$ in the \verb$WRAP_IMAGE_FILTER_INT$ case) will
 be determined by the user-selected build parameters (e.g. \verb$WRAP_long$, and

### 2006-02-26 Python/itkBase.py
Code cleanup, especially for python
darcs-hash:20060226221916-733a7-35445ce0e46540651ea6559ac431657b3ffdc0d1.gz

@@ -1,5 +1,4 @@
-SILENT = 0; WARN = 1; ERROR = 2
-DebugLevel = WARN
+import os, sys, imp, itkConfig, itkTemplate
 
 def LoadModule(name, namespace = None):
   """This function causes a SWIG module to be loaded into memory after its dependencies
@@ -13,7 +12,6 @@ def LoadModule(name, namespace = None):
   'swig' sub-module. If the namespace parameter is provided, this information will
   be placed in a sub-module named 'swig' therein as well. This latter submodule
   will be created if it does not already exist."""
-  import sys, imp, itkTemplate
   
   # find the module's name in sys.modules, or create a new module so named
   this_module = sys.modules.setdefault(name, imp.new_module(name))
@@ -32,6 +30,8 @@ def LoadModule(name, namespace = None):
         # problem.
         namespace.update(symbols)
     return
+  
+  if itkConfig.ImportCallback: itkConfig.ImportCallback(name)
   
   # We're definitely going to load the templates. We set templates_loaded here
   # instead of at the end of the file to protect against cyclical dependencies
@@ -55,7 +55,8 @@ def LoadModule(name, namespace = None):
   # SWIG-generated modules have 'Python' appended. Only load the SWIG module if
   # we haven't already.
   swigModuleName = name + "Python"
-  if not swigModuleName in sys.modules: module = LoadSWIGLibrary(swigModuleName)
+  loader = LibraryLoader()
+  if not swigModuleName in sys.modules: module = loader.load(swigModuleName)
   
   # OK, now the modules on which this one depends are loaded and template-instantiated,
   # and the SWIG module for this one is also loaded.
@@ -106,56 +107,69 @@ def LoadModule(name, namespace = None):
             DebugPrintError("Namespace already has a value for %s, which is not class %s. Overwriting old value." %(pyClassName, cppClassName))
           namespace[pyClassName] = swigClass
   
-def LoadSWIGLibrary(moduleName):
+def DebugPrintError(error):
+  if itkConfig.DebugLevel == itkConfig.WARN:
+    print >> sys.stderr, error
+  elif itkConfig.DebugLevel == itkConfig.ERROR:
+    raise RuntimeError(error)
+
+class LibraryLoader(object):
   """Do all the work to set up the environment so that a SWIG-generated library
[…]

### 2006-02-27 CommonA/itkConstantBoundaryConditionStub.h
Fix (hopefully) MultiThreader and BoundaryCondition issues with __stdcall and __declspec on windows.
darcs-hash:20060227024141-733a7-8cd5f4808d4345ccb60b1199962d06ddd0f6523f.gz

@@ -1,0 +1,56 @@
+#if !(defined(CABLE_CONFIGURATION) && defined(WIN32))
+// gcc-xml cannot be allowed to see the full ConstantBoundaryCondition header on 
+// windows. If we're not gcc_xml or not on windows, just pass through to the
+// proper header.
+#include "itkConstantBoundaryCondition.h"
+#else
+// Here follows the restricted header made available just to gcc-xml on windows.
+// The problem we are working around is the fact that on windows, the 
+// NumericTraits<PixelType>::Zero values are declared as __declspec(dllimport),
+// which gcc-xml and cswig can't deal with properly. So we hide that stuff in
+// these restricted headers.
+
+#ifndef __itkConstantBoundaryCondition_h
+#define __itkConstantBoundaryCondition_h
+#include "itkNeighborhood.h"
+#include "itkNumericTraits.h"
+#include "itkImageBoundaryCondition.h"
+
+namespace itk
+{
+template<class TImage>
+class ITK_EXPORT ConstantBoundaryCondition
+  : public ImageBoundaryCondition<TImage>
+{
+public:
+  typedef ConstantBoundaryCondition Self;
+  typedef ImageBoundaryCondition<TImage> Superclass;
+  typedef typename Superclass::PixelType PixelType;
+  typedef typename Superclass::PixelPointerType PixelPointerType;
+  typedef typename Superclass::IndexType IndexType;
+  typedef typename Superclass::OffsetType OffsetType;
+  typedef typename Superclass::NeighborhoodType NeighborhoodType;
+    
+  typedef typename Superclass::NeighborhoodAccessorFunctorType 
+                                 NeighborhoodAccessorFunctorType;
+
+  itkStaticConstMacro(ImageDimension, unsigned int,Superclass::ImageDimension);
+
+  ConstantBoundaryCondition();
+  virtual PixelType operator()(const OffsetType&,
+                               const OffsetType&,
+                               const NeighborhoodType *) const;
+  virtual PixelType operator()(
+      const OffsetType& ,
+      const OffsetType& ,
+      const NeighborhoodType *,
+      const NeighborhoodAccessorFunctorType & ) const;  
+  void SetConstant(const PixelType &c);
+  /** Get the value of the constant. */
+  const PixelType &GetConstant() const;  
+};
+
+} // end namespace itk
+
+#endif // ifndef stuff
+#endif // end if CABLE_CONFIGURATION and WIN32

### 2006-02-27 CommonA/itkMultiThreaderStub.h

@@ -1,0 +1,79 @@
+#if !(defined(CABLE_CONFIGURATION) && defined(WIN32))
+// gcc-xml cannot be allowed to see the full MultiThreader header on 
+// windows. If we're not gcc_xml or not on windows, just pass through to the
+// proper header.
+#include "itkMultiThreader.h"
+#else
+// Here follows the restricted header made available just to gcc-xml on windows.
+// The problem we are working around is the fact that on windows, the 
+// ThreadFunctionType (defined in the full header) looks like this 
+// unsigned long (__stdcall *)(void*)
+// Unfortunately, gcc_xml and cswig can't properly wrap __stdcall functions,
+// causing compile errors.
+#ifndef __itkMultiThreader_h
+#define __itkMultiThreader_h
+
+#include "itkObject.h"
+#include "itkMutexLock.h"
+
+namespace itk
+{
+#ifdef ITK_USE_SPROC
+#define ITK_MAX_THREADS              128
+#endif
+#ifdef ITK_USE_PTHREADS
+#define ITK_MAX_THREADS              128
+#endif
+#ifdef ITK_USE_WIN32_THREADS
+#define ITK_MAX_THREADS              128
+#endif
+#ifdef __CYGWIN__
+#undef ITK_MAX_THREADS
+#define ITK_MAX_THREADS 128 
+#endif
+#if defined(__MINGW32__)
+#undef ITK_MAX_THREADS
+#define ITK_MAX_THREADS 1 
+#endif
+#if defined(__sgi) && defined(_COMPILER_VERSION) && _COMPILER_VERSION <= 730
+#undef ITK_MAX_THREADS
+#define ITK_MAX_THREADS 1 
+#endif
+#ifndef ITK_MAX_THREADS
+#define ITK_MAX_THREADS 1
+#endif
+
+class  MultiThreader : public Object 
+  {
+public:
+    /** Standard class typedefs. */
+    typedef MultiThreader         Self;
+    typedef Object  Superclass;
+    typedef SmartPointer<Self>  Pointer;
+    typedef SmartPointer<const Self>  ConstPointer;
+    itkNewMacro(Self);  
+    itkTypeMacro(MultiThreader, Object);
+    itkSetClampMacro( NumberOfThreads, int, 1, ITK_MAX_THREADS );
+    itkGetMacro( NumberOfThreads, int );
+    static void SetGlobalMaximumNumberOfThreads(int val);
+    static int  GetGlobalMaximumNumberOfThreads();
[…]

### 2006-02-28 article/Article.tex
Code cleaning and re-organization
darcs-hash:20060225111055-733a7-036ae5e88e995c642252eb1b668981fc5daa5a4c.gz
add ImportCallback doc
darcs-hash:20060228161719-2fc9d-a84297098857aeac1d5cae23f341ddf4fb1c9f8f.gz

@@
 
+\verb$itk$ module can be very long to import. The \verb$itkConfig$ module define
+a \verb$ImportCallback$ method which will be called when each sub module is
+imported in the import process. \verb$ImportCallback$ can be customized to report the
+progress status of the import process. It must be a function that can take
+the name of the library being imported as a parameter. Here is an example of a very
+basic callback function which display the name of the submodule being imported on
+the standard error output.
+\small \begin{verbatim}
+import sys, itkConfig
+def stderr_callback(name):
+  print >> sys.stderr, name
+itkConfig.ImportCallback = stderr_callback
+import itk
+\end{verbatim} \normalsize
+
     \subsection{TCL usage}
@@
   \item \verb$BEGIN_WRAPPER_LIBRARY()$ sets up the environment to wrap a set of classes into a
-library with a given name. This macro is defined in \verb$itkConfigWrapping.cmake$
+library with a given name. This macro is defined in \verb$ConfigureWrapping.cmake$
 \verb$WRAPPER_LIBRARY_DEPENDS$ stores the list of WrapITK libraries on which the

### 2006-02-28 article/Article.tex
begin MedianImageFilter explanation
darcs-hash:20060228170203-2fc9d-49b5cc9c9c1b31064126c45418c4c47188fa3982.gz

@@
 Within such a file, directives are issued to wrap classes and particular
-template instances. All of the available directives are defined and documented
+template instances.
+
+WrapITK define several macros and variable designed to:
+\begin{itemize}
+  \item make creation of wrappers easy. The syntax is simple enough to get in quickely.
+  \item make wchoice of template arguments explicit. It should be easy to understand
+the idea of the author of a wrapper by reading the file.
+  \item support mostly transparently the dimensions and types chosen by the user.
+\end{itemize}
+
+The most common case should be to create a new wrapper for a simple image filter, like 
+\verb$MedianImageFilter$. Let see that example in detail.
+
+Here is the \verb$BasicFiltersB/wrap_itkMedianImageFilter.cmake$ file:
+
+\small \begin{verbatim}
+WRAP_CLASS("itk::MedianImageFilter" POINTER)
+  WRAP_IMAGE_FILTER_INT(2)
+  WRAP_IMAGE_FILTER_SIGN_INT(2)
+  WRAP_IMAGE_FILTER_REAL(2)
+END_WRAP_CLASS()
+\end{verbatim} \normalsize
+
+The file contains a \verb$WRAP_CLASS$ - \verb$END_WRAP_CLASS$ block, which itself contains
+some \verb$WRAP_IMAGE_FILTER_*$ macros. \verb$WRAP_CLASS("itk::MedianImageFilter" POINTER)$
+begin the wrapping of the \verb$itk::MedianImageFilter$ templated class. The name of the class
+must be fully qualified. The option \verb$POINTER$ indicate that the object of the class can be
+manipulated with a \verb$SmartPointer$, and that the \verb$SmartPointer$ specialization for
+the class \verb$itk::MedianImageFilter$ must be created.
+
+Then, several \verb$WRAP_IMAGE_FILTER_*$ macros are called. They are convenient macro which create
+a set of template argument.
+
+All of the available directives are defined and documented
 in \verb$CreateCableSwigInputs.cmake$. The basics are presented here:

### 2006-03-01 Python/itkBase.py
move the callback call to display the real loading order
darcs-hash:20060301151425-2fc9d-d2bb2921540b4ebf28b78de46cab16e344660fbd.gz

@@ -31,8 +31,6 @@ def LoadModule(name, namespace = None):
         namespace.update(symbols)
     return
   
-  if itkConfig.ImportCallback: itkConfig.ImportCallback(name)
-  
   # We're definitely going to load the templates. We set templates_loaded here
   # instead of at the end of the file to protect against cyclical dependencies
   # that could kill the recursive lookup below.
@@ -51,6 +49,8 @@ def LoadModule(name, namespace = None):
   if data:
     for dep in data.depends:
       LoadModule(dep, namespace)
+  
+  if itkConfig.ImportCallback: itkConfig.ImportCallback(name)
   
   # SWIG-generated modules have 'Python' appended. Only load the SWIG module if
   # we haven't already.

### 2006-03-01 Python/Tests/itk-functions.py
test import callback feature
darcs-hash:20060301151657-2fc9d-e88abcb8203ddf1a2efd040fcdbc22e931beef17.gz

@@ -1,5 +1,11 @@
 #!/usr/bin/env python
 
+# also test the import callback feature
+def custom_callback(name):
+  print "loading %s submodule..." % name
+import itkConfig
+itkConfig.ImportCallback = custom_callback
+
 import itk, sys
 
 fileName = sys.argv[1]

### 2006-03-01 Python/Tests/simple_pipeline.py
UNDO: add some filter to test that objects can be passed from one module to one other
darcs-hash:20060301153041-2fc9d-95312869e1a7c2c577f79276882fb8fb5754cb43.gz

@@ -1,10 +1,5 @@
 #!/usr/bin/env python
 
-def custom_callback(name):
-  print "loading %s submodule..." % name
-import itkConfig
-itkConfig.ImportCallback = custom_callback
-
 import itk, sys
 
 # first argument is the pixel type
@@ -17,16 +12,8 @@ IType = itk.Image[PType, dim]
 
 # create the reader
 reader = itk.ImageFileReader[IType].New(FileName=sys.argv[3])
-# use a filter outside the IO sub module to be sure objects can be pass
-# from one module to one other
-cast1 = itk.CastImageFilter[IType, IType].New(reader)
-cast1.Update()
-shift = itk.ShiftScaleImageFilter[IType, IType].New(cast1)
-shift.Update()
-cast2 = itk.CastImageFilter[IType, IType].New(shift)
-cast2.Update()
 # and the writer
-writer = itk.ImageFileWriter[IType].New(cast2, FileName=sys.argv[4])
+writer = itk.ImageFileWriter[IType].New(reader, FileName=sys.argv[4])
 
 # execute the filters in the pipeline !
 writer.Update()

### 2006-03-01 Python/Tests/simple_pipeline.py
add some filter to test that objects can be passed from one module to one other
darcs-hash:20060301153041-2fc9d-e4eaf9b025879ead9e292a53db0e5d69cfb489c8.gz

@@ -1,5 +1,10 @@
 #!/usr/bin/env python
 
+def custom_callback(name):
+  print "loading %s submodule..." % name
+import itkConfig
+itkConfig.ImportCallback = custom_callback
+
 import itk, sys
 
 # first argument is the pixel type
@@ -12,8 +17,16 @@ IType = itk.Image[PType, dim]
 
 # create the reader
 reader = itk.ImageFileReader[IType].New(FileName=sys.argv[3])
+# use a filter outside the IO sub module to be sure objects can be pass
+# from one module to one other
+cast1 = itk.CastImageFilter[IType, IType].New(reader)
+cast1.Update()
+shift = itk.ShiftScaleImageFilter[IType, IType].New(cast1)
+shift.Update()
+cast2 = itk.CastImageFilter[IType, IType].New(shift)
+cast2.Update()
 # and the writer
-writer = itk.ImageFileWriter[IType].New(reader, FileName=sys.argv[4])
+writer = itk.ImageFileWriter[IType].New(cast2, FileName=sys.argv[4])
 
 # execute the filters in the pipeline !
 writer.Update()

### 2006-03-01 Python/itk.py
sort the module so they are always imported in the same order
darcs-hash:20060301153620-2fc9d-3562aae88d9e2d95877843276b719e9c6a02b56f.gz

@@ -9,6 +9,7 @@ import itkBase, itkConfig, os
 # First, find all the xxxConfig.py files in the config_py dir, and strip off the
 # 'Config.py' part of the filename.
 configModules = [f[:-9] for f in os.listdir(itkConfig.config_py) if f.endswith('Config.py')]
+configModules.sort()
 
 for module in configModules:
   # If the configuration defines an auto_load attribute and it's set to True

### 2006-03-01 Python/itkBase.py

@@ -47,7 +47,9 @@ def LoadModule(name, namespace = None):
   # to find those configuration files.
   data = module_data[name]
   if data:
-    for dep in data.depends:
+    deps = list(data.depends)
+    deps.sort()
+    for dep in deps:
       LoadModule(dep, namespace)
   
   if itkConfig.ImportCallback: itkConfig.ImportCallback(name)

### 2006-03-01 Python/Tests/module2module.py
test if object can be passed from one module to one other
darcs-hash:20060301162920-2fc9d-057f11035378da3dc9682321aeca4f3f07b1fecf.gz

@@ -1,0 +1,80 @@
+#!/usr/bin/env python
+
+# def custom_callback(name):
+#   print "loading %s submodule..." % name
+# import itkConfig
+# itkConfig.ImportCallback = custom_callback
+
+import itk, sys
+
+import ITKCommonA
+import ITKCommonB
+import ITKNumerics
+import ITKBasicFiltersA
+import ITKBasicFiltersB
+import ITKBasicFiltersC
+import ITKSpatialObject
+import ITKAlgorithms
+import ITKIO
+
+PType = itk.US
+dim = 2
+IType = itk.Image[PType, dim]
+
+# create the reader
+reader = itk.ImageFileReader[IType].New(FileName=sys.argv[1])
+
+sources = []
+image = ITKCommonA.Image[PType, dim].New()
+r = itk.ImageRegion._2()
+r.SetSize((10, 10))
+image.SetRegions(r)
+image.Allocate()
+
+sources.append(("ITKCommonA", image))
+
+flip = ITKBasicFiltersA.FlipImageFilter[IType].New(reader)
+sources.append(("ITKBasicFiltersA", flip.GetOutput()))
+
+shift = ITKBasicFiltersB.ShiftScaleImageFilter[IType, IType].New(reader)
+sources.append(("ITKBasicFiltersB", shift.GetOutput()))
+
+abs = ITKBasicFiltersC.AbsImageFilter[IType, IType].New(reader)
+sources.append(("ITKBasicFiltersC", abs.GetOutput()))
+
+otsu = ITKAlgorithms.OtsuThresholdImageFilter[IType, IType].New(reader)
+sources.append(("ITKAlgorithms", otsu.GetOutput()))
+
+sources.append(("ITKIO", reader.GetOutput()))
+
+
+
+dests = []
+dflip = ITKBasicFiltersA.FlipImageFilter[IType].New()
+dests.append(("ITKBasicFiltersA", dflip))
+
+dshift = ITKBasicFiltersB.ShiftScaleImageFilter[IType, IType].New()
+dests.append(("ITKBasicFiltersB", dshift))
+
+dabs = ITKBasicFiltersC.AbsImageFilter[IType, IType].New()
+dests.append(("ITKBasicFiltersC", dabs))
+
+dotsu = ITKAlgorithms.OtsuThresholdImageFilter[IType, IType].New()
+dests.append(("ITKAlgorithms", dotsu))
+
+writer = ITKIO.ImageFileWriter[IType].New(FileName='out.png')
[…]

### 2006-03-01 Python/Tests/module2module.py
display the nb of failures
darcs-hash:20060301164418-2fc9d-0b5deb76c0c1092bde71d5de31ba1b483dfbf023.gz

@@ -66,15 +66,22 @@ writer = ITKIO.ImageFileWriter[IType].New(FileName='out.png')
 dests.append(("ITKIO", writer))
 
 
-failure = False
+nb = 0
+failList = []
 for sname, s in sources:
   for dname, d in dests:
+    nb += 1
     d.SetInput( s )
     try:
       d.Update()
       print "%s -> %s pass" % (sname, dname)
     except RuntimeError, e:
-      print "%s -> %s fail (%s)" % (sname, dname, str(e))
-      failure = True
+      print "%s -> %s fail" % (sname, dname)
+      failList.append((sname, dname))
       
-sys.exit(failure)
+      
+print
+print "%i tests succeed" % (nb - len(failList))
+print "%i tests failed" % len(failList)
+
+sys.exit(len(failList))

### 2006-03-02 Python/itkBase.py
Fix problem with dict.update not accepting (k, v) lists on py 2.3.
darcs-hash:20060302231309-733a7-7306035a9ed2fe963640a3782b64bb08da3261da.gz

@@ -22,13 +22,13 @@ def LoadModule(name, namespace = None):
     if namespace:
         swig = namespace.setdefault('swig', imp.new_module('swig'))
         swig.__dict__.update(this_module.swig.__dict__)
-        symbols = [(k, v) for k, v in this_module.__dict__.items() 
-          if not (k.startswith('_') or k == 'swig')]
+
         # don't worry about overwriting the symbols in namespace -- any common
         # symbols should be of type itkTemplate, which is a singleton type. That
         # is, they are all identical, so replacing one with the other isn't a
         # problem.
-        namespace.update(symbols)
+        for k, v in this_module.__dict__.items():
+          if not (k.startswith('_') or k == 'swig'): namespace[k] = v
     return
   
   # We're definitely going to load the templates. We set templates_loaded here

### 2006-03-09 article/Article.tex
some (old) small corrections
darcs-hash:20060309192244-2fc9d-538b32c89d29a66bbb132b1f2f1115de1c48b8c2.gz

@@
 
-Note that you should always build your project outside the source tree.
+Project should always be built outside the source directory, in a \veb$build$
+directory for example.
 
@@
 properly.
-
-TODO: alternatively, the submodules may be imported
 
@@
 \verb$itk.Image.UC3$ refere to the same class than \verb$itk.Image[itk.UC, 3]$
-but have the advantage to allow the usage of tab completion in the interpreter,
+but have the advantage to allow to use the tab-completion in the interpreter,
 and so let the user easily know which template arguments he can use.
 However, this notation is more rigid than the one above and won't let the user
-specify the type and the type and the dimension used in a single place, and thus,
+specify the type and the dimension used in a single place, and thus,
 should be use only in interpreter.
@@
 This makes it easy to write generic routines which
-can deal with any input image type. For example, an function which take an image
+can deal with any input image type. For example, anfunction which take an image
 as parameter and write it to a file without having to give the image type can be:
@@
 \end{verbatim}
-In that case, \verb$New$ will use the \verb$GetOutput()$ of the object if it
-exist to get the image, and the inputs of the new filter.
+In that case, \verb$New$ will use the \verb$GetOutput()$ method of the object, if it
+exist, to get the image and set the inputs of the new filter.
 
@@
 
-A more safe and convenient way to do that, if you have installed the optional patch,
+A more safe and convenient way to do that, if you have installed the optional patches,
 is to use the standard python list interface.
@@
 Instead of using \verb$Size$ object, it is possible to use python sequences, like lists
-and tuple.
+and tuples.
 
@@
 Note that it is called \verb$class_$ and not \verb$class$, because \verb$class$ is a
-reseved word in python.
+reserved word in python.
 
@@
   \item make creation of wrappers easy. The syntax is simple enough to get in quickely.
-  \item make wchoice of template arguments explicit. It should be easy to understand
+  \item make choice of template arguments explicit. It should be easy to understand
 the idea of the author of a wrapper by reading the file.
@@
 The most common case should be to create a new wrapper for a simple image filter, like 
-\verb$MedianImageFilter$. Let see that example in detail.
+\verb$MedianImageFilter$. Let see that example in details.
 
@@
 
-Then, several \verb$WRAP_IMAGE_FILTER_*$ macros are called. They are convenient macro which create
-a set of template argument.
+Then, several \verb$WRAP_IMAGE_FILTER_*$ macros are called. They are convenient macro to
+create wrapper for classes which take only image types as template arguments. The parameter,
+here \verb$2$, give the number of required template arguments. The two image types used as
+template parameter are the same.
 

### 2006-03-18 patch/optional/itkCropImageFilter.h
Clean up patches
darcs-hash:20060318200930-733a7-cd8ca0a1c880936386dea45d4b5ed8d42df77351.gz

@@ -1,39 +1,0 @@
-*** itk/Insight/Code/BasicFilters/itkCropImageFilter.h	2006-01-07 15:09:43.000000000 +0100
---- itk-mima2/Insight/Code/BasicFilters/itkCropImageFilter.h	2005-10-24 13:50:59.000000000 +0200
-***************
-*** 78,83 ****
---- 78,111 ----
-    itkSetMacro(LowerBoundaryCropSize, SizeType);
-    itkGetMacro(LowerBoundaryCropSize, SizeType);
-    
-+   void SetUpperBoundaryCropSize(const unsigned long bound)
-+     {
-+     SizeType s;
-+     s.Fill( bound );
-+     this->SetUpperBoundaryCropSize( s );
-+     }
-+     
-+   void SetLowerBoundaryCropSize(const unsigned long bound)
-+     {
-+     SizeType s;
-+     s.Fill( bound );
-+     this->SetLowerBoundaryCropSize( s );
-+     }
-+     
-+   void SetBoundaryCropSize(const SizeType & s)
-+     {
-+     this->SetUpperBoundaryCropSize( s );
-+     this->SetLowerBoundaryCropSize( s );
-+     }
-+ 
-+   void SetBoundaryCropSize(const unsigned long bound)
-+     {
-+     SizeType s;
-+     s.Fill( bound );
-+     this->SetBoundaryCropSize( s );
-+     }
-+ 
-+   
-                   
-  protected:
-    CropImageFilter()

### 2006-03-18 patch/optional/itkPadImageFilter.h

@@ -1,59 +1,0 @@
-*** itk/Insight/Code/BasicFilters/itkPadImageFilter.h	2006-01-07 15:10:04.000000000 +0100
---- itk-mima2/Insight/Code/BasicFilters/itkPadImageFilter.h	2005-10-24 13:50:58.000000000 +0200
-***************
-*** 18,23 ****
---- 18,24 ----
-  #define __itkPadImageFilter_h
-  
-  #include "itkImageToImageFilter.h"
-+ #include "itkSize.h"
-  
-  namespace itk
-  {
-***************
-*** 78,83 ****
---- 79,122 ----
-    itkSetVectorMacro(PadUpperBound, const unsigned long, ImageDimension);
-    itkGetVectorMacro(PadLowerBound, const unsigned long, ImageDimension);
-    itkGetVectorMacro(PadUpperBound, const unsigned long, ImageDimension);
-+   
-+   void SetPadLowerBound(const itk::Size<ImageDimension> & bound)
-+     {
-+     this->SetPadLowerBound( bound.m_Size );
-+     }
-+     
-+   void SetPadUpperBound(const itk::Size<ImageDimension> & bound)
-+     {
-+     this->SetPadUpperBound( bound.m_Size );
-+     }
-+     
-+   void SetPadBound(const itk::Size<ImageDimension> & bound)
-+     {
-+     this->SetPadLowerBound( bound );
-+     this->SetPadUpperBound( bound );    
-+     }
-+ 
-+   void SetPadLowerBound(const unsigned long bound)
-+     {
-+     itk::Size<ImageDimension> s;
-+     s.Fill( bound );
-+     this->SetPadLowerBound( s );
-+     }
-+     
-+   void SetPadUpperBound(const unsigned long bound)
-+     {
-+     itk::Size<ImageDimension> s;
-+     s.Fill( bound );
-+     this->SetPadUpperBound( s );
-+     }
-+     
-+   void SetPadBound(const unsigned long bound)
-+     {
-+     itk::Size<ImageDimension> s;
-+     s.Fill( bound );
-+     this->SetPadBound( s );
-+     }
-+ 
-                   
-    /** PadImageFilter produces an image which is a different resolution
-     * than its input image.  As such, PadImageFilter needs to

### 2006-03-20 Python/Tests/itk-functions.py
fix strel tests
darcs-hash:20060320205518-2fc9d-f2fe8af134d6d847222b9727e3e3005ed89a5284.gz

@@ -56,16 +56,14 @@ assert itk.image(1) == 1
 # test strel
 # should work with the image type, an image instance or a filter
 # and should work with a list, a tuple, an int or an itk.Size
-for t in [IType, reader, reader.GetOutput(), reader.GetOutput().GetPointer()] :
-  for s in [2, (2, 2), [2, 2], itk.Size[2](2)] :
-    st = itk.strel(t, s)
-    
-    (tpl, param) = itk.template(st)
-    assert tpl == itk.BinaryBallStructuringElement
-    assert param[0] == PType
-    assert param[1] == dim
-    assert st.GetRadius().GetElement(0) == st.GetRadius().GetElement(1) == 2
-
+for s in [2, (2, 2), [2, 2], itk.Size[2](2)] :
+  st = itk.strel(dim, s)
+  
+  (tpl, param) = itk.template(st)
+  assert tpl == itk.BinaryBallStructuringElement
+  assert param[0] == itk.B
+  assert param[1] == dim
+  assert st.GetRadius().GetElement(0) == st.GetRadius().GetElement(1) == 2
 
 # test size
 s = itk.size(reader)

### 2006-03-21 Python/itkTemplate.py
support bz2-compressed man pages
darcs-hash:20060321124116-2fc9d-67f4bde3ee4712ae0a0c859dd9d02ea5311a0029.gz

@@ -225,7 +225,10 @@ class itkTemplate(object):
         import commands
         doxyname = self.__name__.replace("::", "_")
         man_path = "%s/man3/%s.3" %(itkTemplate.__doxygen_root__, doxyname)
-        if os.path.exists(man_path):
+        bzman_path = "%s/man3/%s.3.bz2" %(itkTemplate.__doxygen_root__, doxyname)
+        if os.path.exists(bzman_path):
+	    return commands.getoutput("bunzip2 --stdout '"+bzman_path+"' | groff -mandoc -Tascii -c")
+        elif os.path.exists(man_path):
           # Use groff here instead of man because man dies when it is passed paths with spaces (!)
           # groff does not.
           return commands.getoutput("groff -mandoc -Tascii -c '" + man_path +"'")

### 2006-03-22 article/Article.tex
fix typo
darcs-hash:20060321095655-2fc9d-6e1d82c017100ddddd4639421532ad9c0dd5076a.gz
add a note about article status
darcs-hash:20060322102716-2fc9d-e829b2f6f0a9b1af82b4f51f304765422fde9a20.gz

@@
 
-Currently, WrapITK only supports Python properly; Java and Tcl libraries build
+Currently, WrapITK have been tested on Mandriva Linux, and MacOS X, and only
+supports Python properly; Java and Tcl libraries build
 correctly but the Java and Tcl support classes for loading these libraries needs
@@
 
-It have been tested on Mandriva Linux, and MacOS X.
+The article you're reading is not as nice and complete than what we would have
+done, but it seems important to us to release our work and to get feedbacks
+as soon as possible. The article will continue to evolve with WrapITK.
 
@@
 
-Project should always be built outside the source directory, in a \veb$build$
+Project should always be built outside the source directory, in a \verb$build$
 directory for example.

### 2006-03-22 article/Article.tex
document strel fuction
darcs-hash:20060322102742-2fc9d-d60350ebc037a3a5616c6dd0654f5aadd8169bb4.gz

@@
 
-  \item \verb$itk.strel$
+  \item \verb$itk.strel( d, s )$ is used to create a binary ball structuring of dimension
+\verb$d$ and size \verb$s$. Strucutring element support is quite bad currently in WrapITK
+and should change in the future. Using \verb$itk.strel$ rather than creating a
+\verb$BinaryBallStructuringElement$ directly is recommended to have backward compatibility
+when the structuring element type will be changed.
 

### 2006-03-22 article/Article.tex
give url to download the rpm packages
darcs-hash:20060322120431-2fc9d-3030ebcad1bcf475e067a7389db25364eabe8405.gz
comment are remove TODO items
darcs-hash:20060322120514-2fc9d-96e9321d8e9e9ebc8e54a8e461441b48796a915a.gz
talk about contributing
darcs-hash:20060322120555-2fc9d-9e22fee82f128c8e558660ec2c2a3aab7d019fcf.gz

@@
 
-A rpm package for Mandriva Linux will be available soon.
+RPM packages for Mandriva Linux 2006 are available at \url{http://voxel.jouy.inra.fr/mdk/mima2}.
 
-TODO: provide more binary packages - for mac and windows.
+% TODO: provide more binary packages - for mac and windows.
 
@@
 
-TODO: rename ItkVtk to ItkVtkGlue to avoid problems wiht non-case sensitive filesystems.
-
   \subsection{Extending language support and adding more languages}
@@
 
-- test
-- Work on tcl, java, and others
-- add more classes
+WrapITK is an opensource project, and so all contributions are welcome. Here are
+some points which requires special attention:
+\begin{itemize}
+  \item Test it and report problem. That's the more important thing to do:
+we need feedbacks to enhance WrapITK quality !
+  \item Work on tcl, java, and others. We are not tcl or java developers, and so
+are not able to complete the work for those languages. Any help from tcl and
+java expert would be highly appreciated. Also, there is no reason to be limited
+to python, tcl and java, and WrapITK can be extended to other languages supported
+by swig like perl, ruby, ocaml and others.
+  \item Add more classes. WrapITK add lots of new classes compared to the current
+wrapping system, but there is still lots of work to do, especially to support more
+filter dedicated to \verb$Vector$ pixels.
+\end{itemize}
 
-talk about darcs
+\verb$darcs$ allow to easily contribute to WrapITK, by sending patch by email with
+the command \verb$darcs send$, while keeping credits for the work done.
+Feel free to send patches; they will be tested and integrated in the project.
+
+A web interface (\url{http://auriga.wearlab.de/~alb/darcsweb/}) for the WrapITK darcs
+repository is available at \url{http://voxel.jouy.inra.fr/darcsweb/}.
 

### 2006-03-22 article/Article.tex
Acknowledgments
darcs-hash:20060322120625-2fc9d-59b521f5fba2e29b528f9fb3c0fe4168840ff9f8.gz

@@
 \section{Acknowledgments}
+I thank Dr Pierre Adenot and all the {\em Embryon et Biotechnologie} team for their
+patience during the long development time before getting a tool really usable.
+
+I also thank Richard Beare for his early interest in using itk with python, and for
+his useful feedbacks.
+
+Thank to Charl P. Botha for is help to debug WrapITK on windows plateform and for the
+patches he has contributed.
+
+Finally, we thank the ITK developers for the great tool which is ITK, and for the
+previous work done on wrapping system - without it WrapITK would not be there.
 

### 2006-03-22 article/Article.tex
add a conclusion
darcs-hash:20060322134610-2fc9d-86b892bd2ff36bce638602a89488940af95266da.gz
document more macros
darcs-hash:20060322155801-2fc9d-b57bf2c6580702a4251637e9c3b6a548d4f7bf47.gz

@@
 \begin{itemize}
-  \item \verb$WRAP_INCLUDE("header.h")$ -- causes the named header to be \verb$#included$ in the
-generated files.
-
-  \item \verb$WRAP_CLASS("fully_qualified::ClassName" [POINTER|POINTER_WITH_SUPERCLASS])$ --
+  \item \verb$WRAP_CLASS("fully_qualified::ClassName" [POINTER|POINTER_WITH_SUPERCLASS])$
 causes a templated class to be wrapped. All namespaces must be included in the
@@
 
-  \item \verb$WRAP_TEMPLATE("mangled_suffix" "template parameters")$ -- When issued between \verb$WRAP_CLASS$
+  \item \verb$END_WRAP_CLASS()$ -- end a block of template instantiations for a particular
+class.
+
+  \item \verb$WRAP_INCLUDE("header.h")$. By default, \verb$itkMedianImageFilter.h$ is included
+when the  causes the \verb$itk::MedianImageFilter$ is wrapped, and this behavior is most of the
+time enough. If it not enough, this macro can be used to include some specific files.
+
+  \item \verb$WRAPPER_AUTO_INCLUDE_HEADERS$. This variable is set to \verb$ON$ by default, but can
+be set to \verb$OFF$ to disable the auto include feature. This feature should be used when several
+classes to wrap come from the same header file.
+
+  \item \verb$WRAP_TEMPLATE("mangled_suffix" "template parameters")$. When issued between \verb$WRAP_CLASS$
 and \verb$END_WRAP_CLASS$, this command causes a particular template instantiation of
@@
 
-  \item \verb$WRAP_TEMPLATE_IF_TYPES("mangled_suffix" "template parameters" "type list")$
+  \item \verb$WRAP_NON_TEMPLATE_CLASS("fully_qualified::ClassName" [POINTER|POINTER_WITH_SUPERCLASS])$.
+Same as \verb$WRAP_CLASS$, but creates a wrapper
+for a non-templated class. No \verb$END_WRAP_CLASS()$ is necessary after this macro
+because there is no block of template instantiating commands to close.
 
-  \item \verb$WRAP_type(size)$ (where 'type' is \verb$INT$, \verb$SIGN_INT$, \verb$REAL$, \verb$VECTOR_REAL$,
-\verb$COV_VECTOR_REAL$ or \verb$RGB$) -- create a template instantiation with 'size'
+\end{itemize}
+
+WrapITK define some lists which group the types and dimensions. Those list can be used
+by the developer to create a wrappers but must {\em never} be modified.
+
+\begin{itemize}
+  \item \verb$WRAP_ITK_DIMS$ contains all the dimensions selected by the user.
+
+  \item \verb$WRAP_ITK_INT$ contains all unsigned integer types selected by the user.
+
+  \item \verb$WRAP_ITK_SIGN_INT$ contains all signed integer types selected by the user.
+
+  \item \verb$WRAP_ITK_INTEGRAL$ contains all signed and unsigned integral types
+selected by the user.
+
+  \item \verb$WRAP_ITK_REAL$ contains all the real types selected by the user.
+
+  \item \verb$WRAP_ITK_SCALAR$ contains all the scalar types selected by the user.
+
+  \item \verb$WRAP_ITK_RGB$ contains all the \verb$RGB$ types selected by the user.
+
+  \item \verb$WRAP_ITK_VECTOR_REAL$ contains all the \verb$Vector$ types selected
+by the user.
+
+  \item \verb$WRAP_ITK_COV_VECTOR_REAL$ contains all the \verb$CovariantVector$ types selected
+by the user.
+
+  \item \verb$WRAP_ITK_VECTOR$ contains all the \verb$Vector$ and 
+\verb$CovariantVector$ types selected by the user.
+
+  \item \verb$WRAP_ITK_ALL_TYPES$ contains all the types selected byt the user.
+
+  \item \verb$SMALLER_THAN_D$ contains all the types "smaller" than \verb$double$
+selected by the user. This variable is useful when a filter decrease the range
+of pixel value, like \verb$BinaryThresholdImageFilter$.
+
+  \item \verb$SMALLER_THAN_UL$ contains all the types "smaller" than \verb$unsigned long$
+selected by the user.
+
+  \item \verb$SMALLER_THAN_US$ contains all the types "smaller" than \verb$unsigned short$
+selected by the user.
+
+  \item \verb$SMALLER_THAN_SL$ contains all the types "smaller" than \verb$signed long$
+selected by the user.
+
+  \item \verb$SMALLER_THAN_SS$ contains all the types "smaller" than \verb$signed short$
+selected by the user.
+
+\end{itemize}
+
+WrapITK provides some macros to manipulate those list and use them
+to create the wrappers. Most of those macros are there to fill a lack
+of feature to manipulate lists in CMake, and should be replaced by
+some CMake native commands in the future.
+
+\begin{itemize}
+  \item \verb$UNIQUE()$
+
+  \item \verb$SORT()$
+
+  \item \verb$INTERSECTION()$
+
+  \item \verb$FILTER()$
+
+  \item \verb$FILTER_DIMS()$
+
+  \item \verb$INCREMENT()$
+
+  \item \verb$DECREMENT()$
+
+\end{itemize}
+
+Some convenient macros are available to wrap image filters.
+
+\begin{itemize}
+
+  \item \verb$WRAP_IMAGE_FILTER_type(size)$ . \verb$type$ can be one of:
+  \begin{itemize}
+    \item \verb$INT$
+    \item \verb$SIGN_INT$
+    \item \verb$REAL$
+    \item \verb$VECTOR_REAL$
+    \item \verb$COV_VECTOR_REAL$
+    \item \verb$RGB$
+    \item \verb$ALL$
+    \item \verb$SCALAR$
+    \item \verb$VECTOR$
+  \end{itemize}
+
+ This macro create a template instantiation with \verb$size$
 \verb$itk::Image$ parameters of the given pixel type. So if you are wrapping a filter
@@
 
-  \item \verb$WRAP_type_DIMS(size dims)$ (with \verb$type$ as above) -- Wrap a filter for certain
-dimensions only. Dims should be either a semicolon-separated list of valid
-dimensions, or something of the form \verb$'3+'$ to specify that the filter can be
-instantiated only for three- and higher-dimensional images. Note that if the
-user has not selected to wrap a given dimension at build time, a filter wrapped
-with \verb$WRAP_type_DIMS$ will not be instantiated: the final dimensions wrapped are
-the {/em intersection} of the user-selected dimensions and the valid dimensions
-declared with \verb$WRAP_type_DIMS$.
+  \item \verb$WRAP_IMAGE_FILTER(param_types param_count)$ is a more general
+macro for wrapping image filters that need one or more image parameters of the
+same type. The first parameter to this macro is a list of image pixel types for
+which filter instantiations should be created. The second is a \verb$param_count$
+parameter which controls how many image template parameters are created (see
+above). The optional third parameter is a dimensionality condition (see above
+also).
 
-  \item \verb$END_WRAP_CLASS()$ -- end a block of template instantiations for a particular
-class.
+E.g. \verb@WRAP_IMAGE_FILTER("${WRAP_ITK_ALL}" 2)@ will create template instantiations
+of the filter for every pixel type that the user has selected.
 
-  \item \verb$WRAP_NON_TEMPLATE_CLASS("fully_qualified::ClassName" [POINTER|POINTER_WITH_SUPERCLASS])$
- -- Same as \verb$WRAP_CLASS$, but creates a wrapper
-for a non-templated class. No \verb$END_WRAP_CLASS()$ is necessary after this macro
-because there is no block of template instantiating commands to close.
+  \item \verb$WRAP_IMAGE_FILTER_TYPES()$. Creates template instantiations of the
+current image filter, for all the dimensions selected by the user (or dimensions
+selected by the user that meet the optional dimensionality condition). This
+macro takes a variable number of arguments, which should correspond to the image
+pixel types of the images in the filter's template parameter list. The optional
+dimensionality condition should be  placed in the last parameter.
+
+  \item \verb$WRAP_IMAGE_FILTER_COMBINATIONS()$ takes a variable number of
+parameters. Each parameter is a list of image pixel types. Filter instantiations
+are created for every combination of different pixel types in different
+parameters. A dimensionality condition may be optionally specified as the first
+parameter. E.g. \verb$WRAP_IMAGE_FILTER_COMBINATIONS("UC;US" "UC;US")$ will
+create: \verb$filter<itk::Image<unsigned char, d>, itk::Image<unsigned char, d> >$,
+\verb$filter<itk::Image<unsigned char, d>, itk::Image<unsigned short, d> >$,
+\verb$filter<itk::Image<unsigned short, d>, itk::Image<unsigned char, d> >$, and
+\verb$filter<itk::Image<unsigned short, d>, itk::Image<unsigned short, d> >$
+where \verb$d $is the image dimension, for each selected image dimension.
+
+%   \item \verb$WRAP_type_DIMS(size dims)$ (with \verb$type$ as above) -- Wrap a filter for certain
+% dimensions only. Dims should be either a semicolon-separated list of valid
+% dimensions, or something of the form \verb$'3+'$ to specify that the filter can be
+% instantiated only for three- and higher-dimensional images. Note that if the
+% user has not selected to wrap a given dimension at build time, a filter wrapped
+% with \verb$WRAP_type_DIMS$ will not be instantiated: the final dimensions wrapped are
+% the {/em intersection} of the user-selected dimensions and the valid dimensions
+% declared with \verb$WRAP_type_DIMS$.
+
 \end{itemize}
@@
 
+ITK is a great library, with the drawback to be nearly unusable for prototyping,
+and to have a poor support for other languages than C++. WrapITK address those
+issue and finally give to ITK a quite good support for python. We hope that support
+will soon be extended to tcl and java.
+
 % \url{http://www.itk.org}

### 2006-03-22 article/Article.tex
cosmetics
darcs-hash:20060322160531-2fc9d-e9214ce8bd115ccee7e9b616575e65249b662c46.gz
add some references and use footnotes
darcs-hash:20060322165712-2fc9d-ea159a633e2c5739180dfbdf96895f0ea554d187.gz

@@
 \noindent
-ITK is a huge image analysis library, which contains lots of state of the arts
+ITK \cite{ITKWebSite} is a huge image analysis library, which contains lots of state of the arts
 algorithms implementations. However, using it in C++ can be difficult and is
@@
 (and custom, classes that interact with ITK) to be "wrapped" for use with
-languages like Python, Tcl, and Java.
+languages like Python \cite{PythonWebSite}, Tcl \cite{TclWebSite}, and Java \cite{JavaWebSite}.
 \end{abstract}
@@
 that interact with ITK) to be "wrapped" for use with languages like
-Python, Tcl, and Java.
-
-Note that ITK already has a wrapping infrastructure. This project aims to be
+Python \cite{PythonWebSite}, Tcl \cite{TclWebSite}, and Java \cite{JavaWebSite}.
+
+Note that ITK already has a wrapping infrastructure, and that WrapITK is based
+on it, and use the same tools: CMake \cite{CMakeWebSite}, GCC-XML \cite{GccxmlWebsite}
+and CableSwig \cite{CableSwigWebSite}. This project aims to be
 address the following deficits of the existing wrappers (and others):
@@
 
-For the user which don't want to use darcs but want the last development version,
+For the user which don't want to use darcs \cite{DarcsWebSite} but want the last development version,
 a nightly updated archive is available at
@@
 While prototyping, it is a convenient way for the user to know if
-the execution time will be short or if he can do something more useful than waiting
-for the filter to complete (like having a cup of tea).
+the execution time will be short or if he can do something more useful
+\footnote{like having a cup of tea} than waiting for the filter to complete.
 
@@
 to python, tcl and java, and WrapITK can be extended to other languages supported
-by swig like perl, ruby, ocaml and others.
+by swig like perl \cite{PerlWebSite}, ruby \cite{RubyWebSite}, ocaml \cite{OcamlWebSite} and others.
   \item Add more classes. WrapITK add lots of new classes compared to the current
@@
 
-\verb$darcs$ allow to easily contribute to WrapITK, by sending patch by email with
+\verb$darcs$ \cite{DarcsWebSite} allow to easily contribute to WrapITK, by sending patch by email with
 the command \verb$darcs send$, while keeping credits for the work done.
@@
 
-A web interface (\url{http://auriga.wearlab.de/~alb/darcsweb/}) for the WrapITK darcs
+A web interface \cite{DarcswebWebSite} for the WrapITK's darcs
 repository is available at \url{http://voxel.jouy.inra.fr/darcsweb/}.
@@
 
-Thank to Charl P. Botha for is help to debug WrapITK on windows plateform and for the
+We thank Charl P. Botha for is help to debug WrapITK on windows plateform, and for the
 patches he has contributed.
@@
 
-% \url{http://www.itk.org}
-% \code{Insight/Documentation/Style.pdf}
-% \section{Principles of Solar Spot Detection}
-% \cite{ITKSoftwareGuide}.
-% \doxygen{ImageToImageFilter}
-
-% \small \begin{verbatim}
-% \end{verbatim} \normalsize
-
-% The {itemize} environment uses a bullet for each \item.  If you want the 
-% \item's numbered, use the {enumerate} environment instead.
-% \begin{itemize}
-%   \item  Insight Toolkit 2.4.
-%   \item  CMake 2.2
-% \end{itemize}
-
-% \ref{cthead1}
-
-% \begin{figure}[htbp]
-% \centering
-% \includegraphics{cthead1}
-% \caption{The input image.\label{cthead1}}
-% \end{figure}
-
 \appendix
@@
 \bibliographystyle{plain}
-\bibliography{InsightJournal}
+\bibliography{Article,InsightJournal}
 \nocite{ITKSoftwareGuide}

### 2006-03-23 article/Article.tex
more references
darcs-hash:20060323092432-2fc9d-2a5f80d69c44f15920798a71eac8fe776cadc35d.gz

@@
   \item \verb$itk.show()$, \verb$itk.show2D()$ and \verb$itk.show3D()$ are used to
-display images. \verb$itk.show2D()$ requires to have \verb$imview$ installed.
-\verb$itk.show3D()$ requires to have ItkVtk, PyQt, and iPython installed, and to use
-iPython with the \verb$-qthread$ option.
+display images. \verb$itk.show2D()$ requires to have imview \cite{ImviewWebSite} installed.
+\verb$itk.show3D()$ requires to have ItkVtkGlue\footnote{ItkVtkGlue can be found in
+the {\em ExternalProject} directory of WrapITK}, PyQt \cite{PyQtWebSite}, and iPython
+\cite{IPythonWebSite} installed, and to use iPython with the \verb$-qthread$ option.
 

### 2006-03-23 article/Article.tex
article continued
darcs-hash:20060323154759-2fc9d-40cf372ffa1ab0ae3b8acf649dcd5bedf71f51e9.gz

@@
 on it, and use the same tools: CMake \cite{CMakeWebSite}, GCC-XML \cite{GccxmlWebsite}
-and CableSwig \cite{CableSwigWebSite}. This project aims to be
+and CableSwig\footnote{CableSwig is based on a now quite old version of SWIG
+\cite{SwigWebSite}.} \cite{CableSwigWebSite}. This project aims to
 address the following deficits of the existing wrappers (and others):
@@
 
-For the user which don't want to use darcs \cite{DarcsWebSite} but want the last development version,
+For the user who don't want to use darcs \cite{DarcsWebSite} but want the last development version,
 a nightly updated archive is available at
@@
 
-WrapITK will work properly with a CVS checkout of ITK from 2006-1-31 or later,
-or with the ITK 2.4.1 release. If you are using 2.4.1, there are several
-required patches to correct bugs in ITK that must be applied. Follow the
-directions in \verb$WrapITK/patches$ to do so. Additionally, there are some optional
+WrapITK will work properly with the ITK 2.6.0 release.
+
+There are some optional
 patches to the ITK source in \verb$WrapITK/patches/optional$ which can be applied to
-either a CVS checkout of ITK or to version 2.4.1. These optional patches provide
+version 2.6.0. These optional patches provide
 better support for python by providing some methods like \verb$__str__$, or methods
@@
 This makes it easy to write generic routines which
-can deal with any input image type. For example, anfunction which take an image
+can deal with any input image type. For example, a function which take an image
 as parameter and write it to a file without having to give the image type can be:
@@
 \begin{itemize}
-  \item \verb$itk.image( object )$ try to return an image from the object given in
+  \item \verb$itk.image(object)$ try to return an image from the object given in
 parameter. This function is used in most of the next functions to allow the user to
@@
 
-  \item \verb$itk.range( object )$ return the range of values of an image in a tuple.
+  \item \verb$itk.range(object)$ return the range of values of an image in a tuple.
 \verb$object$ can be an image or a filter. In case of a filter, \verb$itk.image()$ is used
@@
 
-  \item \verb$itk.size( object )$ return the size of an image.
+  \item \verb$itk.size(object)$ return the size of an image.
 \verb$object$ can be an image or a filter. In case of a filter, \verb$itk.image()$ is used
@@
 
-  \item \verb$itk.template( object )$ returns the template class and parameters
+  \item \verb$itk.template(object)$ returns the template class and parameters
 of a class or instance of this class.
@@
 
-  \item \verb$itk.write( object, fileName )$ write an image in a file, without
+  \item \verb$itk.write(object, fileName)$ write an image in a file, without
 having to pass the image type.
@@
 display images. \verb$itk.show2D()$ requires to have imview \cite{ImviewWebSite} installed.
-\verb$itk.show3D()$ requires to have ItkVtkGlue\footnote{ItkVtkGlue can be found in
-the {\em ExternalProject} directory of WrapITK}, PyQt \cite{PyQtWebSite}, and iPython
+\verb$itk.show3D()$ requires to have Vtk for python, ItkVtkGlue\footnote{ItkVtkGlue can be found in
+the {\em ExternalProject} directory of WrapITK} for python, PyQt \cite{PyQtWebSite}, and iPython
 \cite{IPythonWebSite} installed, and to use iPython with the \verb$-qthread$ option.
@@
 
-  \item \verb$itk.strel( d, s )$ is used to create a binary ball structuring of dimension
+  \item \verb$itk.strel(d, s)$ is used to create a binary ball structuring of dimension
 \verb$d$ and size \verb$s$. Strucutring element support is quite bad currently in WrapITK
@@
 
-  \item \verb$itk.auto_progress( b )$ is used to automatically add a progress report
+  \item \verb$itk.auto_progress(b)$ is used to automatically add a progress report
 to all the newly created filters. \verb$b$ must be \verb$True$ or \verb$False$. If
@@
 
-  \item \verb$itk.class_( object )$ return the class of an object. The \verb$__class__$
+  \item \verb$itk.class_(object)$ return the class of an object. The \verb$__class__$
 attribute is often not what the user want with ITK. \verb$itk.class_$ is a convenient
@@
 
-% In WrapITK/ExternalProjects there are several sample "External Projects" that
-% can be built to provide additional functionality to WrapITK and to serve as a
-% demonstration for how to create your own such projects. One project is an
-% ITK-VTK bridge, and the other is a Python class to allow conversion from
-% Numeric/Numarray/numpy matrices to ITK images (and vice-versa).
+External projects let the developer access some custom class with the target languages
+and is a powerful way to extend WrapITK, test new wrapper, wrap more types, etc.
+A nice side effect of wrappers, for contributions\footnote{A nice template for
+contributions to the Insight Journal \cite{InsightJournalWebSite} which include the 
+temlate code to build wrappers is available at
+\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/template/}. Just use the command
+{\em darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/template/ contribName}
+and edit the project name in the {\em CMakeLists.txt} file to
+begin your new contribution.} for example, is to build {\em all}
+the methods of the wrapped classes, and so to be sure everything builds as it should
+\footnote{We have found and fixed numbers of bug in ITK while adding
+more classes to WrapITK}.
 
@@
 directory.
+
+    \subsubsection{Examples}
+
+In \verb$WrapITK/ExternalProjects$ there are several sample "External Projects" that
+can be built to provide additional functionality to WrapITK and to serve as a
+demonstration for how to create your own such projects. One project is an
+ITK-VTK \cite{VtkWebSite} bridge, and the other is a Python class to allow conversion from
+Numeric/Numarray/numpy \cite{NumericWebSite,NumarrayWebSite,NumpyWebSite} matrices to
+ITK images (and vice-versa).
+
+More examples can be found in the contributions to the Insight Journal
+\cite{InsightJournalWebSite}, or directly at \url{http://voxel.jouy.inra.fr/darcsweb/}.
 

### 2006-03-23 article/Article.tex
typo, and complete Benoit s affiliation
darcs-hash:20060323161337-2fc9d-954e146a5562f1d439051e7e7dd1292dc5048b88.gz

@@
 {$^2$}Stanford University, CA 94305, USA\\
-{$^3$}Creatis, CNRS, 69621 Villeurbanne, France}
+{$^3$}CREATIS, CNRS UMR 5515, 69621 Villeurbanne, France}
 
@@
 
-  \item Finally, \verb$WRAPPER_LIBRARY_CREATE_LIBRARY()$ creates rules to parse the CalbeSwig
+  \item Finally, \verb$WRAPPER_LIBRARY_CREATE_LIBRARY()$ creates rules to parse the CableSwig
 inputs and compile a wrapper library. This macro also causes various language

### 2006-03-24 article/Article.tex
fix some typo
darcs-hash:20060324081819-2fc9d-161f3e6a7a004d287d3b6ab9dcc31a97f0aab329.gz

@@
 
-  \item  The template arguments set is poorly choosen, making sometime impossible
+  \item  The template arguments set is poorly chosen, making sometime impossible
 to create a pipeline. In WrapITK, most of the filters have the same input and output
@@
 
-  \item  Names in target laguages are inconsistents. WrapITK use a strict naming
+  \item  Names in target languages are inconsistent. WrapITK use a strict naming
 convention which should make easier to identify the template arguments.
@@
 comes with a new well designed python module easy to use in interpreter, and
-aproviding run-time lookup of templated types - thing which can't be easily done
+providing run-time lookup of templated types - thing which can't be easily done
 in C++. Additionally, WrapITK ensures that \verb$SmartPointer$s are always
@@
 simply issue the command \verb$import itk$, and you are ready to go. This
-is because WrapITK installs a pth file in the python \verb$site-packages$ directory so
+is because WrapITK installs a \verb$.pth$ file in the python \verb$site-packages$ directory so
 that python knows where to find the itk scripts.
@@
 
-A more convenient syntaxe for usage in interpreter is also available:
+A more convenient syntax for usage in interpreter is also available:
 \begin{itemize}
@@
 
-Losts of classes have a \verb$New()$ method which returns a smart pointer to that class. The
+Lots of classes have a \verb$New()$ method which returns a smart pointer to that class. The
 \verb$New()$ method in python has some additional features:
@@
 
-and, more important, most of classes can be instanciated and parametered in one line,
+and, more important, most of classes can be instantiated and parametered in one line,
 which make ITK less verbose, and a lots more easy to use in the interpreter.
@@
 To set the same radius for all dimensions, it is possible to use the \verb$*$ python
-sequence operator - that way, it is possible to write code independant of dimension.
+sequence operator - that way, it is possible to write code independent of dimension.
 
@@
   \item \verb$itk.strel(d, s)$ is used to create a binary ball structuring of dimension
-\verb$d$ and size \verb$s$. Strucutring element support is quite bad currently in WrapITK
+\verb$d$ and size \verb$s$. Structuring element support is quite bad currently in WrapITK
 and should change in the future. Using \verb$itk.strel$ rather than creating a
@@
 \begin{itemize}
-  \item make creation of wrappers easy. The syntax is simple enough to get in quickely.
+  \item make creation of wrappers easy. The syntax is simple enough to get in quickly.
   \item make choice of template arguments explicit. It should be easy to understand
@@
 
-  \item \verb$WRAP_ITK_ALL_TYPES$ contains all the types selected byt the user.
+  \item \verb$WRAP_ITK_ALL_TYPES$ contains all the types selected by the user.
 
@@
 contributions to the Insight Journal \cite{InsightJournalWebSite} which include the 
-temlate code to build wrappers is available at
+template code to build wrappers is available at
 \url{http://voxel.jouy.inra.fr/darcs/contrib-itk/template/}. Just use the command

### 2006-03-24 article/Article.tex
additions from Zach and Benoit
darcs-hash:20060324105919-2fc9d-b984f2f8aabd69fddc872c0925c10e98c7e36b50.gz

@@
 \authoraddress{{$^1$}Unit\'e de Biologie du D\'eveloppement et de la Reproduction, Institut National de la Recherche Agronomique, 78350 Jouy-en-Josas, France\\
-{$^2$}Stanford University, CA 94305, USA\\
+{$^2$}Program in Biomedical Informatics and Department of Biochemistry, Stanford University School of Medicine, Stanford, California\\
 {$^3$}CREATIS, CNRS UMR 5515, 69621 Villeurbanne, France}
@@
 
-\end{itemize}
-
-Currently, WrapITK have been tested on Mandriva Linux, and MacOS X, and only
+  \item ITK was broken on MacOS X \cite{MacOsXWebSite} with python.
+
+\end{itemize}
+
+Currently, WrapITK have been tested on Mandriva Linux \cite{MandrivaWebSite}, and MacOS X, and only
 supports Python properly; Java and Tcl libraries build
-correctly but the Java and Tcl support classes for loading these libraries needs
-some updating.
+correctly but the Java and Tcl support classes for loading these libraries is
+entirely out of date and is not working.
 
@@
 
+On linux boxes however, the user have to set the \verb$LD_LIBRARY_PATH$ to
+point to libSwigRuntime.so. For example
+\verb$export LD_LIBRARY_PATH=/usr/lib/InsightToolkit/WrapITK/Python-SWIG$.
+
 If WrapITK has not been installed, then you will either need to set the
@@
   \item \verb$Vector$
+  \item \verb$ContinuousIndex$
 \end{itemize}
@@
   \item \verb$itk.image(object)$ try to return an image from the object given in
-parameter. This function is used in most of the next functions to allow the user to
-pass an image or a filter.
+parameter. If the object is an image, it is returned without changes. If the object
+is a filter, the object returned by \verb$GetOutput()$ metyhod is returned.
+This function is used in most of the next functions to allow the user to
+pass an image or a filter, and is available here for the same usage in some custom
+fuctions.
 
@@
 \verb$UpdateOutputInformation()$ and \verb$Update()$.
+
+This function is only a convenient function for a common task while prototyping.
 
@@
 
+This function is only a convenient function for a common task while prototyping.
+
 Example:
@@
 support the python \verb$commands$ module, and which have \verb$groff$ in the path. This
-basically means anything but windows will work. (Cygwin should work too.)
+basically means anything but windows \cite{WindowsWebSite} will work. (Cygwin should work too.)
 
@@
 
-\verb$WRAP_CLASS$ issues an implicit call to \verb$WRAP_INCLUDE("ClassName.h")$, so the header
+\verb$WRAP_CLASS("itk::ImageFilter")$ issues an implicit call to \verb$WRAP_INCLUDE("itkImageFilter.h")$, so the header
 for the wrapped class itself does not need to be manually included. To disable
@@
 ITK-style code where the class has a typedef'd \verb$Superclass$, and the superclass
-has \verb$Self$ and \verb$Pointer$ typedefs.)
+has \verb$Self$ and \verb$Pointer$ typedefs). \verb$POINTER_WITH_SUPERCLASS$ is especially
+useful for wrapping classes whose superclasses depend on the template definitions of the given
+filter. E.g. any of the functor image filters, which define  totally different superclass
+template parameters depending on which functor is used.
 
@@
 classes to wrap come from the same header file.
+\verb$WRAPPER_AUTO_INCLUDE_HEADERS$ is re-set to \verb$ON$ for each new \verb$wrap_xxx.cmake$ file.
 
@@
 Some convenient macros are available to wrap image filters.
+
+These macros often take an optional second parameter which is a "dimensionality
+condition" to restrict the dimensions that theis filter will be instantiated
+for. The condition can either be a single number indicating the one dimension
+allowed, a list of dimensions that are allowed (either as a single \verb$-$delimited
+string or just a set of separate parameters), or something of the form \verb$n+$
+(where \verb$n$ is a number) indicating that instantiations are allowed for dimension
+n and above.
 
@@
 which filter instantiations should be created. The second is a \verb$param_count$
-parameter which controls how many image template parameters are created (see
-above). The optional third parameter is a dimensionality condition (see above
-also).
+parameter which controls how many image template parameters are created. The
+optional third parameter is a dimensionality condition.
 
@@
 To build an external project, first ensure that WrapITK has been properly built.
-Then use ccmake to configure a build directory for the external project. If
+Then use \verb$ccmake$ to configure a build directory for the external project. If
 WrapITK has not been installed, you will have to manually enter the path to the
 WrapITK build directory.
+
+By default, the build options are the same than the one used for building WrapITK,
+but can be modified in the advanced options.
 
@@
 
+Write me.
+
     \subsubsection{ItkVtkGlue: an example of extension for all languages, including C++}
 
+ItkVtkGlue wrap the classes used to convert data from ITK to VTK \cite{VtkWebSite} and from VTK to ITK.
+Those classes comes from the InsightApplications \cite{ITKWebSite}, and make the conversion
+as simple in python as in C++. It has been tested with VTK 5.0.0.
+
+By default, those classes are not loaded in the \verb$itk$ module to avoid loading
+all the \verb$vtk$ module while importing \verb$itk$. The command \verb$import itkvtk$
+will load the module, and add the classes both in \verb$itkvtk$ and\verb$itk$ module.
+The classes are then usable as the other itk classes.
+
+Example:
+\begin{verbatim}
+1> import itk
+
+2> import itkvtk
+
+3> reader = itk.ImageFileReader.IUC3.New()
+
+4> converter = itk.ImageToVTKImageFilter.IUC3.New(reader)
+
+5> converter.GetOutput()
+5> <libvtkFilteringPython.vtkImageData vtkobject at 0xb7675b60>
+\end{verbatim}
+
+The \verb$itk.show3D$ class use the class \verb$ImageToVTKImageFilter$ to create the
+volume rendering shown in Figure \ref{screenshot}.
+
   \subsection{Extending language support and adding more languages}
 
+Write me.
+
     \subsubsection{Generating target language code}
 
+Write me.
+
     \subsubsection{typemaps}
+
+Write me.
 
@@
 
-I also thank Richard Beare for his early interest in using itk with python, and for
-his useful feedbacks.
-
-We thank Charl P. Botha for is help to debug WrapITK on windows plateform, and for the
-patches he has contributed.
+We would like to thank Charl P. Botha for is help to debug WrapITK on windows
+plateform, and for the patches he has contributed, as well as Richard Beare for
+his early interest in using itk with python, for his useful feedbacks, and for
+his work on buffer conversion in python.
+
+We thank Brad King for his assistance during the development process.
 

### 2006-03-24 article/Article.tex
fix some typo
darcs-hash:20060324161341-2fc9d-ff61171a134722adff2f3f4d7a5ed5eb955b82d3.gz

@@
 parameter. If the object is an image, it is returned without changes. If the object
-is a filter, the object returned by \verb$GetOutput()$ metyhod is returned.
+is a filter, the object returned by \verb$GetOutput()$ method is returned.
 This function is used in most of the next functions to allow the user to
@@
 These macros often take an optional second parameter which is a "dimensionality
-condition" to restrict the dimensions that theis filter will be instantiated
+condition" to restrict the dimensions that the filter will be instantiated
 for. The condition can either be a single number indicating the one dimension
@@
 all the \verb$vtk$ module while importing \verb$itk$. The command \verb$import itkvtk$
-will load the module, and add the classes both in \verb$itkvtk$ and\verb$itk$ module.
+will load the module, and add the classes both in \verb$itkvtk$ and \verb$itk$ module.
 The classes are then usable as the other itk classes.

### 2006-03-26 Python/Tests/simple_pipeline.py
first work to run tests with ctest
darcs-hash:20060326193311-2fc9d-f02a42a31f55aef7ef2e0659d57a762d5c6d6ed6.gz

@@ -3,7 +3,7 @@
 import itk, sys
 
 # first argument is the pixel type
-PType = itk.ctype(sys.argv[1])
+PType = getattr(itk, sys.argv[1])
 # second arguement the image dimension
 dim = int(sys.argv[2])
 

### 2006-03-26 Python/Tests/template.py

@@ -3,7 +3,7 @@
 import itk
 
 dim = 2
-PType = itk.UC
+PType = itk.US
 
 # check the repr string
 assert "<itkTemplate itk::Image>" == repr(itk.Image)
@@ -21,7 +21,7 @@ im2 = IType.New()
 
 readerType = itk.ImageFileReader[IType]
 readerType2 = itk.ImageFileReader[im]
-readerType3 = itk.ImageFileReader.IUC2
+readerType3 = itk.ImageFileReader.IUS2
 
 assert readerType == readerType2 == readerType3
 

### 2006-03-26 Python/Tests/typemaps.py

@@ -31,7 +31,7 @@ size4 = itk.Size[2](i)
 assert size1.GetElement(0) == size2.GetElement(0) == size3.GetElement(0) == size4.GetElement(0) == i
 assert size1.GetElement(1) == size2.GetElement(1) == size3.GetElement(1) == size4.GetElement(1) == i
 
-median = itk.MedianImageFilter.IUC2IUC2.New()
+median = itk.MedianImageFilter.IUS2IUS2.New()
 median.SetRadius(size)
 size1 = median.GetRadius()
 median.SetRadius(t)
@@ -45,7 +45,7 @@ assert size1.GetElement(1) == size2.GetElement(1) == size3.GetElement(1) == size
 
 
 # smart pointers
-im = itk.Image.UC2.New()
+im = itk.Image.US2.New()
 assert im.GetPointer() != None
 assert im.GetPointer().__class__ != im.__class__
 

### 2006-03-26 Tests/Python/testPrint.py

@@ -1,13 +1,0 @@
-from InsightToolkit import *
-from itkPython import *
-import sys
-
-reader = itkImageFileReaderIUC2.New()
-reader.SetFileName("C:/Creatis/homersbrain.bmp")
-reader.Update()
-
-print "Reader : "
-itkPrint(reader)
-print "Reader Output : "
-itkPrint(reader.GetOutput())
-

### 2006-03-26 Tests/Python/testTemplate.py

@@ -1,26 +1,0 @@
-from itkPython import *
-
-print "#######################################################################"
-print itkImage
-print "-----------------------------------------------------------------------"
-for elt in itkImage.keys():
-   print elt
-print "-----------------------------------------------------------------------"
-for elt in itkImage.items():
-   print elt
-print "-----------------------------------------------------------------------"
-print itkImage[itkUS,2]
-print
-print "#######################################################################"
-print itkDifferenceImageFilter
-print "-----------------------------------------------------------------------"
-for elt in itkDifferenceImageFilter.keys():
-   print elt
-print "-----------------------------------------------------------------------"
-for elt in itkDifferenceImageFilter.items():
-   print elt
-print "-----------------------------------------------------------------------"
-print itkDifferenceImageFilter[itkImage[itkUS,2],itkImage[itkUS,2]]
-print itkDifferenceImageFilter[itkImage[itkUS,2].New(),itkImage[itkUS,2]]
-print itkDifferenceImageFilter[itkImage[itkUS,2].New().GetPointer(),itkImage[itkUS,2]]
-

### 2006-03-26 Tests/Python/testTemplateUse.py

@@ -1,23 +1,0 @@
-import InsightToolkit as itk
-import itkPython as itkPy
-
-#########################################################
-reader = itk.itkImageFileReaderIUC2_New()
-reader.SetFileName("C:/Creatis/homersbrain.bmp")
-
-writer = itkPy.itkImageFileWriter[reader.GetOutput()].New()
-writer.SetInput(reader.GetOutput())
-
-writer.SetFileName("./testout1.png")
-writer.Update()
-
-#########################################################
-reader = itkPy.itkImageFileReader[itkPy.itkImage[itkPy.itkUC,2]].New()
-reader.SetFileName("C:/Creatis/homersbrain.bmp")
-
-writer = itkPy.itkImageFileWriter[reader.GetOutput()].New()
-writer.SetInput(reader.GetOutput())
-
-writer.SetFileName("./testout2.png")
-writer.Update()
-

### 2006-03-26 Python/Tests/itk-functions.py
use unsigned short instead of unsigned char for tests
darcs-hash:20060326212324-2fc9d-bc8dc99c10e615e817f8c64812b1d067cbc92cf9.gz

@@ -10,7 +10,7 @@ import itk, sys
 
 fileName = sys.argv[1]
 
-PType = itk.UC
+PType = itk.US
 dim = 2
 IType = itk.Image[PType, dim]
 ReaderType = itk.ImageFileReader[IType]
@@ -37,8 +37,8 @@ except KeyError:
   pass
 
 # test ctype
-assert itk.ctype("unsigned char") == itk.UC
-assert itk.ctype("        unsigned      \n   char \t  ") == itk.UC
+assert itk.ctype("unsigned short") == itk.US
+assert itk.ctype("        unsigned      \n   short \t  ") == itk.US
 try:
   itk.ctype("dummy")
   raise Exception("unknown C type should send an exception")

### 2006-04-03 Python/PyUtils/itkPyImageFilter.h
add a class able to run python code during the execution of a pipeline
darcs-hash:20060403183940-2fc9d-9cb13c9d6b67629d45badfa090dfa66d4a9f3577.gz

@@ -1,0 +1,96 @@
+/*=========================================================================
+
+  Program:   Insight Segmentation & Registration Toolkit
+  Module:    $RCSfile: itkPyImageFilter.h,v $
+  Language:  C++
+  Date:      $Date: 2005/03/25 13:17:57 $
+  Version:   $Revision: 1.1 $
+
+  Copyright (c) Insight Software Consortium. All rights reserved.
+  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
+
+     This software is distributed WITHOUT ANY WARRANTY; without even 
+     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
+     PURPOSE.  See the above copyright notices for more information.
+
+=========================================================================*/
+#ifndef _itkPyImageFilter_h
+#define _itkPyImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+// The python header defines _POSIX_C_SOURCE without a preceding #undef
+#undef _POSIX_C_SOURCE
+#include <Python.h>
+
+namespace itk
+{
+
+/** \Class PyImageFilter
+ *  \brief Command subclass that calls a Python callable object, e.g.
+ *  a Python function.
+ * 
+ * With this class, arbitrary Python callable objects (e.g. functions)
+ * can be associated with an instance to be used in AddObserver calls.
+ * This is analogous to itk::TclCommand, but then a tad more flexible. ;)
+ *
+ * This class was contributed by Charl P. Botha <cpbotha |AT| ieee.org>
+ */
+
+
+template <class TInputImage, class TOutputImage>
+class ITK_EXPORT PyImageFilter : public ImageToImageFilter<TInputImage,TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef PyImageFilter  Self;
+  typedef ImageToImageFilter<TInputImage,TOutputImage>  Superclass;
+  typedef SmartPointer<Self>   Pointer;
+  typedef SmartPointer<const Self>  ConstPointer;
+
+  /** Method for creation through the object factory. */
+  itkNewMacro(Self);
+
+  /** Run-time type information (and related methods). */
+  itkTypeMacro(PyImageFilter, ImageToImageFilter);
+
+  /** Some convenient typedefs. */
+  typedef TInputImage InputImageType;
+  typedef typename    InputImageType::Pointer    InputImagePointer;
[…]

### 2006-04-04 ExternalProjects/MultiThreaderControl/itkMultiThreaderStub.h
Add MultiThreaderController external project
darcs-hash:20060404183952-733a7-5c33c3de644a6d4fb9ad82c0879f2e240f457d7e.gz

@@ -1,7 +1,7 @@
-#if !(defined(CABLE_CONFIGURATION) && defined(WIN32))
-// gcc-xml cannot be allowed to see the full MultiThreader header on 
-// windows. If we're not gcc_xml or not on windows, just pass through to the
-// proper header.
+#ifndef CABLE_CONFIGURATION
+// This file should *only* ever be included on windows systems!
+// gcc-xml cannot be allowed to see the full MultiThreader header.
+// If we're not gcc_xml, just pass through to the proper header.
 #include "itkMultiThreader.h"
 #else
 // Here follows the restricted header made available just to gcc-xml on windows.
@@ -72,8 +72,10 @@ public:
     static void Initialize();
 #endif
     friend class ProcessObject;
+private:
+  int                        m_NumberOfThreads;
   }; 
   
 }  // end namespace itk
 #endif // ifndef stuff
-#endif // end if CABLE_CONFIGURATION and WIN32
+#endif // end if CABLE_CONFIGURATION

### 2006-04-04 CommonA/itkConstantBoundaryConditionStub.h
Fix BoundaryCondition windows compilation problems
darcs-hash:20060404184109-733a7-01d32e994965fc4e7d913c0dcea265dd6d671966.gz

@@ -1,7 +1,7 @@
-#if !(defined(CABLE_CONFIGURATION) && defined(WIN32))
-// gcc-xml cannot be allowed to see the full ConstantBoundaryCondition header on 
-// windows. If we're not gcc_xml or not on windows, just pass through to the
-// proper header.
+#ifndef CABLE_CONFIGURATION
+// This file should *only* ever be included on windows systems!
+// gcc-xml cannot be allowed to see the full ConstantBoundaryCondition header.
+// If we're not gcc_xml, just pass through to the proper header.
 #include "itkConstantBoundaryCondition.h"
 #else
 // Here follows the restricted header made available just to gcc-xml on windows.
@@ -53,4 +53,4 @@ public:
 } // end namespace itk
 
 #endif // ifndef stuff
-#endif // end if CABLE_CONFIGURATION and WIN32
+#endif // end if CABLE_CONFIGURATION

### 2006-04-10 article/Article.tex
add bugtracker url and reference
darcs-hash:20060405145241-2fc9d-b2a2fc6c9c6e35f9d422e1abfb5b61027fbbbd05.gz
article continued
darcs-hash:20060410155846-2fc9d-29b6f0fc7eca3e02d23dceb170673d564602a13e.gz

@@
 
-Currently, WrapITK have been tested on Mandriva Linux \cite{MandrivaWebSite}, and MacOS X, and only
-supports Python properly; Java and Tcl libraries build
-correctly but the Java and Tcl support classes for loading these libraries is
-entirely out of date and is not working.
-
 The article you're reading is not as nice and complete than what we would have
@@
 
+\section{Supported languages and plateforms}
+
+Java, Tcl and Python builds properly and are fully usable. However, Java and
+Tcl don't yet have the extended features added to Python\footnote{Any help
+to extend Java and Tcl support would be higly appreciated.}.
+
+WrapITK is mainly developed on Mandriva Linux \cite{MandrivaWebSite} and 
+MacOS X \cite{MacOsXWebSite} and so is well tested on this palteforms.
+It also builds on windows \cite{WindowsWebSite}, but require more testing
+to be sure everything work as it should. See below for details about how
+to report bugs are contribute patches.
+
+Several tests are available\footnote{There is currently 49 tests with the default
+configuration.} for Python, Tcl and Java. They can be run with the \verb$ctest$
+command.
+
+\section{Performance}
+
 \section{User guide}
@@
 
-    \subsubsection{Get the software}
+    \subsubsection{Get the software sources}
 
@@
 
-To get the last version from the darcs repository can be obtained
-with the command 
-\verb$darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/$.
-
-For the user who don't want to use darcs \cite{DarcsWebSite} but want the last development version,
+The last version can be obtained from the development repository with darcs \cite{DarcsWebSite}.
+The command is
+\verb$darcs get --partial http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/$\footnote{Note
+that the {\em --partial} option is required on systems with case insensitive filesystem like
+windows or Mac Os X.}.
+
+For the user who don't want to use darcs \cite{DarcsWebSite} but still want the last development version,
 a nightly updated archive is available at
@@
 
-RPM packages for Mandriva Linux 2006 are available at \url{http://voxel.jouy.inra.fr/mdk/mima2}.
-
-% TODO: provide more binary packages - for mac and windows.
-
-    \subsubsection{CableSwig}
-
-WrapITK requires ITK and CableSwig to have been previously downloaded and built.
-To get CableSwig, simply run:
-\verb$cvs -d:pserver:anonymous@public.kitware.com:/cvsroot/CableSwig co CableSwig$
-(Note that no cvs login is needed here.)
-
-If you check out CableSwig into the \verb$Insight/Utilities$ directory, then it will be
-built as a part of ITK, and will be automatically detected by WrapITK when ITK
-is found.
-
-    \subsubsection{Required and optional patches}
+    \subsubsection{ITK}
 
@@
 for standard python sequence interface (see below).
+
+    \subsubsection{CableSwig}
+
+WrapITK requires ITK and CableSwig \cite{ITKWebSite} to have been previously downloaded and built.
+To get a development version of CableSwig, simply run:
+\verb$cvs -d:pserver:anonymous@public.kitware.com:/cvsroot/CableSwig co CableSwig$
+(Note that no cvs login is needed here.)
+
+If you check out CableSwig into the \verb$Insight/Utilities$ directory, then it will be
+built as a part of ITK, and will be automatically detected by WrapITK when ITK
+is found.
+
+    \subsubsection{Python}
+
+Python \cite{PythonWebSite} is required only to build python support.
+WrapITK is reported to work with python 2.3 and python 2.4. However, the test framework
+requires the \verb$subprocess$ module available in standard only in python 2.4 and above.
+To run the python test with python 2.3, you have to install \verb$subprocess$.
+
+    \subsubsection{Tcl}
+
+Tcl \cite{TclWebSite} is required only to build tcl support.
+WrapITK have been tested with Tcl 8.4.11.
+
+    \subsubsection{Java}
+
+Java \cite{JavaWebSite} is required only to build java support.
+WrapITK have been tested with java \verb$1.5.0_06-b05$.
 
@@
 
+    \subsubsection{Binary packages}
+
+RPM packages for Mandriva Linux 2006 are available at \url{http://voxel.jouy.inra.fr/mdk/mima2}.
+
+% TODO: provide more binary packages - for mac and windows.
+
   \subsection{Python usage}
@@
 \begin{itemize}
+  \item \verb$Array$
+  \item \verb$ContinuousIndex$
   \item \verb$CovariantVector$
@@
   \item \verb$Vector$
-  \item \verb$ContinuousIndex$
 \end{itemize}
@@
 more classes to WrapITK}.
+In WrapITK, we used them to avoid managing switches if some dependencies or not
+found: the project must found this dependencies or fail.
 
@@
 More examples can be found in the contributions to the Insight Journal
-\cite{InsightJournalWebSite}, or directly at \url{http://voxel.jouy.inra.fr/darcsweb/}.
+\cite{InsightJournalWebSite}, or directly at \url{http://voxel.jouy.inra.fr/darcs/contrib-itk/}.
 
@@
   \item Test it and report problem. That's the more important thing to do:
-we need feedbacks to enhance WrapITK quality !
+we need feedbacks to enhance WrapITK quality ! Report all bugs you may found
+to \url{http://voxel.jouy.inra.fr/roundup/wrapitk/} \cite{RoundupWebSite}.
   \item Work on tcl, java, and others. We are not tcl or java developers, and so
@@
 
-\verb$darcs$ \cite{DarcsWebSite} allow to easily contribute to WrapITK, by sending patch by email with
-the command \verb$darcs send$, while keeping credits for the work done.
+\verb$darcs$ \cite{DarcsWebSite} allow to easily contribute to WrapITK, by sending
+patch by email, while keeping credits for the work done.
 Feel free to send patches; they will be tested and integrated in the project.
+
+The basic commands to know are:
+\begin{itemize}
+
+  \item \verb$darcs get --partial http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/$
+to get a copy of WrapITK repository.
+
+  \item \verb$darcs whatsnew$ to display the changes you have done in
+your copy of the repository.
+
+  \item \verb$darcs record$ to record the changes you have made in your
+copy of the repository. darcs will propose you to select some changes
+to record. It is better to create one patch for each feature or bug
+fix, rather than one big patch for all your current changes.
+
+  \item \verb$darcs send$ to send by email the patches you have recorded with
+\verb$darcs record$.
+% TODO: which email adress ??
+
+\end{itemize}
+
+Read the {\em Getting started} section of the darcs manual \cite{DarcsWebSite}
+for more information.
 
@@
 
+We thank Andr\'e Bongers.
+
 We thank Brad King for his assistance during the development process.

### 2006-04-12 article/Article.tex
add more info about rpm packages
darcs-hash:20060412140251-2fc9d-fd487192e14648c319d7491857ffa284c169311a.gz

@@
 RPM packages for Mandriva Linux 2006 are available at \url{http://voxel.jouy.inra.fr/mdk/mima2}.
+To install WrapITK for mandriva linux 2006.0, just add a new media with the
+command
+
+\begin{verbatim}
+urpmi.addmedia mima2-2006.0 http://voxel.jouy.inra.fr/mdk/mima2/2006.0/i586/
+\end{verbatim}
+
+and install the package you want with
+
+\begin{verbatim}
+urpmi python-itk
+\end{verbatim}
+
+This media also contain several packages which may be useful to use WrapITK,
+and which are not available in mandriva linux 2006.0. Here is the full list:
+\begin{itemize}
+  \item \verb$cmake$
+  \item \verb$itk-data$
+  \item \verb$itk-doc$
+  \item \verb$itk-examples$
+  \item \verb$itkvtk-devel$
+  \item \verb$libitk$
+  \item \verb$libitk-devel$
+  \item \verb$libvtk$
+  \item \verb$libvtk-devel$
+  \item \verb$libvtk-qt$
+  \item \verb$python-itk$
+  \item \verb$python-itk-numarray$
+  \item \verb$python-itkvtk$
+  \item \verb$python-vtk$
+  \item \verb$tcl-itk$
+  \item \verb$tcl-vtk$
+  \item \verb$vtk-data$
+  \item \verb$vtk-doc$
+  \item \verb$vtk-examples$
+  \item \verb$vtk-test-suite$
+  \item \verb$wrapitk-devel$
+\end{itemize}
+
+WrapITK is also available in cooker, the development version of mandriva.
 
@@
 In WrapITK, we used them to avoid managing switches if some dependencies or not
-found: the project must found this dependencies or fail.
+found: the project must found its dependencies or fail.
 

### 2006-04-16 Python/Tests/notYetUsable/ResampleImageFilter1.py
switch to new wrapper syntax (not tested yet)
darcs-hash:20060416143357-2fc9d-eeb44c94b04bf377e56bd702f2abe2e364f200f5.gz

@@ -1,60 +1,34 @@
 
 
-from InsightToolkit import *
-
+import itk
 from sys import argv
 
+dim = 2
+PType = itk.US
+IType = itk.Image[PType, dim]
 
-scale = itkScaleTransform2_New()
-
-reader = itkImageFileReaderUS2_New()
-writer = itkImageFileWriterUS2_New()
-
-reader.SetFileName( argv[1] )
-writer.SetFileName( argv[2] )
-
-parameters = scale.GetParameters()
-
-parameters.SetElement( 0, eval( argv[3] ) )
-parameters.SetElement( 1, eval( argv[3] ) )
-
-reader.Update()
-
+reader = itk.ImageFileReader[IType].New(FileName=argv[1])
 inputImage = reader.GetOutput()
+# it is not required to update the filter: itk.size() update it
+# to get the information it needs
+size = itk.size(inputImage)
 
-size    = inputImage.GetLargestPossibleRegion().GetSize()
-
-centralPixel = itkIndex3()  
-
-centralPixel.SetElement( 0, size.GetElement(0) / 2 )
-centralPixel.SetElement( 1, size.GetElement(1) / 2 )
-
-centralPoint = itkPointD2() 
-
-spacing = inputImage.GetSpacing()
-
-interpolator = itkLinearInterpolateImageFunctionUS2D_New()
-
-centralPoint.SetElement(0, centralPixel.GetElement(0) )
-centralPoint.SetElement(1, centralPixel.GetElement(1) )
-
+scale = itk.ScaleTransform[itk.D, dim].New(Parameters=[eval( argv[3] ), eval( argv[3] )])
+# sequence typemap is not supported yet for itk::Point
+centralPoint = itk.Point[itk.D, dim]()
+centralPoint[0] = size[0] / 2.
+centralPoint[1] = size[1] / 2.
 scale.SetCenter( centralPoint )
-scale.SetParameters( parameters )
 
-resampler = itkResampleImageFilterUS2US2_New()
+interpolator = itkLinearInterpolateImageFunction[PType, dime, itk.D].New()
 
-resampler.SetInput( reader.GetOutput() )
-
+resampler = itkResampleImageFilter[IType, IType].New(reader)
 resampler.SetTransform( scale.GetPointer() )
 resampler.SetInterpolator( interpolator.GetPointer() )
 resampler.SetSize( size )
-resampler.SetOutputSpacing( spacing )
[…]

### 2006-04-18 article/Article.tex
some details in the article
darcs-hash:20060418140413-2fc9d-165bf780cd6b9e3db7d7fabb4a9e096f0e923d0d.gz

@@
   \item \verb$darcs send$ to send by email the patches you have recorded with
-\verb$darcs record$.
-% TODO: which email adress ??
+\verb$darcs record$. Please send your patches to the WrapITK bugtracker
+(wrapitk-bugmaster@jouy.inra.fr\footnote{Note that you must have an account to
+be able to send something to the bug tracker. Visit
+\url{http://voxel.jouy.inra.fr/roundup/wrapitk/} to create one.}) so everyone
+would be able to find it easily.
 
@@
 and to have a poor support for other languages than C++. WrapITK address those
-issue and finally give to ITK a quite good support for python. We hope that support
-will soon be extended to tcl and java.
+issue and finally give to ITK a good support for python. Java and Tcl, while
+not as much tweaked than python part, also take benefit of the higher number of
+wrapped classes, and of the increase of consistency in available types and names
 

### 2006-04-20 Python/itk.py
Allow lazy loading of ITK modules
darcs-hash:20060420230751-733a7-ee75b395b847116fa7941ee941ad308693efaa6d.gz

@@ -1,10 +1,5 @@
-
 # Auto-load the modules described in the itkConfig.config_py directory (usually
 # WrapITK/Python/Configuration, and populate the 'itk' namespace with the templates.
-
-from itkTypes import *
-del itkCType # we don't need that from itkTypes!
-
 import itkBase, itkConfig, os
 # First, find all the xxxConfig.py files in the config_py dir, and strip off the
 # 'Config.py' part of the filename.
@@ -20,265 +15,6 @@ for module in configModules:
 
 del itkBase, itkConfig, os
 
-
-# new features introduced by itk module
-# each new feature use a name in lower case
-
-def auto_progress( b ):
-  import itkTemplate
-  itkTemplate.auto_progress = b
-  
-
-# Function to print itk object info
-import sys
-def echo(object, f=sys.stderr) :
-   ss = StringStream()
-   try :
-      try:
-         object.Print(ss.GetStream())
-      except:
-         object.Print(ss.GetStream(),Indent.New());
-   except:
-      print >> f, repr(object)
-   else:
-      print >> f, ss.GetString()
-del sys
-
-# return the size of an imageClass
-def size(imageOrFilter) :
-  # we don't need the entire output, only its size
-  imageOrFilter.UpdateOutputInformation()
-  img = image(imageOrFilter)
-  return img.GetLargestPossibleRegion().GetSize()
-  
-# return a structuring elt
-def strel(dim, radius=1) :
-  st = BinaryBallStructuringElement[B, dim]()
-  st.SetRadius(radius)
-  # call the boring CreateStructuringElement() method
-  st.CreateStructuringElement()
-  return st
-  
-# return an image
-from itkTemplate import image
-
-# return the template of a class and its parameters
-def template(cl) :
-  from itkTemplate import itkTemplate
-  return itkTemplate.__class_to_template__[class_(cl)]
-  
-# return ctype
-def ctype(s) :
-  from itkTypes import itkCType
-  ret = itkCType.GetCType(" ".join(s.split()))
-  if ret == None :
-    raise KeyError("Unrecognized C type '%s'" % s)
-  return ret
-  
-# return a class from an instance
-def class_(obj) :
-  import inspect
-  if inspect.isclass(obj) :
-    # obj is already a class !
-    return obj
-  else :
[…]

### 2006-04-20 Python/itkBase.py

@@ -19,7 +19,7 @@ def LoadModule(name, namespace = None):
   # if this library and it's template instantiations have already been loaded
   # into sys.modules, bail out after loading the defined symbols into 'namespace'
   if hasattr(this_module, '__templates_loaded'):
-    if namespace:
+    if namespace is not None:
         swig = namespace.setdefault('swig', imp.new_module('swig'))
         swig.__dict__.update(this_module.swig.__dict__)
 
@@ -72,10 +72,10 @@ def LoadModule(name, namespace = None):
   # between this_module and namespace.
   
   this_module.swig = imp.new_module('swig')
-  if namespace: swig = namespace.setdefault('swig', imp.new_module('swig'))
+  if namespace is not None: swig = namespace.setdefault('swig', imp.new_module('swig'))
   for k, v in module.__dict__.items():
     if not k.startswith('__'): setattr(this_module.swig, k, v)
-    if namespace and not k.startswith('__'): setattr(swig, k, v)
+    if namespace is not None and not k.startswith('__'): setattr(swig, k, v)
 
   data = module_data[name]
   if data:
@@ -90,7 +90,7 @@ def LoadModule(name, namespace = None):
         try: templateContainer.__add__(templateParams, getattr(module, swigClassName))
         except Exception, e: DebugPrintError("%s not loaded from module %s because of exception:\n %s" %(swigClassName, name, e))
         setattr(this_module, pyClassName, templateContainer)
-        if namespace:
+        if namespace is not None:
           current_value = namespace.get(pyClassName)
           if current_value != None and current_value != templateContainer:
             DebugPrintError("Namespace already has a value for %s, which is not an itkTemplate instance for class %s. Overwriting old value." %(pyClassName, cppClassName))
@@ -103,7 +103,7 @@ def LoadModule(name, namespace = None):
         except Exception, e: DebugPrintError("%s not found in module %s because of exception:\n %s" %(swigClassName, name, e))
         itkTemplate.registerNoTpl(cppClassName, swigClass)
         setattr(this_module, pyClassName, swigClass)
-        if namespace:
+        if namespace is not None:
           current_value = namespace.get(pyClassName)
           if current_value != None and current_value != swigClass:
             DebugPrintError("Namespace already has a value for %s, which is not class %s. Overwriting old value." %(pyClassName, cppClassName))

### 2006-04-20 Python/itkExtras.py

@@ -1,0 +1,261 @@
+# new features introduced by itk module
+# each new feature use a name in lower case
+
+def auto_progress( b ):
+  import itkTemplate
+  itkTemplate.auto_progress = b
+  
+
+# Function to print itk object info
+import sys
+def echo(object, f=sys.stderr) :
+   ss = StringStream()
+   try :
+      try:
+         object.Print(ss.GetStream())
+      except:
+         object.Print(ss.GetStream(),Indent.New());
+   except:
+      print >> f, repr(object)
+   else:
+      print >> f, ss.GetString()
+del sys
+
+# return the size of an imageClass
+def size(imageOrFilter) :
+  # we don't need the entire output, only its size
+  imageOrFilter.UpdateOutputInformation()
+  img = image(imageOrFilter)
+  return img.GetLargestPossibleRegion().GetSize()
+  
+# return a structuring elt
+def strel(dim, radius=1) :
+  st = BinaryBallStructuringElement[B, dim]()
+  st.SetRadius(radius)
+  # call the boring CreateStructuringElement() method
+  st.CreateStructuringElement()
+  return st
+  
+# return an image
+from itkTemplate import image
+
+# return the template of a class and its parameters
+def template(cl) :
+  from itkTemplate import itkTemplate
+  return itkTemplate.__class_to_template__[class_(cl)]
+  
+# return ctype
+def ctype(s) :
+  from itkTypes import itkCType
+  ret = itkCType.GetCType(" ".join(s.split()))
+  if ret == None :
+    raise KeyError("Unrecognized C type '%s'" % s)
+  return ret
+  
+# return a class from an instance
+def class_(obj) :
+  import inspect
+  if inspect.isclass(obj) :
+    # obj is already a class !
+    return obj
+  else :
+    # First, drop the smart pointer
+    try:
+      obj = obj.GetPointer()
+    except:
+      pass
+    # try to get the real object if elt is a pointer (ends with Ptr)
+    try:
+      cls = obj.__dict__[obj.__class__]
+    except:
+      cls = obj.__class__
+    # finally, return the class found
+    return cls
+
+# return range
+def range(imageOrFilter) :
+  img = image(imageOrFilter)
+  img.UpdateOutputInformation()
+  img.Update()
[…]

### 2006-04-20 Python/itkLazy.py

@@ -1,0 +1,46 @@
+from types import ModuleType
+import sys, os
+import itkBase, itkConfig, itkTypes, itkExtras
+
+class NotLoaded(object):
+  def __init__(self):
+    raise RuntimeError('Not Loaded')
+
+class LazyModuleType(ModuleType):  
+  def __init__(self, attr_to_module_map, loader):
+    self.attr_to_module_map = attr_to_module_map
+    self.module_to_attr_map = {}
+    for (attr, module) in attr_to_module_map.items():
+      self.module_to_attr_map.setdefault(module, []).append(attr)
+    self.loader = loader
+    self.__dict__.update( (attr, NotLoaded) for attr in attr_to_module_map.keys() )
+  def __getattribute__(self, attr):
+    value = ModuleType.__getattribute__(self, attr)
+    if value is NotLoaded:
+      module = self.attr_to_module_map[attr]
+      namespace = {}
+      self.loader(module, namespace)
+      # put things in namespace first, then self.__dict__ to prevent warnings
+      # about overwriting the 'NotLoaded' values already in self.__dict__
+      self.__dict__.update(namespace)
+      value = self.__dict__[attr]
+    return value 
+
+
+# First, find all the xxxConfig.py files in the config_py dir, and strip off the
+# 'Config.py' part of the filename.
+configModules = [f[:-9] for f in os.listdir(itkConfig.config_py) if f.endswith('Config.py')]
+configModules.sort()
+attr_to_module_map = {}
+for module in configModules:
+  templateNames = [t[0] for t in itkBase.module_data[module].templates]
+  attr_to_module_map.update( (n, module) for n in templateNames)
+
+itk = LazyModuleType(attr_to_module_map, itkBase.LoadModule)
+
+itk.__dict__.update( (k, v) for k, v in itkTypes.__dict__.items() if not k.startswith('__'))
+itk.__dict__.update( (k, v) for k, v in itkExtras.__dict__.items() if not k.startswith('__'))
+del itk.__dict__['itkCType']
+sys.modules['itk'] = itk
+
+del sys, os, itkBase, itkConfig, LazyModuleType, itkTypes, itkExtras

### 2006-04-22 Python/itk.py
LazyLoading default
darcs-hash:20060422000312-733a7-e21842674977042712f67c3ebbc35d6500624606.gz

@@ -1,20 +1,31 @@
-# Auto-load the modules described in the itkConfig.config_py directory (usually
-# WrapITK/Python/Configuration, and populate the 'itk' namespace with the templates.
-import itkBase, itkConfig, os
-# First, find all the xxxConfig.py files in the config_py dir, and strip off the
-# 'Config.py' part of the filename.
-configModules = [f[:-9] for f in os.listdir(itkConfig.config_py) if f.endswith('Config.py')]
-configModules.sort()
+"""itk.py : Top-level container module for ITK wrappers."""
+import itkBase, itkConfig, itkLazy, itkTypes, itkExtras, os, sys
 
-for module in configModules:
-  # If the configuration defines an auto_load attribute and it's set to True
-  # then load the module into the global 'itk' namespace
-  if ( hasattr(itkBase.module_data[module], 'auto_load') and 
-       itkBase.module_data[module].auto_load == True ):
-    itkBase.LoadModule(module, globals())
+if itkConfig.LazyLoading:
+  # If we are loading lazily (on-demand), make a dict mapping the available 
+  # classes/functions/etc. (read from the configuration modules) to the 
+  # modules they are declared in. Then pass that dict to a LazyITKModule
+  # instance and do some surgery on sys.modules so that the 'itk' module
+  # becomes that new instance instead of what is executed from this file.
+  lazyAttributes = {}
+  for module, data in itkBase.module_data.items():
+    templateNames = [ t[0] for t in data['templates'] ]
+    lazyAttributes.update( (n, module) for n in templateNames)
+  sys.modules[__name__] = itkLazy.LazyITKModule(__name__, lazyAttributes)
+else: 
+  # Load the modules in the order specified in the known_modules list
+  # for consistency.
+  for module in itkBase.known_modules:
+      itkBase.LoadModule(module, globals())
 
-del itkBase, itkConfig, os
+# Now load up the itk module (either this module, or the LazyITKModule
+# instance created above) with the types and extras information.
+thisModule =  sys.modules[__name__]
+for k, v in itkTypes.__dict__.items():
+  if k != 'itkCType': setattr(thisModule, k, v)
+for k, v in itkExtras.__dict__.items():
+  setattr(thisModule, k, v)
 
-from itkTypes import *
-del itkCType
-from itkExtras import *
+# Clean up the namespace -- only matters if we aren't using lazy loading.
+del configModules, module, thisModule
+del itkBase, itkConfig, itkLazy, itkTypes, itkExtras, os, sys

### 2006-04-22 Python/itkBase.py

@@ -47,7 +47,7 @@ def LoadModule(name, namespace = None):
   # to find those configuration files.
   data = module_data[name]
   if data:
-    deps = list(data.depends)
+    deps = list(data['depends'])
     deps.sort()
     for dep in deps:
       LoadModule(dep, namespace)
@@ -79,7 +79,7 @@ def LoadModule(name, namespace = None):
 
   data = module_data[name]
   if data:
-    for template in data.templates:
+    for template in data['templates']:
       if len(template) == 4: 
         # this is a template description      
         pyClassName, cppClassName, swigClassName, templateParams = template
@@ -173,46 +173,13 @@ class LibraryLoader(object):
       except: pass
 
 
-class ModuleData(dict):
-  """A dictionary that knows how to look up module configuration data from the
-  auto-generated configuration files. The location of these files is specified in
-  itkConfig."""
-  
-  def __getitem__(self, key):
-    try:
-      return dict.__getitem__(self, key)
-    except KeyError:
-      # search order for keyConfig.py: 
-      # (1) itkConfig.config_py directory
-      # (2) __file__/Configuration
-      # (3) ./Configuration
-      # (4) .
-      data = self.__find_file(key,
-        [itkConfig.config_py, os.path.join(__file__, 'Configuration'), 'Configuration', '.'])
-      if data:
-        return data
-      else:
-        DebugPrintError("Could not find configuration data for module %s." %key)
-        
-  def __find_file(self, module, paths):
-    configFile = "%sConfig.py" %module
-    for path in paths:
-      try: listing = os.listdir(path)
-      except: continue
-      if configFile in listing:
-        result = self.AttributeDict() # so we can write 'result.depends, etc., instead of result['depends']'
-        execfile(os.path.join(path, configFile), result)
-        self[file] = result
-        return result
-    return None
-  
-  class AttributeDict(dict):
-    """A dictionary that can be accessed with __getattribute__, so that d[key] or
-    d.key both return the value for that key."""    
-    def __getattribute__(self, key):
-      try:
-        return self[key]
-      except:
-        return dict.__getattribute__(self, key)
-
-module_data = ModuleData()
+# Make a list of all know modules (described in *Config.py files in the 
+# config_py directory) and load the information described in those Config.py
+# files.
+known_modules = [f[:-9] for f in os.listdir(itkConfig.config_py) if f.endswith('Config.py')]
+known_modules.sort()
+module_data = {}
[…]

### 2006-04-22 Python/itkLazy.py

@@ -1,46 +1,26 @@
-from types import ModuleType
-import sys, os
-import itkBase, itkConfig, itkTypes, itkExtras
+import types, itkBase
 
-class NotLoaded(object):
-  def __init__(self):
-    raise RuntimeError('Not Loaded')
+not_loaded = 'not loaded'
 
-class LazyModuleType(ModuleType):  
-  def __init__(self, attr_to_module_map, loader):
-    self.attr_to_module_map = attr_to_module_map
-    self.module_to_attr_map = {}
-    for (attr, module) in attr_to_module_map.items():
-      self.module_to_attr_map.setdefault(module, []).append(attr)
-    self.loader = loader
-    self.__dict__.update( (attr, NotLoaded) for attr in attr_to_module_map.keys() )
+class LazyITKModule(types.ModuleType):
+  """Subclass of ModuleType that implements a custom __getattribute__ method
+  to allow lazy-loading of attributes from ITK sub-modules."""
+  def __init__(self, name, lazy_attributes):
+    types.ModuleType.__init__(self, name)
+    self.__lazy_attributes = lazy_attributes
+    for k in lazy_attributes:
+      setattr(self, k, not_loaded)
   def __getattribute__(self, attr):
-    value = ModuleType.__getattribute__(self, attr)
-    if value is NotLoaded:
-      module = self.attr_to_module_map[attr]
+    value = types.ModuleType.__getattribute__(self, attr)
+    if value is not_loaded:
+      module = self.__lazy_attributes[attr]
       namespace = {}
-      self.loader(module, namespace)
-      # put things in namespace first, then self.__dict__ to prevent warnings
-      # about overwriting the 'NotLoaded' values already in self.__dict__
-      self.__dict__.update(namespace)
-      value = self.__dict__[attr]
-    return value 
-
-
-# First, find all the xxxConfig.py files in the config_py dir, and strip off the
-# 'Config.py' part of the filename.
-configModules = [f[:-9] for f in os.listdir(itkConfig.config_py) if f.endswith('Config.py')]
-configModules.sort()
-attr_to_module_map = {}
-for module in configModules:
-  templateNames = [t[0] for t in itkBase.module_data[module].templates]
-  attr_to_module_map.update( (n, module) for n in templateNames)
-
-itk = LazyModuleType(attr_to_module_map, itkBase.LoadModule)
-
[…]

### 2006-04-22 Python/itk.py
More fixes for LazyLoading
darcs-hash:20060422010408-733a7-fb0a7c800e2258d39d06955bd489b639aafcf5d7.gz

@@ -1,31 +1,46 @@
 """itk.py : Top-level container module for ITK wrappers."""
 import itkBase, itkConfig, itkLazy, itkTypes, itkExtras, os, sys
 
+thisModule = sys.modules[__name__]
+
 if itkConfig.LazyLoading:
   # If we are loading lazily (on-demand), make a dict mapping the available 
   # classes/functions/etc. (read from the configuration modules) to the 
   # modules they are declared in. Then pass that dict to a LazyITKModule
-  # instance and do some surgery on sys.modules so that the 'itk' module
-  # becomes that new instance instead of what is executed from this file.
+  # instance and (later) do some surgery on sys.modules so that the 'itk' 
+  # module becomes that new instance instead of what is executed from this file.
   lazyAttributes = {}
   for module, data in itkBase.module_data.items():
     templateNames = [ t[0] for t in data['templates'] ]
     lazyAttributes.update( (n, module) for n in templateNames)
-  sys.modules[__name__] = itkLazy.LazyITKModule(__name__, lazyAttributes)
+  if isinstance(thisModule, itkLazy.LazyITKModule):
+    # Handle reload case where we've already done this once.
+    # If we made a new module every time, multiple reload()s would fail
+    # because the identity of sys.modules['itk'] would always be changing.
+    thisModule.__init__(__name__, lazyAttributes)
+    del lazyAttributes
+  else:
+    thisModule = itkLazy.LazyITKModule(__name__, lazyAttributes)
 else: 
-  # Load the modules in the order specified in the known_modules list
-  # for consistency.
+  # We're not lazy-loading. Just load the modules in the order specified in 
+  # the known_modules list for consistency.
   for module in itkBase.known_modules:
-      itkBase.LoadModule(module, globals())
-
-# Now load up the itk module (either this module, or the LazyITKModule
-# instance created above) with the types and extras information.
-thisModule =  sys.modules[__name__]
+    itkBase.LoadModule(module, thisModule.__dict__)
+  
+# Regardless of how it was loaded, fill up the itk module with the ITK types
+# and extras.
 for k, v in itkTypes.__dict__.items():
-  if k != 'itkCType': setattr(thisModule, k, v)
+  if k != 'itkCType' and not k.startswith('_'): 
+    setattr(thisModule, k, v)
 for k, v in itkExtras.__dict__.items():
-  setattr(thisModule, k, v)
[…]

### 2006-04-23 article/Article.tex
Remove AUTO_LOAD in favor of lazy loading.
darcs-hash:20060422010436-733a7-d1f29c9d7557527a394da78e459d0dcd6a6c4cf3.gz
Divide modules (4)
darcs-hash:20060423012550-733a7-a7c8fa84bc02b783bd9ef527727a81cd34bf5248.gz

@@
      \subsubsection{Creating a CMakeLists.txt file for a wrapper library}
-Each WrapITK sub-library (e.g. \verb$ITKCommonA$, or \verb$ITKAlgorithms$) lives in a
-sub-directory of the WrapITK project (e.g. \verb$CommonA$ or \verb$Algorithms$) with a
+Each WrapITK sub-library (e.g. \verb$Base$, or \verb$SpatialObject$) lives in a
+sub-directory of the WrapITK project (within the \verb$Modules$ directory) with a
 \verb$CMakeLists.txt$ file that describes how that library  and language support files
@@
 BEGIN_WRAPPER_LIBRARY("MySpatialObjectExtensions")
-SET(WRAPPER_LIBRARY_DEPENDS ITKSpatialObject ITKCommonA)
+SET(WRAPPER_LIBRARY_DEPENDS SpatialObject Base)
 SET(WRAPPER_LIBRARY_LINK_LIBRARIES ITKCommon)
@@
 \verb$SpatialObject$, that are going to be used in the current library). Every project
-should at least depend on \verb$ITKCommonA$.
+should at least depend on \verb$Base$.
 
@@
 WrapITK libraries, and it will be imported into the \verb$itk$ namespace when the
-\verb$import itk$ command is issued from Python. (This can be disabled by setting
-\verb$WRAPPER_LIBRARY_AUTO_LOAD$ to \verb$OFF$ in the external project's \verb$CMakeLists.txt$.)
+\verb$import itk$ command is issued from Python.
 

### 2006-04-23 Python/Tests/module2module.py

@@ -25,13 +25,13 @@ IType = itk.Image[PType, dim]
 reader = itk.ImageFileReader[IType].New(FileName=sys.argv[1])
 
 sources = []
-image = ITKCommonA.Image[PType, dim].New()
+image = Base.Image[PType, dim].New()
 r = itk.ImageRegion._2()
 r.SetSize((10, 10))
 image.SetRegions(r)
 image.Allocate()
 
-sources.append(("ITKCommonA", image))
+sources.append(("Base", image))
 
 flip = ITKBasicFiltersA.FlipImageFilter[IType].New(reader)
 sources.append(("ITKBasicFiltersA", flip.GetOutput()))

### 2006-04-23 Python/itkTemplate.py
Divide modules (6 -- bug fix)
darcs-hash:20060423014320-733a7-da88a59961cbd4c1c555d93b321038e8af821709.gz

@@ -349,7 +349,7 @@ def New(self, *args, **kargs) :
 
   # now, try to add observer to display progress
   if auto_progress :
-    import ITKPyUtils, ITKCommonA
+    import ITKPyUtils, Base
     try :
       def progress() :
         clrLine = "\033[2000D\033[K"
@@ -361,7 +361,7 @@ def New(self, *args, **kargs) :
 
       command = ITKPyUtils.PyCommand.New()
       command.SetCommandCallable(progress)
-      newItkObject.AddObserver(ITKCommonA.ProgressEvent(), command.GetPointer())
+      newItkObject.AddObserver(Base.ProgressEvent(), command.GetPointer())
     except :
       # it seems that something goes wrong...
       # as this feature is designed for prototyping, it's not really a problem

### 2006-04-26 Python/itkExtras.py
add pipeline class
darcs-hash:20060426092218-2fc9d-75131d47efaf2c7e9b7b6e4c19473902a06c910b.gz

@@ -259,3 +259,76 @@ class show3D :
   def SetMinOpacity(self, val) :
     self.__MinOpacity__ = val
     self.AdaptColorAndOpacity()
+
+
+class pipeline:
+  """A convenient class to store the reference to the filters of a pipeline
+  
+  With this class, a method can create a pipeline of several filters and return
+  it without losing the references to the filters in this pipeline. The pipeline
+  object act almost like a filter (it has a GetOutput() method) and thus can
+  be simply integrated in another pipeline.
+  """
+  def __init__( self, input=None ):
+    self.clear()
+    self.SetInput( input )
+
+  def connect( self, filter ):
+    """Connect a new filter to the pipeline
+    
+    The output of the first filter will be used as the input of this
+    one and the filter passed as parameter will be added to the list
+    """
+    if self.GetOutput() != None:
+      filter.SetInput( self.GetOutput() )
+    self.append( filter )
+
+  def append( self, filter ):
+    """Add a new filter to the pipeline
+    
+    The new filter will not be connected. The user must connect it.
+    """
+    self.filter_list.append( filter )
+
+  def clear( self ):
+    """Clear the filter list
+    """
+    self.filter_list = []
+
+  def GetOutput( self ):
+    """Return the output of the pipeline
+    
+    If another output is needed, use
+    pipeline[-1].GetAnotherOutput() instead of this method, or subclass
+    pipeline to implement another GetOutput() method
+    """
+    if len(self) == 0:
+      return self.GetInput()
+    else :
+      return self[-1].GetOutput()
+
+  def SetInput( self, input ):
+    """Set the input of the pipeline
+    """
+    if len(self) != 0:
+      self[0].SetInput(input)
+    self.input = input
+
+  def GetInput( self ):
+    """Get the input of the pipeline
+    """
+    return self.input
+    
+  def Update( self ):
+    """Update the pipeline
+    """
+    if len(self) > 0:
+      return self[-1].Update()
+
+  def __getitem__( self, i ):
+     return self.filter_list[i]
+
+  def __len__( self ):
+     return len(self.filter_list)
+ 
+ 

### 2006-04-26 Python/itkExtras.py
add index function
darcs-hash:20060426114227-2fc9d-941cda687f57d48f7782b01d0006d8aa45fd142c.gz

@@ -28,6 +28,13 @@ def size(imageOrFilter) :
   img = image(imageOrFilter)
   return img.GetLargestPossibleRegion().GetSize()
   
+# return the index of an imageClass
+def index(imageOrFilter) :
+  # we don't need the entire output, only its size
+  imageOrFilter.UpdateOutputInformation()
+  img = image(imageOrFilter)
+  return img.GetLargestPossibleRegion().GetIndex()
+  
 # return a structuring elt
 def strel(dim, radius=1) :
   st = BinaryBallStructuringElement[B, dim]()

### 2006-04-26 Python/Tests/module2module.py
fix module2module test
darcs-hash:20060426162242-2fc9d-4f4b4fe8f5cc5541156b565f59ce81d292f65e35.gz

@@ -7,19 +7,41 @@
 
 import itk, sys
 
-import ITKCommonA
-import ITKCommonB
-import ITKNumerics
-import ITKBasicFiltersA
-import ITKBasicFiltersB
-import ITKBasicFiltersC
-import ITKSpatialObject
-import ITKAlgorithms
-import ITKIO
+import Base
+import BaseNumerics
+import BaseSpatialObject
+import BaseTransforms
+import BinaryMorphology
+import Calculators
+import Compose
+import DeformableTransforms
+import Denoising
+import DistanceMap
+import EdgesAndContours
+import FFT
+import Filtering
+import IntensityFilters
+import Interpolators
+import IO
+import Iterators
+import LevelSet
+import Morphology
+# import Patented
+import PixelMath
+import Registration
+import Resize
+import SegmentationAndThreshold
+import SegmentationValidation
+import SimpleFilters
+import UnaryPixelMath
+import VXLNumerics
+
 
 PType = itk.US
 dim = 2
 IType = itk.Image[PType, dim]
+
+kernel = itk.strel(2, 1)
 
 # create the reader
 reader = itk.ImageFileReader[IType].New(FileName=sys.argv[1])
@@ -31,39 +53,111 @@ r.SetSize((10, 10))
 image.SetRegions(r)
 image.Allocate()
 
+
+
+# BaseNumerics
+# BaseSpatialObject
+# BaseTransforms
+# Compose
+# DeformableTransforms
+# FFT
+# Interpolators
+# Iterators
+# LevelSet
+# Patented
+# PixelMath
+# Registration
+# SegmentationValidation
+# VXLNumerics
+# EdgesAndContours
+# Filtering
+
+
 sources.append(("Base", image))
 
-flip = ITKBasicFiltersA.FlipImageFilter[IType].New(reader)
-sources.append(("ITKBasicFiltersA", flip.GetOutput()))
+sources.append(("IO", reader.GetOutput()))
 
-shift = ITKBasicFiltersB.ShiftScaleImageFilter[IType, IType].New(reader)
-sources.append(("ITKBasicFiltersB", shift.GetOutput()))
+otsu = SegmentationAndThreshold.OtsuThresholdImageFilter[IType, IType].New(reader)
+sources.append(("SegmentationAndThreshold", otsu.GetOutput()))
 
-abs = ITKBasicFiltersC.AbsImageFilter[IType, IType].New(reader)
[…]

### 2006-04-26 Python/itkExtras.py
fix itkExtra functions
darcs-hash:20060426162308-2fc9d-cf9443530f566d28b82f898557f3f99e967e4634.gz

@@ -9,7 +9,8 @@ def auto_progress( b ):
 # Function to print itk object info
 import sys
 def echo(object, f=sys.stderr) :
-   ss = StringStream()
+   import itk
+   ss = itk.StringStream()
    try :
       try:
          object.Print(ss.GetStream())
@@ -37,7 +38,8 @@ def index(imageOrFilter) :
   
 # return a structuring elt
 def strel(dim, radius=1) :
-  st = BinaryBallStructuringElement[B, dim]()
+  import itk
+  st = itk.BinaryBallStructuringElement[itk.B, dim]()
   st.SetRadius(radius)
   # call the boring CreateStructuringElement() method
   st.CreateStructuringElement()
@@ -81,18 +83,20 @@ def class_(obj) :
 
 # return range
 def range(imageOrFilter) :
+  import itk
   img = image(imageOrFilter)
   img.UpdateOutputInformation()
   img.Update()
-  comp = MinimumMaximumImageCalculator[img].New(Image=img)
+  comp = itk.MinimumMaximumImageCalculator[img].New(Image=img)
   comp.Compute()
   return (comp.GetMinimum(), comp.GetMaximum())
 
 # write an image
 def write(imageOrFilter, fileName):
+  import itk
   img = image(imageOrFilter)
   img.UpdateOutputInformation()
-  writer = ImageFileWriter[img].New(Input=img, FileName=fileName)
+  writer = itk.ImageFileWriter[img].New(Input=img, FileName=fileName)
   writer.Update()
   
 # choose the method to call according to the dimension of the image
@@ -121,7 +125,6 @@ class show3D :
   def __init__(self, input=None, MinOpacity=0.0, MaxOpacity=0.2) :
     import qt
     import vtk
-    import itkvtk
     from vtk.qt.QVTKRenderWindowInteractor import QVTKRenderWindowInteractor
     self.__MinOpacity__ = MinOpacity
     self.__MaxOpacity__ = MaxOpacity
@@ -182,12 +185,11 @@ class show3D :
       # a real fix would be to wrap c++ exception in vtk
       img.UpdateOutputInformation()
       img.Update()
-      import itkvtk
       self.__flipper__ = FlipImageFilter[img].New(Input=img)
       axes = self.__flipper__.GetFlipAxes()
       axes.SetElement(1, True)
       self.__flipper__.SetFlipAxes(axes)
[…]

### 2006-04-26 Python/itk.py
Fix for python versions < 2.4
darcs-hash:20060426234217-733a7-14113dc909193abd6421acae4eeafa5e21351361.gz

@@ -12,7 +12,7 @@ if itkConfig.LazyLoading:
   lazyAttributes = {}
   for module, data in itkBase.module_data.items():
     templateNames = [ t[0] for t in data['templates'] ]
-    lazyAttributes.update( (n, module) for n in templateNames)
+    lazyAttributes.update( [(n, module) for n in templateNames] )
   if isinstance(thisModule, itkLazy.LazyITKModule):
     # Handle reload case where we've already done this once.
     # If we made a new module every time, multiple reload()s would fail

### 2006-04-27 Python/itk.py
More changes for Py2.3 compatibility
darcs-hash:20060427002744-733a7-8b744404cf5febf0dbea2c5678432e9baaf50cf3.gz

@@ -12,7 +12,8 @@ if itkConfig.LazyLoading:
   lazyAttributes = {}
   for module, data in itkBase.module_data.items():
     templateNames = [ t[0] for t in data['templates'] ]
-    lazyAttributes.update( [(n, module) for n in templateNames] )
+    attributes = dict( [(n, module) for n in templateNames] )
+    lazyAttributes.update(attributes)
   if isinstance(thisModule, itkLazy.LazyITKModule):
     # Handle reload case where we've already done this once.
     # If we made a new module every time, multiple reload()s would fail

### 2006-04-27 article/Article.tex
change import callback signature and add import callback when calling auto_progress(True)
darcs-hash:20060427134155-2fc9d-914e20191066fcb77809554427aef26f25db3544.gz

@@
 
+\verb$itk.auto_progress(True)$ also set an import callback which show the module name when
+the module are imported.
+
   \item \verb$itk.class_(object)$ return the class of an object. The \verb$__class__$
@@
 import sys, itkConfig
-def stderr_callback(name):
-  print >> sys.stderr, name
+def stderr_callback(name, progress):
+  if progress == 0:
+    print >> sys.stderr, "Loading %s..." % name,
+  if progress == 1:
+    print >> sys.stderr, "done"
 itkConfig.ImportCallback = stderr_callback
@@
 \end{verbatim} \normalsize
+
+\verb$progress$ take only the value $0$ and $1$, but may take values between $0$ and $1$
+in the future.
 
@@
 
-     \subsubsection{Creating wrapXXX.cmake files to wrap classes}
+     \subsubsection{Creating wrap\_XXX.cmake files to wrap classes}
 
@@
 not as much tweaked than python part, also take benefit of the higher number of
-wrapped classes, and of the increase of consistency in available types and names
+wrapped classes, and of the increase of consistency in available types and names.
 

### 2006-04-27 Python/Tests/extras.py

@@ -1,8 +1,11 @@
 #!/usr/bin/env python
 
 # also test the import callback feature
-def custom_callback(name):
-  print "loading %s submodule..." % name
+def custom_callback(name, progress):
+  if progress == 0:
+    print >> sys.stderr, "Loading %s..." % name,
+  if progress == 1:
+    print >> sys.stderr, "done"
 import itkConfig
 itkConfig.ImportCallback = custom_callback
 

### 2006-04-27 Python/itkBase.py

@@ -52,7 +52,7 @@ def LoadModule(name, namespace = None):
     for dep in deps:
       LoadModule(dep, namespace)
   
-  if itkConfig.ImportCallback: itkConfig.ImportCallback(name)
+  if itkConfig.ImportCallback: itkConfig.ImportCallback(name, 0)
   
   # SWIG-generated modules have 'Python' appended. Only load the SWIG module if
   # we haven't already.
@@ -108,6 +108,8 @@ def LoadModule(name, namespace = None):
           if current_value != None and current_value != swigClass:
             DebugPrintError("Namespace already has a value for %s, which is not class %s. Overwriting old value." %(pyClassName, cppClassName))
           namespace[pyClassName] = swigClass
+  
+  if itkConfig.ImportCallback: itkConfig.ImportCallback(name, 1)
   
 def DebugPrintError(error):
   if itkConfig.DebugLevel == itkConfig.WARN:

### 2006-04-27 Python/itkExtras.py

@@ -5,6 +5,19 @@ def auto_progress( b ):
   import itkTemplate
   itkTemplate.auto_progress = b
   
+  import itkConfig
+  if b :
+    def loadingCallback(name, p):
+      import sys
+      clrLine = "\033[2000D\033[K"
+      print >> sys.stderr, clrLine+"Loading %s..." % name,
+      if p == 1 :
+        print >> sys.stderr, clrLine,
+    
+    itkConfig.ImportCallback = loadingCallback
+  else:
+    itkConfig.ImportCallback = None
+  
 
 # Function to print itk object info
 import sys

### 2006-04-27 Python/itkExtras.py
fix missing itk prefix for the FlipImageFilter
darcs-hash:20060427142616-2fc9d-fd212947bda17a08bcc08ae61ed5ad0b3de150b4.gz

@@ -198,7 +198,8 @@ class show3D :
       # a real fix would be to wrap c++ exception in vtk
       img.UpdateOutputInformation()
       img.Update()
-      self.__flipper__ = FlipImageFilter[img].New(Input=img)
+      import itk
+      self.__flipper__ = itk.FlipImageFilter[img].New(Input=img)
       axes = self.__flipper__.GetFlipAxes()
       axes.SetElement(1, True)
       self.__flipper__.SetFlipAxes(axes)

### 2006-04-27 Python/Tests/extras.py
add force_load() function
darcs-hash:20060427143519-2fc9d-ac66a1f6457e7a743ea0ac2442ed9c4e28f3c777.gz

@@ -11,6 +11,9 @@ itkConfig.ImportCallback = custom_callback
 
 import itk, sys
 
+# test the force load function
+itk.force_load()
+
 fileName = sys.argv[1]
 
 PType = itk.US

### 2006-04-27 Python/itkExtras.py

@@ -19,6 +19,12 @@ def auto_progress( b ):
     itkConfig.ImportCallback = None
   
 
+def force_load():
+  """force itk to load all the submodules"""
+  import itk
+  for k in dir(itk):
+    dir(getattr(itk, k))
+
 # Function to print itk object info
 import sys
 def echo(object, f=sys.stderr) :

### 2006-04-27 article/Article.tex
import vtk module before returning a vtk object to fix the segfault and deprecate itkvtk
darcs-hash:20060427201314-2fc9d-7788977ca5a53d1ddceea3ad0202e277f56927a1.gz

@@
 
-By default, those classes are not loaded in the \verb$itk$ module to avoid loading
-all the \verb$vtk$ module while importing \verb$itk$. The command \verb$import itkvtk$
-will load the module, and add the classes both in \verb$itkvtk$ and \verb$itk$ module.
-The classes are then usable as the other itk classes.
+With the python lazy loading, the classes are not loaded by default, and thus avoid
+loading the entire vtk code in memory. The classes are directly available in the
+\verb$itk$ module, and the underlaying code is loaded only when those classes are used.
 
@@
 
-2> import itkvtk
-
-3> reader = itk.ImageFileReader.IUC3.New()
-
-4> converter = itk.ImageToVTKImageFilter.IUC3.New(reader)
-
-5> converter.GetOutput()
-5> <libvtkFilteringPython.vtkImageData vtkobject at 0xb7675b60>
+2> reader = itk.ImageFileReader.IUC3.New()
+
+3> converter = itk.ImageToVTKImageFilter.IUC3.New(reader)
+
+4> converter.GetOutput()
+4> <libvtkFilteringPython.vtkImageData vtkobject at 0xb7675b60>
 \end{verbatim}

### 2006-04-27 ExternalProjects/ItkVtkGlue/Wrapping/Python/itkvtk.py

@@ -11,3 +11,9 @@ del itk, vtk, ItkVtkGlue, names, name
 
 # also keep ItkVtkGlue members in that namespace
 from ItkVtkGlue import *
+
+# display a deprecation warning
+import sys
+print >> sys.stderr, "Warning: ItkVtkGlue classes are available in itk module, without importing itkvtk."
+print >> sys.stderr, "Warning: itkvtk is no more supported and will be removed soon."
+del sys

### 2006-04-27 Python/itkExtras.py
simplify force_load()
darcs-hash:20060427201350-2fc9d-0ff9359251c19abf8fbf77452a40c2a7445ad323.gz

@@ -23,7 +23,7 @@ def force_load():
   """force itk to load all the submodules"""
   import itk
   for k in dir(itk):
-    dir(getattr(itk, k))
+    getattr(itk, k)
 
 # Function to print itk object info
 import sys

### 2006-08-28 article/Article.tex
fix Benoit's afffiliation
darcs-hash:20060828132449-2fc9d-03457b50c6586f216c7b9728c8edf606f30aaf9a.gz

@@
 % The author and/or editor can define 'significant' however they like.
-\release{0.1}
+\release{0.2}
 
@@
 \author{Ga\"etan Lehmann{$^1$}{\small{,}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
-\authoraddress{{$^1$}Unit\'e de Biologie du D\'eveloppement et de la Reproduction, Institut National de la Recherche Agronomique, 78350 Jouy-en-Josas, France\\
+\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et 
+Reproduction, Jouy en Josas, F-78350, France\\
 {$^2$}Program in Biomedical Informatics and Department of Biochemistry, Stanford University School of Medicine, Stanford, California\\
-{$^3$}CREATIS, CNRS UMR 5515, 69621 Villeurbanne, France}
+{$^3$}CREATIS, CNRS UMR 5515, Inserm U630, Univ. Lyon1, INSA Lyon, 69621 Villeurbanne, France}
 
@@
 \noindent
-ITK \cite{ITKWebSite} is a huge image analysis library, which contains lots of state of the arts
+ITK \cite{ITKWebSite} is a huge image analysis library, which contains lots of state of the art
 algorithms implementations. However, using it in C++ can be difficult and is
-definitively bad suited for prototyping. WrapITK aims to allow classes from ITK
+poorly suited for prototyping. WrapITK aims to allow classes from ITK
 (and custom, classes that interact with ITK) to be "wrapped" for use with
@@
 
-\section{Introduction}
-
-WrapITK is a project designed to allow classes from ITK (and custom, classes
+\newpage
+\part{Introduction}
+
+WrapITK is a project designed to allow classes from ITK (and custom classes
 that interact with ITK) to be "wrapped" for use with languages like
@@
   \item  ITK is a huge library, but only a small number of classes are available
-in target languages. It become quickly frustrating for the user, especially when
+in target languages. This quickly becomes frustrating for the user, especially when
 he has to spend lot of time to extend the current set of classes. Even if it is
 not yet complete, the WrapITK's set of classes have been highly extended. Moreover,
-the user can choose at build time which types and which dimensions he want to wrap.
-
-  \item  The template arguments set is poorly chosen, making sometime impossible
+the user can choose at build time which types and which dimensions he wants to wrap.
+With 202 wrapped filters, WrapITK covers 63\% of the available filters.
+
+  \item  The template argument set is poorly chosen, sometimes making it impossible
 to create a pipeline. In WrapITK, most of the filters have the same input and output
-types, and only a few filters allow to change type. This make the types manipulated 
+types, and only a few filters are allowed to change type. This make the types manipulated 
 by filters more consistent, and the user should always be able to build his pipeline.
 
-  \item  Lots of types returned by ITK object's methods are not usable in target
+  \item  Many types returned by ITK object's methods are not usable in target
 languages. For example, the \verb$GetPixel()$ method of the class \verb$itk::Image$
-returns a string describing a pointer, but don't return the pixel value. In WrapITK,
-most types used in classes are available in target languages.
-
-  \item  Names in target languages are inconsistent. WrapITK use a strict naming
-convention which should make easier to identify the template arguments.
+returns a string describing a pointer, but does not return the pixel value. In WrapITK,
+most types used in the classes are available in target languages.
+
+  \item  Names in target languages are inconsistent. WrapITK uses a strict naming
+convention which should make it easier to identify the template arguments.
 
@@
 external C++ classes to be wrapped and even installed in the WrapITK tree so
-that they interact seamlessly with the other wrapped classes.
+they interact seamlessly with the other wrapped classes.
 
   \item  The python's \verb$InsightToolkit$ module is only structured as a big
-list of names. It make it nearly unusable in the python interpreter. WrapITK
-comes with a new well designed python module easy to use in interpreter, and
-providing run-time lookup of templated types - thing which can't be easily done
+list of names which makes it nearly unusable in the python interpreter. WrapITK
+comes with a new, well-designed python module that is easy to use with the interpreter, and
+which provides run-time lookup of templated types - things which can't be easily done
 in C++. Additionally, WrapITK ensures that \verb$SmartPointer$s are always
@@
 
-\end{itemize}
-
-The article you're reading is not as nice and complete than what we would have
-done, but it seems important to us to release our work and to get feedbacks
+  \item  Loading python modules can take lot of time. With WrapITK, by default,
+only the modules really used are loaded, so the loading time is much shorter
+in common situations.
+
+\end{itemize}
+
+The article you're reading is not yet complete,
+but it seems important for us to release our work and to get feedback
 as soon as possible. The article will continue to evolve with WrapITK.
 
-\section{Supported languages and plateforms}
-
-Java, Tcl and Python builds properly and are fully usable. However, Java and
+\newpage
+\part{Supported languages and plateforms}
+
+Java, Tcl and Python build properly and are fully usable. However, Java and
 Tcl don't yet have the extended features added to Python\footnote{Any help
@@
 WrapITK is mainly developed on Mandriva Linux \cite{MandrivaWebSite} and 
-MacOS X \cite{MacOsXWebSite} and so is well tested on this palteforms.
-It also builds on windows \cite{WindowsWebSite}, but require more testing
-to be sure everything work as it should. See below for details about how
-to report bugs are contribute patches.
-
-Several tests are available\footnote{There is currently 49 tests with the default
-configuration.} for Python, Tcl and Java. They can be run with the \verb$ctest$
-command.
-
-\section{Performance}
-
-\section{User guide}
-
-  \subsection{Installation}
-
-    \subsubsection{Get the software sources}
+MacOS X \cite{MacOsXWebSite} and therefore is well tested on these platforms.
+It also builds on windows \cite{WindowsWebSite}, but more testing is required
+to be sure everything works as it should. See below for details about how
+to report bugs and contribute patches.
+
+Several tests are available\footnote{There is currently 67 tests with the default
+configuration.} for Python, Tcl and Java. They ensure the high quality of WrapITK.
+They can be run with the \verb$ctest$ command.
+
+\newpage
+\part{Performance and memory usage}
+
+WrapITK provides an interface to some C++ compiled code, so execution times
+are very similar to pure C++ programs in most of cases.
+
+The major difference comes from the memory
+usage: while a C++ program will produce a binary executable containing only
+the required code, the WrapITK binary contains all the wrapped classes. So,
+WrapITK can take a significant amount of memory.
+
+Some convenient features, like sequence management in python, can be quite
+inefficient and should not be used in a loop.
+
+\newpage
+\part{User guide}
+
+  \section{Installation}
+
+    \subsection{Get the software sources}
 
@@
 
-The last version can be obtained from the development repository with darcs \cite{DarcsWebSite}.
+The latest version can be obtained from the development repository with darcs \cite{DarcsWebSite}.
 The command is
 \verb$darcs get --partial http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/$\footnote{Note
-that the {\em --partial} option is required on systems with case insensitive filesystem like
-windows or Mac Os X.}.
-
-For the user who don't want to use darcs \cite{DarcsWebSite} but still want the last development version,
+that the {\em --partial} option is required on systems with case insensitive filesystems like
+windows or Mac OS X.}.
+
+For the user who does not want to use darcs \cite{DarcsWebSite} but still wants the last development version,
 a nightly updated archive is available at
-\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz}.
-
-    \subsubsection{ITK}
-
-WrapITK will work properly with the ITK 2.6.0 release.
+\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz} or
+\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.zip}.
+
+    \subsection{ITK}
+
+WrapITK will work properly with the ITK 2.8.1 release.
 
@@
 patches to the ITK source in \verb$WrapITK/patches/optional$ which can be applied to
-version 2.6.0. These optional patches provide
+version 2.8.1. These optional patches provide
 better support for python by providing some methods like \verb$__str__$, or methods
@@
 
-    \subsubsection{CableSwig}
+Some required patches may appear in the development version of WrapITK. Those
+patches are required for the last stable version of ITK, and should be already
+integrated in the last CVS version of ITK.
+
+    \subsection{CableSwig}
 
@@
 
-    \subsubsection{Python}
+    \subsection{Python}
 
@@
 WrapITK is reported to work with python 2.3 and python 2.4. However, the test framework
-requires the \verb$subprocess$ module available in standard only in python 2.4 and above.
+requires the \verb$subprocess$ module to be available, which is standard only in python 2.4 and above.
 To run the python test with python 2.3, you have to install \verb$subprocess$.
 
-    \subsubsection{Tcl}
+    \subsection{Tcl}
 
 Tcl \cite{TclWebSite} is required only to build tcl support.
-WrapITK have been tested with Tcl 8.4.11.
-
-    \subsubsection{Java}
+WrapITK has been tested with Tcl 8.4.11.
+
+    \subsection{Java}
 
 Java \cite{JavaWebSite} is required only to build java support.
-WrapITK have been tested with java \verb$1.5.0_06-b05$.
-
-    \subsubsection{Build options}
+WrapITK has been tested with java \verb$1.5.0_06-b05$ and \verb$1.4.2_11$.
+
+    \subsection{Build options}
 
@@
 
-The project is provided with defaults build option which should OK for most of
-users. However, for specific needs, you might want to change those options:
+The project is provided with default build options which should be OK for most
+users. However, for specific needs, you might want to change these options:
 \begin{itemize}
@@
   \item \verb$WRAP_double$ \verb$OFF$, by default.
-  \item \verb$WRAP_float$ \verb$ON$, by default. Note that it is the only signed
+  \item \verb$WRAP_float$ \verb$ON$, by default. Note that float is the only signed
 type selected by default, so you will have to use floats to manipulate signed
@@
   \item \verb$WRAP_unsigned_short$, \verb$ON$ by default. \verb$unsigned short$
-is the only integer type available by default. This type have been choose rather
+is the only integer type available by default. This type has been choosen rather
 than \verb$unsigned char$ to be able to manipulate 8-bits as well as 16-bits images,
@@
 
-The user should modify those options carefully: activate all the types, and/or
-add lots of dimensions will produce very large binary files which will take lots
+The user should modify these options carefully: activate all the types, and/or
+adding many dimensions will produce very large binary files which will take a lot
 of memory once loaded.
@@
 could declare that it should only be wrapped for 3D images with floating-point
-typed pixels. In this case, then wrappers will only be created if the user has
-selected to build 3-dimensional image wrappers and has selected one or more
+typed pixels. In this case, the wrappers will only be created if the user has
+chosen to build 3-dimensional image wrappers and has selected one or more
 floating point types (e.g. double or float) in ccmake. Thus, the ccmake
@@
 
-Project should always be built outside the source directory, in a \verb$build$
+Projects should always be built outside the source directory, in a \verb$build$
 directory for example.
 
-    \subsubsection{Install WrapITK or use it in the build tree}
+    \subsection{Install WrapITK or use it in the build tree}
 
@@
 
-    \subsubsection{Binary packages}
+    \subsection{Binary packages}
 
 RPM packages for Mandriva Linux 2006 are available at \url{http://voxel.jouy.inra.fr/mdk/mima2}.
-To install WrapITK for mandriva linux 2006.0, just add a new media with the
+To install WrapITK for Mandriva Linux 2006.0, just add a new media with the
 command
@@
 
-This media also contain several packages which may be useful to use WrapITK,
+This media also contains several packages which may be useful to use WrapITK,
 and which are not available in mandriva linux 2006.0. Here is the full list:
@@
   \item \verb$cmake$
+  \item \verb$darcs$
   \item \verb$itk-data$
@@
 
-  \subsection{Python usage}
-
-     \subsubsection{Configuring python and importing the libraries}
+  \section{Python usage}
+
+In this section, we detail python usage. Some of the examples shown here are copied
+from the console which shows the interpreter prompt:
+
+\begin{verbatim}
+2> 12+3
+2> 15
+
+3> result = 12+3
+
+4> 
+\end{verbatim}
+
+In the example above, \verb$12+3$ is what is written in the interpreter, and
+\verb$15$ is the result. \verb$2>$, \verb$3>$, \verb$4>$ are the prompts
+of the interpreter.
+
+     \subsection{Configuring python and importing the libraries}
 
@@
 
-On linux boxes however, the user have to set the \verb$LD_LIBRARY_PATH$ to
+On linux boxes however, the user must set the \verb$LD_LIBRARY_PATH$ to
 point to libSwigRuntime.so. For example
 \verb$export LD_LIBRARY_PATH=/usr/lib/InsightToolkit/WrapITK/Python-SWIG$.
+This step is not required with the mandriva's package.
 
@@
 
-     \subsubsection{Template usage}
+     \subsection{Template usage}
 Most class in the itk python module are "template proxy classes" that
@@
 \end{verbatim}
-This construction is similar to what is done in C++, and make it easy to change
-the dimension used for example - it can even be changed at run-time.
-
-A more convenient syntax for usage in interpreter is also available:
+This construction is similar to what is done in C++, and makes it easy to change
+the dimension used. For example - it can even be changed at run-time.
+
+A more convenient syntax for usage in the interpreter is also available:
 \begin{itemize}
@@
 \end{itemize}
-\verb$itk.Image.UC3$ refere to the same class than \verb$itk.Image[itk.UC, 3]$
-but have the advantage to allow to use the tab-completion in the interpreter,
-and so let the user easily know which template arguments he can use.
+\verb$itk.Image.UC3$ refers to the same class as \verb$itk.Image[itk.UC, 3]$
+but has the advantage of allowing the use of tab-completion in the interpreter,
+and lets the user easily know which template arguments he can use.
 However, this notation is more rigid than the one above and won't let the user
-specify the type and the dimension used in a single place, and thus,
-should be use only in interpreter.
+specify the type and the dimension used in a single place. Therefor, this syntax
+should be used only in interpreter.
 
@@
   \item or \verb$itk.ImageFileReader[imageType]$
-  \item or even with an instance of the class used as template parameter: \verb$itk.ImageFileReader[image]$.
+  \item or even with an instance of the class used as a template parameter: \verb$itk.ImageFileReader[image]$.
 \end{itemize}
 This makes it easy to write generic routines which
-can deal with any input image type. For example, a function which take an image
-as parameter and write it to a file without having to give the image type can be:
+can deal with any input image type. For example, a function which takes an image
+as parameter and writes it to a file without having to give the image type can be:
 \begin{verbatim}
@@
 
-     \subsubsection{The {\em New()} method}
-
-Lots of classes have a \verb$New()$ method which returns a smart pointer to that class. The
-\verb$New()$ method in python has some additional features:
+     \subsection{The {\em New()} method}
+
+Many classes have a \verb$New()$ method which returns a smart pointer to an object of
+that class. In python, the \verb$New()$ method has some additional features:
 \begin{itemize}
@@
 \end{verbatim}
-In that case, \verb$New$ will use the \verb$GetOutput()$ method of the object, if it
-exist, to get the image and set the inputs of the new filter.
-
-  \item Additionally, keyword arguments are allowed as well. Keyword arguments cause
+In that case, \verb$New()$ will use the \verb$GetOutput()$ method of the object, if it
+exists, to get the image and set the inputs of the new filter.
+
+  \item Additionally, keyword arguments are allowed . Keyword arguments cause
 the corresponding \verb$Set...$ method to be called, so you could write the
@@
 
-and, more important, most of classes can be instantiated and parametered in one line,
-which make ITK less verbose, and a lots more easy to use in the interpreter.
-
-     \subsubsection{Python sequences and ITK}
-
-To set the radius of a \verb$MedianImageFilter$ object, for example, the user have to
-create a \verb$Size$ object and use it as argument of the \verb$SetRadius()$ method.
+and, more importantly, most of the classes can be instantiated and parameterized in one line,
+which make ITK less verbose, and a lot more easy to use in the interpreter.
+
+     \subsection{Python sequences and ITK}
+
+To set the radius of a \verb$MedianImageFilter$ object, for example, the user has to
+create a \verb$Size$ object and use it as an argument of the \verb$SetRadius()$ method.
 \begin{verbatim}
@@
 
-Note that the \verb$SetElement()$ method doesn't check the bound of the object, and thus
+Note that the \verb$SetElement()$ method doesn't check the bounds of the object, and thus
 is unsafe. The following code is executed, and can lead to a segmentation fault.
@@
 
-This time, a bound check is performed, and the user is not able to use an invalid index.
+This time, a bounds check is performed, and the user is not able to use an invalid index.
 
@@
 
-Even if it's a safe method, it is still not really convenient.
+Even if it is a safe method, it is still not really convenient.
 
@@
 
-Also, with the optional patches, some itk object can be converted to python sequences.
+Also, with the optional patches, some itk objects can be converted to python sequences.
 
@@
 
-     \subsubsection{Python specific functions in the {\em itk} module}
-
-Some convenient functions are provided with the itk module. They all begin with a lower
+     \subsection{Python specific functions in the {\em itk} module}
+
+Some convenience functions are provided with the itk module. They all begin with a lower
 case character to clearly show they are not part of ITK.
@@
 is a filter, the object returned by \verb$GetOutput()$ method is returned.
-This function is used in most of the next functions to allow the user to
+This function is used in most of the following functions to allow the user to
 pass an image or a filter, and is available here for the same usage in some custom
@@
 
-  \item \verb$itk.range(object)$ return the range of values of an image in a tuple.
+  \item \verb$itk.range(object)$ returns the range of values of an image in a tuple.
 \verb$object$ can be an image or a filter. In case of a filter, \verb$itk.image()$ is used
-to get the output image of the filter. The function update the pipeline by calling
+to get the output image of the filter. The function updates the pipeline by calling
 \verb$UpdateOutputInformation()$ and \verb$Update()$.
 
-This function is only a convenient function for a common task while prototyping.
+This function is only a convenience function for a common task while prototyping.
 
@@
   \item \verb$itk.size(object)$ return the size of an image.
-\verb$object$ can be an image or a filter. In case of a filter, \verb$itk.image()$ is used
-to get the output image of the filter. The function update only the information of the
-pipeline, by calling \verb$UpdateOutputInformation()$, but don't trigger a full update
+\verb$object$ can be an image or a filter. In the case of a filter, \verb$itk.image()$ is used
+to get the output image of the filter. The function updates only the information of the
+pipeline, by calling \verb$UpdateOutputInformation()$, but does not trigger a full update
 of the pipeline.
 
-This function is only a convenient function for a common task while prototyping.
+This function is only a convenience function for a common task while prototyping.
 
@@
 
-  \item \verb$itk.write(object, fileName)$ write an image in a file, without
+  \item \verb$itk.write(object, fileName)$ write an image to a file, without
 having to pass the image type.
-\verb$object$ can be an image or a filter. In case of a filter, \verb$itk.image()$ is used
-to get the output image of the filter. The function update the pipeline by calling
+\verb$object$ can be an image or a filter. In the case of a filter, \verb$itk.image()$ is used
+to get the output image of the filter. The function updates the pipeline by calling
 \verb$UpdateOutputInformation()$ and \verb$Update()$.
 
-This function is only a convenient function for a common task while prototyping.
+This function is only a convenience function for a common task while prototyping.
 
@@
   \item \verb$itk.show()$, \verb$itk.show2D()$ and \verb$itk.show3D()$ are used to
-display images. \verb$itk.show2D()$ requires to have imview \cite{ImviewWebSite} installed.
-\verb$itk.show3D()$ requires to have Vtk for python, ItkVtkGlue\footnote{ItkVtkGlue can be found in
+display images. \verb$itk.show2D()$ requires that imview \cite{ImviewWebSite} be installed.
+\verb$itk.show3D()$ requires Vtk for python, ItkVtkGlue\footnote{ItkVtkGlue can be found in
 the {\em ExternalProject} directory of WrapITK} for python, PyQt \cite{PyQtWebSite}, and iPython
-\cite{IPythonWebSite} installed, and to use iPython with the \verb$-qthread$ option.
+\cite{IPythonWebSite} with the \verb$-qthread$ option.
 
@@
 
-\verb$itk.show3D()$ display a volumic rendering of the image. See Figure~\ref{screenshot}.
+\verb$itk.show3D()$ display a volumetric rendering of the image. See Figure~\ref{screenshot}.
 
@@
 \verb$BinaryBallStructuringElement$ directly is recommended to have backward compatibility
-when the structuring element type will be changed.
+when the structuring element type changes.
 
@@
 
-\verb$itk.auto_progress(True)$ also set an import callback which show the module name when
+\verb$itk.auto_progress(True)$ also sets an import callback which show the module name when
 the module are imported.
 
-  \item \verb$itk.class_(object)$ return the class of an object. The \verb$__class__$
-attribute is often not what the user want with ITK. \verb$itk.class_$ is a convenient
+  \item \verb$itk.class_(object)$ returns the class of an object. The \verb$__class__$
+attribute is often not what the user wants with ITK. \verb$itk.class_$ is a convenience
 function to get the class of an ITK object.
@@
 
-\end{itemize}
-
-     \subsubsection{Advanced Features}
+  \item \verb$itk.echo(object, file)$ is a convenience function to call the \verb$Print()$
+method of an ITK object without the need to pass a \verb$StringStream$ object.
+This function is less useful with the optional patches: the \verb$__str__()$
+method does a very similar job with better integration with python.
+
+Example:
+
+\begin{verbatim}
+12> itk.echo(median)
+MedianImageFilter (0x82c5b68)
+  RTTI typeinfo:   itk::MedianImageFilter<itk::Image<unsigned char, 3u>, itk::Image<unsigned char, 3u> >
+  Reference Count: 1
+  Modified Time: 10
+  Debug: Off
+  Observers:
+    none
+  Number Of Required Inputs: 1
+  Number Of Required Outputs: 1
+  Number Of Threads: 2
+  ReleaseDataFlag: Off
+  ReleaseDataBeforeUpdateFlag: Off
+  No Inputs
+  Output 0: (0x875da68)
+  AbortGenerateData: Off
+  Progress: 0
+  Multithreader:
+    RTTI typeinfo:   itk::MultiThreader
+    Reference Count: 1
+    Modified Time: 2
+    Debug: Off
+    Observers:
+      none
+    Thread Count: 2
+    Global Maximum Number Of Threads: 0
+  Radius: [1, 1, 1]
+\end{verbatim}
+
+  \item \verb$itk.pipeline$ class let the developer easily create
+a custom pipeline which can then be manipulated as a pure ITK filter.
+It provides several methods:
+\begin{itemize}
+  \item \verb$__init__( self, input=None )$ is the constructor of the pipeline.
+The input of the pipeline can be passed as parameter.
+
+  \item \verb$connect( self, filter )$ connect a new filter to the pipeline.
+The output of the last filter in the pipeline will be set as the input of the filter
+passed as a parameter, and the filter passed as a parameter will be added to the filter
+list.
+
+  \item \verb$append( self, filter )$ add a filter to the pipeline's filters list,
+but don't connect it. The connection must be done by the user. This method is likely
+to be used with filters with several inputs.
+
+  \item \verb$clear( self )$  clear the filter list.
+
+  \item \verb$GetOutput( self )$ return the output of the last filter in the pipeline.
+If another output is needed, use \verb$pipeline[-1].GetAnotherOutput()$ instead of
+this method, or subclass pipeline to implement another \verb$GetOutput()$ method.
+
+  \item \verb$SetInput( self, input )$ set the input of the first filter in the
+pipeline. If another input is needed, use \verb$pipeline[0].SetAnotherIntput()$ instead of
+this method, or subclass pipeline to implement another \verb$SetIntput()$ method.
+
+  \item \verb$GetInput( self )$ return the input of the last filter in the pipeline.
+If another input is needed, use \verb$pipeline[0].GetAnotherInput()$ instead of
+this method, or subclass the pipeline to implement another \verb$GetInput()$ method.
+
+  \item \verb$Update( self )$ update the pipeline by calling \verb$Update()$ method
+on the last filter in the pipeline.
+
+  \item \verb$__getitem__( self, i )$ and \verb$__len__( self )$ provide the common
+python list manipulation interface to the pipeline object.
+
+\end{itemize}
+
+Example:
+ITK's current implementation of morphological dilation, erosion, opening and closing
+can be very inefficient with large structuring elements. Also, WrapITK only gives
+access to ball structuring element. The following class illustrates the use of the 
+\verb$itk.pipeline$ class to implement an efficient opening in 3 dimensions with
+a box structuring element. We take advantage of structuring element decomposition:
+a dilation (or erosion) by a box can be more efficiently computed by perfoming
+3 dilations (or erosion) with line structuring element oriented on each dimension.
+The \verb$itk.pipeline$ encapsulates the 6 filters needed to perform the efficient
+opening, and takes care of setting the structuring elements for all the internal
+filters in the \verb$SetKernel(self, x,y,z)$, according to the size wanted by the
+user.
+
+\begin{verbatim}
+class mkOpeningPipe (itk.pipeline):
+  def __init__(self, Input, x=1, y=1, z=1):
+    im = itk.image(Input)
+    itk.pipeline.__init__(self, im)
+    KernelType = itk.class_(itk.strel(3, 0))
+    InType = itk.class_(im)
+    self.connect(itk.GrayscaleErodeImageFilter[InType, InType, KernelType].New())
+    self.connect(itk.GrayscaleErodeImageFilter[InType, InType, KernelType].New())
+    self.connect(itk.GrayscaleErodeImageFilter[InType, InType, KernelType].New())
+    self.connect(itk.GrayscaleDilateImageFilter[InType, InType, KernelType].New())
+    self.connect(itk.GrayscaleDilateImageFilter[InType, InType, KernelType].New())
+    self.connect(itk.GrayscaleDilateImageFilter[InType, InType, KernelType].New())
+    self.SetKernel(x,y,z)
+
+  def SetKernel(self, x,y,z):
+    self[0].SetKernel(itk.strel(3, (x,0,0)))
+    self[1].SetKernel(itk.strel(3, (0,y,0)))
+    self[2].SetKernel(itk.strel(3, (0,0,z)))
+    self[3].SetKernel(itk.strel(3, (x,0,0)))
+    self[4].SetKernel(itk.strel(3, (0,y,0)))
+    self[5].SetKernel(itk.strel(3, (0,0,z)))
+\end{verbatim}
+
+The \verb$mkOpeningPipe$ object can be used as a standard ITK filter:
+
+\begin{verbatim}
+reader = itk.ImageFileReader.IUC3.New(FileName='image.tif')
+opening = mkOpeningPipe(reader)
+ws = itk.MorphologicalWatershedImageFilter.IUC3IUC3.New(opening)
+itk.write(ws, "result.tif")
+\end{verbatim}
+
+\end{itemize}
+
+     \subsection{Advanced Features}
 
@@
 In addition (as mentioned above), WrapITK by default ensures that no bare
-pointers are ever returned to python: instead reference-counting \verb$SmartPointer$s
+pointers are ever returned to python: instead, reference-counting \verb$SmartPointer$s
 are used. However, there may be times when extracting a bare pointer or creating
@@
 
-\verb$itk$ module can be very long to import. The \verb$itkConfig$ module define
+WrapITK modules can take very long to import. The \verb$itkConfig$ module defines
 a \verb$ImportCallback$ method which will be called when each sub module is
@@
 the name of the library being imported as a parameter. Here is an example of a very
-basic callback function which display the name of the submodule being imported on
+basic callback function which displays the name of the submodule being imported on
 the standard error output.
@@
 
-\verb$progress$ take only the value $0$ and $1$, but may take values between $0$ and $1$
+\verb$progress$ takes only the values $0$ and $1$, but may take values between $0$ and $1$
 in the future.
 
-    \subsection{TCL usage}
+It must be noted that using \verb$import itk$ loads only python code, and doesn't load
+any C++ compiled code. This feature is called {\em lazy loading}. It implies some specific
+behaviors:
+\begin{itemize}
+ \item \verb$import itk$ is done in a very short time
+ \item a compiled module is loaded only when a class in that module is used. Thus,
+when a python program is run, only the revelant modules are loaded in memory
+ \item using a class in a program can block the program (for a short time). The user
+can choose to load the entire library at once with the command \verb$itk.force_load()$.
+\end{itemize}
+
+     \subsection{Full python script examples}
+
+This script is the exact transcription to python of the C++ example 
+which can be found at Examples/Filtering/GradientMagnitudeRecursiveGaussianImageFilter.cxx
+in the ITK source tree. More information about the filters used can be found in 
+the ITK Software Guide \cite{ITKSoftwareGuide}, section 6.4.2.
+
+\small \begin{verbatim}
+import itk
+from sys import argv
+
+InputPixelType = itk.F
+OutputPixelType = itk.F
+
+InputImageType = itk.Image[InputPixelType, 2]
+OutputImageType = itk.Image[OutputPixelType, 2]
+
+reader = itk.ImageFileReader[InputImageType].New( FileName=argv[1] )
+
+filter = itk.GradientMagnitudeRecursiveGaussianImageFilter[InputImageType, OutputImageType].New(
+                     reader,
+                     Sigma=float(argv[3]) )
+filter.Update();
+
+WritePixelType = itk.UC
+WriteImageType = itk.Image[WritePixelType, 2]
+
+rescaler = itk.RescaleIntensityImageFilter[OutputImageType, WriteImageType].New( filter,
+                     OutputMinimum=0,
+                     OutputMaximum=255 )
+
+writer = itk.ImageFileWriter[WriteImageType].New( rescaler, FileName=argv[2] )
+
+writer.Update();
+\end{verbatim} \normalsize
+
+More examples can be found in the directory \verb$Python/Tests$.
+
+    \section{TCL usage}
+
+Some examples are available in \verb$Tcl/Tests$ directory.
 
@@
 
-    \subsection{Java usage}
+    \section{Java usage}
+
+Some examples are available in \verb$Java/Tests$ directory.
 
@@
 
-\section{Developer guide}
+\newpage
+\part{Developer guide}
 
@@
 
-  \subsection{WrapITK description}
-
-     \subsubsection{Creating a CMakeLists.txt file for a wrapper library}
+  \section{WrapITK description}
+
+     \subsection{Creating a CMakeLists.txt file for a wrapper library}
 Each WrapITK sub-library (e.g. \verb$Base$, or \verb$SpatialObject$) lives in a
 sub-directory of the WrapITK project (within the \verb$Modules$ directory) with a
-\verb$CMakeLists.txt$ file that describes how that library  and language support files
+\verb$CMakeLists.txt$ file that describes how that library and its language support files
 (e.g. python template definitions) is to be created. Moreover, any external
@@
   \item \verb$BEGIN_WRAPPER_LIBRARY()$ sets up the environment to wrap a set of classes into a
-library with a given name. This macro is defined in \verb$ConfigureWrapping.cmake$
+library with a given name. This macro is defined in \verb$ConfigureWrapping.cmake$.
 \verb$WRAPPER_LIBRARY_DEPENDS$ stores the list of WrapITK libraries on which the
@@
   \item \verb$WRAPPER_LIBRARY_LINK_LIBRARIES$ stores a set of other libraries to add at link
-time. This can be 3rd party libraries that you will use (be sure to properly set
+time. These can be 3rd party libraries that you will use (be sure to properly set
 \verb$LINK_DIRECTORIES$ in this case), or more commonly, the ITK libraries that need to
-be linked in, like \verb$ITKCommon$, \verb$ITKIO$, or other.
+be linked in, like \verb$ITKCommon$, \verb$ITKIO$, etc.
 
@@
 inputs and compile a wrapper library. This macro also causes various language
-support files to be created (python only currently) which make it easy to load
-that library in python, and which know about the template instances defined.
+support files to be created (currently only python) which makes it easy to load
+that library in python, and which knows about the template instances defined.
 This macro is defined in \verb$CreateWrapperLibrary.cmake$, and calls language support
@@
 
-     \subsubsection{Creating wrap\_XXX.cmake files to wrap classes}
+     \subsection{Creating wrap\_XXX.cmake files to wrap classes}
 
@@
 
-WrapITK define several macros and variable designed to:
-\begin{itemize}
-  \item make creation of wrappers easy. The syntax is simple enough to get in quickly.
-  \item make choice of template arguments explicit. It should be easy to understand
+WrapITK define several macros and variables designed to:
+\begin{itemize}
+  \item make creation of wrappers easy. The syntax is simple enough start quickly.
+  \item make the choice of template arguments explicit. It should be easy to understand
 the idea of the author of a wrapper by reading the file.
@@
 The most common case should be to create a new wrapper for a simple image filter, like 
-\verb$MedianImageFilter$. Let see that example in details.
+\verb$MedianImageFilter$. Let's see that example in detail.
 
@@
 WRAP_CLASS("itk::MedianImageFilter" POINTER)
-  WRAP_IMAGE_FILTER_INT(2)
+  WRAP_IMAGE_FILTER_USIGN_INT(2)
   WRAP_IMAGE_FILTER_SIGN_INT(2)
@@
 some \verb$WRAP_IMAGE_FILTER_*$ macros. \verb$WRAP_CLASS("itk::MedianImageFilter" POINTER)$
-begin the wrapping of the \verb$itk::MedianImageFilter$ templated class. The name of the class
-must be fully qualified. The option \verb$POINTER$ indicate that the object of the class can be
+begins the wrapping of the \verb$itk::MedianImageFilter$ templated class. The name of the class
+must be fully qualified. The option \verb$POINTER$ indicates that the object of the class can be
 manipulated with a \verb$SmartPointer$, and that the \verb$SmartPointer$ specialization for
@@
   \item \verb$WRAP_INCLUDE("header.h")$. By default, \verb$itkMedianImageFilter.h$ is included
-when the  causes the \verb$itk::MedianImageFilter$ is wrapped, and this behavior is most of the
-time enough. If it not enough, this macro can be used to include some specific files.
+when \verb$itk::MedianImageFilter$ is wrapped, and this behavior is usually
+enough. If it not enough, this macro can be used to include some specific files.
 
@@
 
-WrapITK define some lists which group the types and dimensions. Those list can be used
+WrapITK defines some lists which group the types and dimensions. Those lists can be used
 by the developer to create a wrappers but must {\em never} be modified.
@@
 
-  \item \verb$WRAP_ITK_INT$ contains all unsigned integer types selected by the user.
+  \item \verb$WRAP_ITK_USIGN_INT$ contains all unsigned integer types selected by the user.
 
@@
 
-  \item \verb$WRAP_ITK_INTEGRAL$ contains all signed and unsigned integral types
+  \item \verb$WRAP_ITK_INT$ contains all signed and unsigned integral types
 selected by the user.
@@
 
-WrapITK provides some macros to manipulate those list and use them
+WrapITK provides some macros to manipulate those list and uses them
 to create the wrappers. Most of those macros are there to fill a lack
-of feature to manipulate lists in CMake, and should be replaced by
+of features to manipulate lists in CMake, and should be replaced by
 some CMake native commands in the future.
@@
 \begin{itemize}
-  \item \verb$UNIQUE()$
-
-  \item \verb$SORT()$
-
-  \item \verb$INTERSECTION()$
-
-  \item \verb$FILTER()$
-
-  \item \verb$FILTER_DIMS()$
-
-  \item \verb$INCREMENT()$
-
-  \item \verb$DECREMENT()$
+  \item \verb$UNIQUE(var list)$ creates a new list called \verb$var$ composed of the same
+elements as the ones in \verb$list$ without duplicates. This macro is useful to impose
+a type even if it hasn't been selected by the user. The following line for example, from
+\verb$Modules/IO/wrap_itkImageFileReader.cmake$, forces the unsigned char type to be
+wrapped:
+
+\small \begin{verbatim}
+  UNIQUE(image_types "UC;${WRAP_ITK_ALL_TYPES}")
+\end{verbatim} \normalsize
+
+  \item \verb$SORT(var list)$ creates a new list called \verb$var$ which contains the
+same elements as \verb$list$, sorted lexicographically
+
+  \item \verb$INTERSECTION(var list1 list2)$ creates a new list called \verb$var$ which
+is the intersection of lists \verb$list1$ and \verb$list2$
+
+  \item \verb$REMOVE(var list1 list2)$ removes elements in \verb$list2$ from \verb$list1$
+and store the result in \verb$var$
+
+  \item \verb$INCREMENT(var number)$ increments \verb$number$ by one and stores the result
+in \verb$var$
+
+  \item \verb$DECREMENT(var number)$ decrement \verb$number$ by one an store the result
+in \verb$var$
+
+  \item \verb$FILTER_DIMS(var dimension_condition)$ processes a \verb$dimension_condition$
+and returns a list of the dimensions that (a) meet the condition, and (b) were selected
+to be wrapped. Recall that the condition is either a CMake list of dimensions, or a
+string of the form "n+" where n is a number.
 
@@
   \begin{itemize}
-    \item \verb$INT$
-    \item \verb$SIGN_INT$
-    \item \verb$REAL$
-    \item \verb$VECTOR_REAL$
-    \item \verb$COV_VECTOR_REAL$
-    \item \verb$RGB$
-    \item \verb$ALL$
-    \item \verb$SCALAR$
-    \item \verb$VECTOR$
-  \end{itemize}
-
- This macro create a template instantiation with \verb$size$
+    \item \verb$USIGN_INT$ to select all the image types with unsigned integral
+pixel types selected by the user
+    \item \verb$SIGN_INT$ to select all the image types with signed integral
+pixel types selected by the user
+    \item \verb$INT$ to select all the image types with signed and unsigned integral
+pixel types selected by the user
+    \item \verb$REAL$ to select all the image types with real pixel types selected by the user
+    \item \verb$VECTOR_REAL$ to select all the image types with \verb$Vector$
+pixel types selected by the user
+    \item \verb$COV_VECTOR_REAL$ to select all the image types with \verb$CovariantVector$
+pixel types selected by the user
+    \item \verb$RGB$ to select all the image types with \verb$RGBPixel$
+pixel types selected by the user
+    \item \verb$SCALAR$ to select all the image types with scalar pixel types selected by the user
+    \item \verb$VECTOR$ to select all the image types with \verb$Vector$ and \verb$CovariantVector$
+pixel types selected by the user
+    \item \verb$ALL$ to select all the image types selected by the user.
+  \end{itemize}
+
+ This macro creates a template instantiation with \verb$size$
 \verb$itk::Image$ parameters of the given pixel type. So if you are wrapping a filter
-which should take two images with integral pixel types, write \verb$WRAP_IMAGE_FILTER_INT(2)$. The
-specific integral data type(s) (\verb$char$, \verb$long$, or \verb$short$ in the \verb$WRAP_IMAGE_FILTER_INT$ case) will
+which should take two images with integral pixel types, write \verb$WRAP_IMAGE_FILTER_USIGN_INT(2)$. The
+specific integral data type(s) (\verb$char$, \verb$long$, or \verb$short$ in the \verb$WRAP_IMAGE_FILTER_USIGN_INT$ case) will
 be determined by the user-selected build parameters (e.g. \verb$WRAP_long$, and
@@
   \item \verb$WRAP_IMAGE_FILTER_TYPES()$. Creates template instantiations of the
-current image filter, for all the dimensions selected by the user (or dimensions
+current image filter for all the dimensions selected by the user (or dimensions
 selected by the user that meet the optional dimensionality condition). This
@@
 pixel types of the images in the filter's template parameter list. The optional
-dimensionality condition should be  placed in the last parameter.
+dimensionality condition should be placed as the last parameter.
 
@@
 
-  \subsection{Extending or customizing WrapITK}
+  \section{Extending or customizing WrapITK}
 
@@
 
-  \subsection{External projects}
-
-    \subsubsection{Why external projects?}
+  \section{External projects}
+
+    \subsection{Why external projects?}
 
@@
 and edit the project name in the {\em CMakeLists.txt} file to
-begin your new contribution.} for example, is to build {\em all}
+begin your new contribution.}, for example, to build {\em all}
 the methods of the wrapped classes, and so to be sure everything builds as it should
-\footnote{We have found and fixed numbers of bug in ITK while adding
+\footnote{We have found and fixed  a number of bugs in ITK while adding
 more classes to WrapITK}.
-In WrapITK, we used them to avoid managing switches if some dependencies or not
-found: the project must found its dependencies or fail.
-
-    \subsubsection{Building}
+In WrapITK, we used them to avoid managing switches if some dependencies are not
+found: the project must find its dependencies or fail.
+
+External projects are not yet supported for Tcl and Java. See \ref{section:contribute}
+to contribute external project support for those languages.
+
+    \subsection{Building}
 To build an external project, first ensure that WrapITK has been properly built.
@@
 
-    \subsubsection{Usage}
+    \subsection{Usage}
 Once an external project has been built, it can be tested directly from the
@@
 subdirectory, and run the command \verb$import ProjectConfig$ (or 
-\verb$import ProjectConfig-[Debug|Release|...]$ if you were using an IDE, depending on which
+\verb$import ProjectConfig-[Debug|Release|...]$ if you are using an IDE, depending on which
 build configuration was set from the IDE). This command sets up the search paths
@@
 
-    \subsubsection{Installation}
+    \subsection{Installation}
 Simply type \verb$make install$ (or run your IDE's install step) to install the
@@
 
-    \subsubsection{Top-level CMakeLists for external projects}
+    \subsection{Top-level CMakeLists for external projects}
 In addition to having a set of \verb$wrap_XXX.cmake$ files and the proper
@@
 
-    \subsubsection{Examples}
+    \subsection{Examples}
 
@@
 
-    \subsubsection{BufferConversion: an example of extension for one language}
-
-Write me.
-
-    \subsubsection{ItkVtkGlue: an example of extension for all languages, including C++}
-
-ItkVtkGlue wrap the classes used to convert data from ITK to VTK \cite{VtkWebSite} and from VTK to ITK.
+    \subsection{BufferConversion: an example of extension for one language}
+
+This project is a python only project. It requires you to have Numeric, Numarray or numpy installed
+on your system, and will let the user convert ITK images to python matrices, and python matrices
+to ITK images. It thus provide a bridge between ITK and other great python tools like SciPy
+\ref{SciPyWebSite} (and a lot of others).
+
+Once installed, the function are directly available in the \verb$itk$ module - there is nothing
+special to import. A \verb$PyBuffer$ template let you choose the type to convert, exactly
+like with the ITK classes. You can then use the \verb$GetArrayFromImage()$ and
+\verb$GetImageFromArray()$ method to convert an array to an ITK image, and an
+ITK image to an array respectively. There is no need to instantiate a \verb$PyBuffer$ object: the methods
+are \verb$static$.
+
+\begin{verbatim}
+1> import itk
+
+2> reader = itk.ImageFileReader.IUS2.New(FileName='cthead1.png')
+
+3> array = itk.PyBuffer.IUS2.GetArrayFromImage(reader.GetOutput())
+
+4> array
+4>
+array([[0, 0, 0, ..., 0, 0, 0],
+       [0, 0, 0, ..., 0, 0, 0],
+       [0, 0, 0, ..., 0, 0, 0],
+       ...,
+       [0, 0, 0, ..., 0, 0, 0],
+       [0, 0, 0, ..., 0, 0, 0],
+       [0, 0, 0, ..., 0, 0, 0]], type=UInt16)
+
+5> image = itk.PyBuffer.IUS2.GetImageFromArray(array)
+
+6> image
+6> <C itk::SmartPointer<(itk::Image<(unsigned short,2)>)> instance at _50684208_p_itk__SmartPointerTitk__ImageTunsigned_short_2_t_t>
+\end{verbatim}
+
+Because PyBuffer is a python only external project, its directory structure is very
+simple - there is no subdirectory. This external project should be used as an example
+for all the languages specific external projects.
+
+    \subsection{ItkVtkGlue: an example of extension for all languages, including C++}
+
+ItkVtkGlue wraps the classes used to convert data from ITK to VTK \cite{VtkWebSite} and from VTK to ITK.
 Those classes comes from the InsightApplications \cite{ITKWebSite}, and make the conversion
@@
 
-With the python lazy loading, the classes are not loaded by default, and thus avoid
+With python lazy loading, the classes are not loaded by default, and thus avoid
 loading the entire vtk code in memory. The classes are directly available in the
-\verb$itk$ module, and the underlaying code is loaded only when those classes are used.
+\verb$itk$ module, and the underlying code is loaded only when those classes are used.
 
@@
 
-The \verb$itk.show3D$ class use the class \verb$ImageToVTKImageFilter$ to create the
+The \verb$itk.show3D$ class uses the class \verb$ImageToVTKImageFilter$ to create the
 volume rendering shown in Figure \ref{screenshot}.
 
-  \subsection{Extending language support and adding more languages}
+This project provides new features for all the languages, including C++.
+Its directory structure reflects this.
+
+\begin{verbatim}
+|-- CMakeLists.txt
+|-- Wrapping
+|   |-- CMakeLists.txt
+|   |-- Python
+|   |   |-- CMakeLists.txt
+|   |   |-- Tests
+|   |   |   |-- CMakeLists.txt
+|   |   |   |-- CannyEdgeDetectionImageFilter.py
+|   |   |   `-- simpleItkVtkPipeline.py
+|   |   `-- itkvtk.py
+|   |-- itkvtk.swg
+|   |-- wrap_itkImageToVTKImageFilter.cmake
+|   `-- wrap_itkVTKImageToImageFilter.cmake
+|-- images
+|   `-- cthead1.png
+`-- src
+    |-- itkImageToVTKImageFilter.h
+    |-- itkImageToVTKImageFilter.txx
+    |-- itkVTKImageToImageFilter.h
+    `-- itkVTKImageToImageFilter.txx
+\end{verbatim}
+
+The C++ source files are in
+directory src, while the files needed for WrapITK are in Wrapping.
+The CMakeLists.txt file in the root of the project includes the
+Wrapping sub directory only if the user ask for it with the option
+BUILD\_WRAPPERS. Some python specific code can be found in Wrapping/Python
+directory, and some python tests in Wrapping/Python/Tests.
+The itkvtk.swg file contains the typemaps required to return vtk
+objects.
+The images directory contains the images used for the tests. Putting
+the images in this directory rather than in the root of the project
+prevents overriding the reference files during the test, which might occur if the build
+is done in the source tree.
+The project should also provide C++ tests - it is not done yet.
+
+  \section{Extending language support and adding more languages}
 
@@
 
-    \subsubsection{Generating target language code}
+    \subsection{Generating target language code}
 
@@
 
-    \subsubsection{typemaps}
+    \subsection{typemaps}
 
@@
 
-  \subsection{Contributing to WrapITK}
-
-WrapITK is an opensource project, and so all contributions are welcome. Here are
+  \section{Contributing to WrapITK}
+\label{section:contribute}
+
+WrapITK is an open source project, so all contributions are welcome. Here are
 some points which requires special attention:
 \begin{itemize}
-  \item Test it and report problem. That's the more important thing to do:
-we need feedbacks to enhance WrapITK quality ! Report all bugs you may found
+  \item Test it and report problem. That's the most important thing to do:
+we need feedback to enhance WrapITK quality! Report all bugs you may find
 to \url{http://voxel.jouy.inra.fr/roundup/wrapitk/} \cite{RoundupWebSite}.
@@
 by swig like perl \cite{PerlWebSite}, ruby \cite{RubyWebSite}, ocaml \cite{OcamlWebSite} and others.
-  \item Add more classes. WrapITK add lots of new classes compared to the current
-wrapping system, but there is still lots of work to do, especially to support more
-filter dedicated to \verb$Vector$ pixels.
-\end{itemize}
-
-\verb$darcs$ \cite{DarcsWebSite} allow to easily contribute to WrapITK, by sending
-patch by email, while keeping credits for the work done.
+  \item Add more classes. WrapITK adds many new classes compared to the current
+wrapping system, but there is still a lot of work to do, especially to support more
+filters dedicated to \verb$Vector$ pixels.
+\end{itemize}
+
+\verb$darcs$ \cite{DarcsWebSite} allows you to easily contribute to WrapITK, by sending
+patches by email, while keeping credits for the work you have done.
 Feel free to send patches; they will be tested and integrated in the project.
@@
 
-  \item \verb$darcs whatsnew$ to display the changes you have done in
+  \item \verb$darcs whatsnew$ to display the changes you have made in
 your copy of the repository.
@@
   \item \verb$darcs record$ to record the changes you have made in your
-copy of the repository. darcs will propose you to select some changes
+copy of the repository. darcs will ask you to select some changes
 to record. It is better to create one patch for each feature or bug
@@
 
-  \item \verb$darcs send$ to send by email the patches you have recorded with
-\verb$darcs record$. Please send your patches to the WrapITK bugtracker
+  \item \verb$darcs send$ to send the patches you have recorded with
+\verb$darcs record$ by email. Please send your patches to the WrapITK bugtracker
 (wrapitk-bugmaster@jouy.inra.fr\footnote{Note that you must have an account to
@@
 \url{http://voxel.jouy.inra.fr/roundup/wrapitk/} to create one.}) so everyone
-would be able to find it easily.
+will be able to find it easily.
 
@@
 
-\section{Acknowledgments}
+\newpage
+\part{Known bugs}
+See \url{http://voxel.jouy.inra.fr/roundup/wrapitk/}.
+
+\newpage
+\part{Acknowledgments}
 I thank Dr Pierre Adenot and all the {\em Embryon et Biotechnologie} team for their
-patience during the long development time before getting a tool really usable.
-
-We would like to thank Charl P. Botha for is help to debug WrapITK on windows
-plateform, and for the patches he has contributed, as well as Richard Beare for
-his early interest in using itk with python, for his useful feedbacks, and for
-his work on buffer conversion in python.
-
-We thank Andr\'e Bongers.
+patience during the long development time before getting the tool really usable.
+
+We would like to thank Charl P. Botha for is help to debug WrapITK on the windows
+platform, and for the patches he has contributed, as well as Richard Beare for
+his early interest in using itk with python, for his useful feedback, and for
+his work on buffer conversions in python.
+
+We thank Andr\'e Bongers for his help debugging the java build on windows.
 
@@
 Finally, we thank the ITK developers for the great tool which is ITK, and for the
-previous work done on wrapping system - without it WrapITK would not be there.
-
-\section{Conclusion}
-
-ITK is a great library, with the drawback to be nearly unusable for prototyping,
-and to have a poor support for other languages than C++. WrapITK address those
-issue and finally give to ITK a good support for python. Java and Tcl, while
-not as much tweaked than python part, also take benefit of the higher number of
+previous work done on the wrapping system - without it WrapITK would not exist.
+
+\newpage
+\part{Conclusion}
+
+ITK is a great library, with the drawback of being nearly unusable for prototyping,
+and having poor support for other languages than C++. WrapITK addresses those
+issue and finally gives ITK a good support for python. Java and Tcl, while
+not as complete as python, also benefit from the larger number of
 wrapped classes, and of the increase of consistency in available types and names.
 
+\newpage
 \appendix
